### 2014-12-19 jhamrick-cs281a.tex
Work on paper

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{apacite}
\usepackage{color}
\usepackage{setspace}

\newcommand{\TODO}[1]{\textcolor{red}{[TODO: #1]}}

\doublespacing{}

\title{Making decisions from samples with variable time costs}
\author{Jessica B. Hamrick (\texttt{jhamrick@berkeley.edu})}
\date{}\bibliographystyle{apacite}

\begin{document}

\maketitle

\section{Introduction}

% How do sample-based agents make decisions based on samples that take a variable amount of time?

% Evidence for sample (simulation based agents)

% Previous models have mostly compared people to an agent that takes an infinite number of samples.

% One and done: the best thing to do is take very few samples

% But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?

\section{Sampling with variable time costs}

\citeA{Vul:2014ba} previously found that optimal sample-based agents should take only a few samples before making a decision, subject to the time cost of taking those samples. In this section, we first briefly summarize their formulation of the problem. Then, we describe how this formulation must be adjusted to account for samples with variable time costs.

\subsection{Background}

% briefly go over one and done math
Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples. Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.

In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. In practice, the agent cannot take infinite samples. Thus, to determine when to stop sampling (i.e., what the value of $N$ is), we use the \emph{sequential probability ratio test} \cite{wald1947sequential}. When using a SPRT strategy, the agent accumulates $Y_N=\sum_{i=1}^N 2X_i-1$, and stops either when $Y_N=T$ or $Y_N=-T$, for some threshold number of samples $T$. Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
\begin{equation}
\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
\label{eq:pr-choose-h1}
\end{equation}
and so the marginal probability of correctly choosing the MAP hypothesis is:
\begin{equation}
\Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
\label{eq:pr-correct}
\end{equation}
Then, the expected utility for a decision, given a threshold and the true probability, is:
\begin{equation}
\mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
\label{eq:expected-utility}
\end{equation}
where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.

We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}. Under the SPRT strategy, the probability of taking $N$ samples and then choosing $H_1$ is:
\begin{equation}
\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
\end{equation}
for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
\begin{equation}
\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
\label{eq:pr-n}
\end{equation}

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/thresholds.pdf}
        \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$. Black dots in the left two subplots show the optimal threshold $T^*$ and corresponding rate of return for each line. Left subplot: rates of return for a fixed time cost. Middle subplot: rates of return for a variable time cost. The distribution of $t_s$ was calculated empirically from simulations of a ball bouncing in a box (see Section \ref{sec:model}). Right subplot: difference in rates of return between the variable time cost and fixed time cost, approximated with Equation \ref{eq:ror-diff}.}
        \label{fig:rors}
    \end{center}
\end{figure}

Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
\begin{equation}
\mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
\label{eq:ror-fixed}
\end{equation}
where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}. Finally, given this equation, we can compute the optimal threshold for an agent using the SPRT strategy:
\begin{equation}
T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
\label{eq:optimal-threshold}
\end{equation}

The rate of return and corresponding optimal thresholds for a variety of time costs, as computed by Equations \ref{eq:ror-fixed} and \ref{eq:optimal-threshold}, are shown in the left subplot of Figure \ref{fig:rors}.

\subsection{Variable time costs}

% convert one and done math to variable time costs
We now turn to the case where $t_s$ is variable and unknown. Let $t_N:=\sum_{i=1}^N t_s^{(i)}$ be the time it takes to draw $N$ samples. Then, the rate of return becomes:
\begin{equation}
\mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
\label{eq:ror}
\end{equation}

Because $t_N$ is always positive, $(t_N+t_a)^{-1}$ is convex. Using Jensen's inequality:
\begin{equation}
\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\geq \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a},
\end{equation}
where the right hand side of the inequality corresponds to the original formulation by \citeA{Vul:2014ba}. Thus, the rate of return when the time cost is unknown will always be greater than when it is known. Intuitively, this makes sense: when an agent knows less to begin with, the samples it takes will give it more information, ultimately resulting in a higher rate of return.

We can approximate the extent to which samples are more useful when the time cost is unknown by computing using a Taylor expansion around $N\cdot{}\mathbb{E}[t_s]$:
\begin{equation}
\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\approx \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}+\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}-\ldots{}
\end{equation}
Thus, the difference is approximated by:
\begin{equation}
\mathbb{E}\left[\frac{1}{t_s+t_a}\right]-\frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}\approx \frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}
\end{equation}
Plugging this back into Equation \ref{eq:ror}, we obtain the overall difference on the rate of return:
\begin{equation}
\mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
\label{eq:ror-diff}
\end{equation}

In practice, this difference is quite small. The middle subplot of Figure \ref{fig:rors} shows the rates of return using a variable time cost,\footnote{The times used for this plot were computed empirically using physical simulations of a ball boucing in a box. See Section \ref{sec:model} for details.} and the right subplot shows the difference computed from \ref{eq:ror-diff}. Even the largest difference, which occurs at $T=1$ and $t_a=\mathbb{E}[t_s]$, is so small that it does not change the value of $T^*$; the difference would need to be about 100 times greater in order to have an effect. Using different distributions for $\Pr[t_s]$ may have larger effects, but even these are not substantial. For example, using a uniform distribution can change $T^*$ from 0 to 1 for smaller cost ratios.

To summarize, we find that the introduction of uncertainty into the time cost has very little effect. The implication of this result is that even if it \emph{does} takes a variable amount of time to draw a sample, an agent need not bother taking its uncertainty into account: it can rely solely on its estimate of the average sample time to determine an optimal threshold.

\section{Case study: intuitive physics}

How well does the optimal SPRT strategy actually match up with human responses on a task with variable sample costs? To answer this question, we considered the scenario where participants watch a ball bouncing around in a box, and must determine whether the ball will go through a hole in the wall.

\subsection{Model}
\label{sec:model}

% describe model from sources of uncertainty
As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Ullman:2014ut}. Here, we assume this to be the case, and use the model from \citeA{Smith2012}. Briefly, their model incorporates four sources of uncertainty into the physical simulations: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$). To determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model. For each sample, we computed whether the ball went in the hole, and then averaged over all the samples.

\subsection{Methods}

\subsubsection{Participants}

We recruited $N=328$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework. Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work. Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli). Additionally, we excluded $N=8$ participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of $N=320$ participants.

\subsubsection{Stimuli}

% include figure of stimulus
The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px. All stimuli consisted of two separate animations. The first was he stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction. The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole hitting the wall with the hole in it. In both animations, the ball had a velocity of 400px/s. Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).

There were 48 different initial animations, and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus. The four feedback types were: ``straight hit'', where the ball went directly through the center of the hole; ``far miss'', where the ball missed the hole by a wide margin; ``close hit'', where the ball just barely went through the hole; and ``near miss'', where the ball just barely missed the hole. The two hole sizes were 100px and 200px.

In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size. Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.

In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants. The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px). Thus, participants saw a total of 63 trials throughout the experiment.

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. The left panel shows the initial screen presented to the participant. The middle panel shows the occluded ball, after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. The right panel shows the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure}

\subsubsection{Procedure}

The experiment was divided into two phases: the training phase, and the experimental phase. During the training phase, participants made judgments on the seven instruction trials in order to get used to the task. During the experimental phase, participants made judgements on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.

On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole. Participants were instructed to press the ``space'' key to begin the trial. Immediately upon pressing ``space'', the initial stimulus presentation began. As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from). Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' to respond in the affirmative, and `p' to respond in the negative. Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response. Additionally, the gray occluder was removed, and participants were shown the feedback animation. After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial. Figure \ref{fig:experiment} shows a few frames from one of the experimental trials.

\subsection{Results}

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/human_pct_vs_rt.pdf}
        \caption{\textbf{Response times as a function of response.}}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure}

\section{Discussion}

\bibliography{references}

\end{document}

### 2014-12-19 jhamrick-cs281a.tex
Fix filename
Add introduction, some results

@@
 % How do sample-based agents make decisions based on samples that take a variable amount of time?
-
-% Evidence for sample (simulation based agents)
-
-% Previous models have mostly compared people to an agent that takes an infinite number of samples.
+Bayesian agents must often make judgments about situations that require computing a difficult, if not intractable, posterior distribution.
+One popular method to handle this issue is to use a Monte Carlo approximation to the posterior, where the agent draws some number of samples and bases its decision on those samples.
+However, even this approach is not always feasible for agents with limited computational computational power, as it can take thousands or even millions of samples to approach a decent approximation.
+The situation is further complicated by the fact that samples can vary in a variety of ways: for example, some samples may provide more information than others, and some samples may vary in how \emph{long} they take to compute.
+Given these constraints, what is the optimal sampling behavior for a sample-based agent?
 
 % One and done: the best thing to do is take very few samples
+Recent research by \citeA{Vul:2014ba} asked how many samples an agent should take before making a decision.
+Surprisingly, they found that to optimize success in the \emph{long} run, it is not useful for sample-based agents to take more than a few samples.
+For example, suppose that there is a reward for correct answers and no penalty for incorrect answers, and that the agent can take ten samples in the time it takes to actually execute the action that reflects the decision.
+Then, the optimal number of samples that the agent should base their decision on is only one!
+While this is obviously suboptimal for each \emph{individual} decision, over many decisions, this strategy trades off between the amount of time one can actually spend taking actions versus thinking.
 
 % But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?
+One piece of the puzzle not addressed by \citeA{Vul:2014ba} was the case where samples themselves take a variable amount of time.
+This case is not unheard of: for example, recent research studying how people reason about the physical world suggests that people may rely on samples from noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+If people are, in fact, using physical simulations, then it is likely that each simulation will take a different amount of time to run, due to the sequential nature of the simulation.
+For example, if the task is to predict whether a bouncing ball will hit a green or red target first \cite{Smith:2013ug}, the time it takes to run the simulation is unknown until the ball actually hits one of the targets.
+
+However, in nearly all the research on intuitive physics, people have been compared to a simulation-based model which took a large number of samples---rather than a small number of samples which would be optimal in the long run---and those samples have been assumed to take constant time.
+In their appendix, \citeA{Battaglia2013}, attempted to determine the number of samples taken by people in several tasks concerning towers of building blocks.
+They did find a consistent story with \citeA{Vul:2014ba}: participants in their experiments seemed to use between three and seven samples per judgment.
+Despite this analysis, the samples were still assumed to be constant in time cost.
+
+% talk about SPRT
+\cite{wald1947sequential}
+\cite{Bitzer:2014ea}
+\cite{Gold:2007fo}
+\cite{Ratcliff:2008ux}
+
+% Summary
+In this paper, we ask the question: how many samples should sample-based agents take before coming to a decision, if the time cost of these samples is unknown?
+We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost.
+To show this, we first summarize the formal model as described by \citeA{Vul:2014ba}.
+Then, we extend this model to handle the case where samples take a variable amount of time.
+Finally, we apply this model to a behavioral case study.
 
@@
 \begin{equation}
-\mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
+\Delta=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
 \label{eq:ror-diff}
@@
 % describe model from sources of uncertainty
-As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Ullman:2014ut}.
+As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 Here, we assume this to be the case, and use the model from \citeA{Smith2012}.
@@
 There were 48 different initial animations, and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
-The four feedback types were: ``straight hit'', where the ball went directly through the center of the hole; ``far miss'', where the ball missed the hole by a wide margin; ``close hit'', where the ball just barely went through the hole; and ``near miss'', where the ball just barely missed the hole.
+The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
 The two hole sizes were 100px and 200px.
@@
 
+\subsection{Analysis}
+
+\TODO{}
+
 \subsection{Results}
 
-\begin{figure}[h]
+\begin{figure}[t]
     \begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/human_pct_vs_rt.pdf}
-        \caption{\textbf{Response times as a function of response.}}
+        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
+        \caption{\textbf{Response times as a function of response.} \TODO{}}
         \label{fig:pct-vs-rt}
@@
 \end{figure}
+
+\subsubsection{Responses}
+
+On average, participants were correct about 76\% of the time ($\mu=0.76$, $\sigma^2=0.00001$), and responded that the ball would go in the hole about half the time ($\mu=0.53$, $\sigma^2=0.00001$).
+There was a significant effect of feedback type on participants' responses \TODO{}; there was also an effect of hole size, though less so \TODO{}.
+Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.
+
+\subsubsection{Response times}
+
+Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms).
+There was a significant effect of feedback type on response time \TODO{}, however, there was not a large effect of hole size on response time, except in the case of the ``far in'' (FI) trials, in which the ball went straight through the center of the hole \TODO{}.
+Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.
+
+\subsubsection{Speed-accuracy tradeoff}
+
+As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear speed-accuracy tradeoff in participants responses and response times.
+In particular, participants were on average faster to respond on trials that they were more certain about, and slower to respond to trials that they were unsure about.
+This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ take much longer to make, because it takes longer to get to one threshold versus the other.
+
+\subsubsection{Comparison to SPRT}
+
+Participant responses were well correlated with a SPRT model with $T=2$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
+There was also a significant correlation with resonse time for the $T=2$ SPRT model ($r=0.35$, 95\% CI [0.27, 0.43]).
 

### 2014-12-19 jhamrick-cs281a.tex
More work on introduction

@@
 
+% SPRT
+\citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
+For example, consider the case where an agent must decide between two options.
+If they draw samples favoring one of the options with probability 0.95, then the agent can be fairly confident about which is the better option after only a few samples.
+In contrast, if the probability is 0.55, then the agent would need many samples to be confident about which option is better.
+Of course, the agent doesn't know what the probability is: that is the point of sampling.
+One strategy which addresses this issue is known as the \emph{sequential probability ratio test} \cite{wald1947sequential}, or SPRT, and has been used extensively to model a variety of decision making tasks in humans \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}.
+An agent using SPRT accumulates evidence for one option versus another, and stops sampling once a particular threshold of evidence has been reached.
+So, rather than optimizing for a fixed number of samples, the agent should optimize for the threshold.
+
 % But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?
@@
 
-% talk about SPRT
-\cite{wald1947sequential}
-\cite{Bitzer:2014ea}
-\cite{Gold:2007fo}
-\cite{Ratcliff:2008ux}
-
 % Summary
-In this paper, we ask the question: how many samples should sample-based agents take before coming to a decision, if the time cost of these samples is unknown?
+In this paper, we ask the question: what SPRT threshold should sample-based agents use when making decisions, if the time cost of taking samples is unknown?
 We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost.
@@
 Then, we extend this model to handle the case where samples take a variable amount of time.
-Finally, we apply this model to a behavioral case study.
+Finally, we apply the SPRT model to a behavioral case study in order to understand how people treat variable-time samples.
 

### 2014-12-19 jhamrick-cs281a.tex
Add results of statistical tests

@@
 Briefly, their model incorporates four sources of uncertainty into the physical simulations: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$).
-To determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model.
-For each sample, we computed whether the ball went in the hole, and then averaged over all the samples.
+We fit these model parameters to human judgments in a related but separate task.
+Then, to determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model.
+From these samples, we estimated a truncated normal distribution along the wall with the hole in it, and then computed the probability density lying within the region of the hole.
 
@@
 
-\subsection{Analysis}
-
-\TODO{}
-
 \subsection{Results}
@@
 
-On average, participants were correct about 76\% of the time ($\mu=0.76$, $\sigma^2=0.00001$), and responded that the ball would go in the hole about half the time ($\mu=0.53$, $\sigma^2=0.00001$).
-There was a significant effect of feedback type on participants' responses \TODO{}; there was also an effect of hole size, though less so \TODO{}.
+On average, participants were correct 76.1\% of the time ($N=17686$) and responded that the ball would go in the hole 52.8\% of the time ($N=17686$).
+There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$).
+Additionally, there was an interaction between feedback type and hole size ($\chi^2(3)=64.469, p<0.001$).
 Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.
@@
 Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms).
-There was a significant effect of feedback type on response time \TODO{}, however, there was not a large effect of hole size on response time, except in the case of the ``far in'' (FI) trials, in which the ball went straight through the center of the hole \TODO{}.
+There were significant effects of both feedback type ($\chi^2(3)=63.611, p<0.001$) and hole size ($\chi^2(1)=8.9808, p<0.01$) on response time, as well as an interaction between feedback type and hole size ($\chi^2(3)=27.146, p<0.001$).
+However, the hole size was only significant in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole.
 Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.

### 2014-12-19 jhamrick-cs281a.tex
Almost done

@@
         \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
-        \caption{\textbf{Response times as a function of response.} \TODO{}}
+        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
         \label{fig:pct-vs-rt}
@@
 
+For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples.
 Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms).
@@
 
-\subsubsection{Speed-accuracy tradeoff}
+\subsubsection{Relationship of responses to reaction time}
 
@@
 
-Participant responses were well correlated with a SPRT model with $T=2$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
+We fit participant responses and response times to the SPRT model with different values of $T$, and found that $T=2$ to have the best fit.
+Participant responses were well correlated with the SPRT model ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
 There was also a significant correlation with resonse time for the $T=2$ SPRT model ($r=0.35$, 95\% CI [0.27, 0.43]).
+However, it turns out that the number of bounces is a much better predictor of people's response times than the model itself.
+At first glance, this seems like it could contradict the earlier result that unknown sampling times have little effect on the optimal number of samples to take.
+An alternate possibility is just that each bounce adds time to people's simulations above and beyond what it adds to the model simulations, but does not actually affect the number of samples they take.
+More investigation will be required to fully understand what is going on here.
 
 \section{Discussion}
+
+In this paper, we asked the question: how should a sample-based agent act when it does not know how long it takes to draw a sample?
+To answer this question, we examined the optimal behavior of agents using the sequential probability ratio test (SPRT) with unknown time costs.
+Surprisingly, we found that the uncertainty introduced by the unknown sample times did not have a large effect: in most cases, the optimal threshold is the same regardless.
+
+We additionally ran an experiment to see how well SPRT predicts human behavior on a task which enforces unknown time costs (as well as a range of underlying probabilities).
+While we did find a clear relationship between people's responses and their reaction time, analagous to the type of relationship that would be expected from a SPRT-like policy.
+However, our SPRT model was only a mediocre explanation of people's response times---less so than even the number of times the ball bounced.
+However, people did not see the number of times that the ball bounced; thus, the effect of the number of bounces is a fairly clear sign that they \emph{are} using simulations in some manner.
+Rather than a failing of the SPRT model, this may be a failure of our simulation-based model to appropriately account for additional simulation time from bounces.
+
+However, based on our earlier result that unknown simulation time has little effect, even if we added extra simulation time per bounce to the model, it should not change the best-fitting threshold.
+Future work will investigate this claim further.
 

### 2015-01-22 manuscript.tex
Add cogsci style

--- 2014-12-19 jhamrick-cs281a.tex
@@
-\documentclass[11pt]{article}
+\documentclass[10pt,letterpaper]{article}
 
-\usepackage[margin=1in]{geometry}
+\usepackage{cogsci}
+\usepackage{pslatex}
+\usepackage{apacite}
+
 \usepackage{amsmath, amsthm, amssymb}
 \usepackage{graphicx}
-\usepackage{authblk}
-\usepackage{apacite}
 \usepackage{color}
-\usepackage{setspace}
 
@@
 
-\doublespacing{}
+\title{How long to simulate?}
 
-\title{Making decisions from samples with variable time costs}
-\author{Jessica B. Hamrick (\texttt{jhamrick@berkeley.edu})}
-\date{}\bibliographystyle{apacite}
+\author{{\large \bf Jessica B.~Hamrick (jhamrick@berkeley.edu)} \\
+  Department of Psychology \\
+  University of California, Berkeley
+  \AND {\large \bf Kevin A.~Smith (k2smith@ucsd.edu)} \\
+  Department of Psychology \\
+  University of California, San Diego
+  \AND {\large \bf Thomas L.~Griffiths (tom\_griffiths@berkeley.edu)} \\
+  Department of Psychology \\
+  University of California, Berkeley
+  \AND {\large \bf Edward Vul (evul@ucsd.edu)} \\
+  Department of Psychology \\
+  University of California, San Diego}
 
@@
 \maketitle
+
+\begin{abstract}
+\TODO{}
+
+\textbf{Keywords:} 
+add your choice of indexing terms or keywords; kindly use a
+semicolon; between each term
+\end{abstract}
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
     \begin{center}
@@
     \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
+\bibliographystyle{apacite}
+
+\setlength{\bibleftmargin}{.125in}
+\setlength{\bibindent}{-\bibleftmargin}
+
 \bibliography{references}

### 2015-01-25 manuscript.tex
Add methods for Experiment 1

@@
 
-% How do sample-based agents make decisions based on samples that take a variable amount of time?
-Bayesian agents must often make judgments about situations that require computing a difficult, if not intractable, posterior distribution.
+% % How do sample-based agents make decisions based on samples that take a variable amount of time?
+% Bayesian agents must often make judgments about situations that require computing a difficult, if not intractable, posterior distribution.
 One popular method to handle this issue is to use a Monte Carlo approximation to the posterior, where the agent draws some number of samples and bases its decision on those samples.
@@
 
-% One and done: the best thing to do is take very few samples
-Recent research by \citeA{Vul:2014ba} asked how many samples an agent should take before making a decision.
+% % One and done: the best thing to do is take very few samples
+% Recent research by \citeA{Vul:2014ba} asked how many samples an agent should take before making a decision.
 Surprisingly, they found that to optimize success in the \emph{long} run, it is not useful for sample-based agents to take more than a few samples.
@@
 
-% SPRT
-\citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
+% % SPRT
+% \citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
 For example, consider the case where an agent must decide between two options.
@@
 
-% But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?
-One piece of the puzzle not addressed by \citeA{Vul:2014ba} was the case where samples themselves take a variable amount of time.
+% % But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?
+% One piece of the puzzle not addressed by \citeA{Vul:2014ba} was the case where samples themselves take a variable amount of time.
 This case is not unheard of: for example, recent research studying how people reason about the physical world suggests that people may rely on samples from noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
@@
 
-However, in nearly all the research on intuitive physics, people have been compared to a simulation-based model which took a large number of samples---rather than a small number of samples which would be optimal in the long run---and those samples have been assumed to take constant time.
+% However, in nearly all the research on intuitive physics, people have been compared to a simulation-based model which took a large number of samples---rather than a small number of samples which would be optimal in the long run---and those samples have been assumed to take constant time.
 In their appendix, \citeA{Battaglia2013}, attempted to determine the number of samples taken by people in several tasks concerning towers of building blocks.
@@
 
-% Summary
-In this paper, we ask the question: what SPRT threshold should sample-based agents use when making decisions, if the time cost of taking samples is unknown?
+% % Summary
+% In this paper, we ask the question: what SPRT threshold should sample-based agents use when making decisions, if the time cost of taking samples is unknown?
 We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost.
@@
 
-\section{Sampling with variable time costs}
+% \section{Sampling with variable time costs}
 
-\citeA{Vul:2014ba} previously found that optimal sample-based agents should take only a few samples before making a decision, subject to the time cost of taking those samples.
+% \citeA{Vul:2014ba} previously found that optimal sample-based agents should take only a few samples before making a decision, subject to the time cost of taking those samples.
 In this section, we first briefly summarize their formulation of the problem.
@@
 
-\subsection{Background}
+% \subsection{Background}
 
-% briefly go over one and done math
-Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+% % briefly go over one and done math
+% Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 
-In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
+% In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
 In practice, the agent cannot take infinite samples.
@@
 Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
-\begin{equation}
-\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
-\label{eq:pr-choose-h1}
-\end{equation}
-and so the marginal probability of correctly choosing the MAP hypothesis is:
-\begin{equation}
-\Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
-\label{eq:pr-correct}
-\end{equation}
-Then, the expected utility for a decision, given a threshold and the true probability, is:
-\begin{equation}
-\mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
-\label{eq:expected-utility}
-\end{equation}
-where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.
+% \begin{equation}
+% \Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+% \label{eq:pr-choose-h1}
+% \end{equation}
+% and so the marginal probability of correctly choosing the MAP hypothesis is:
+% \begin{equation}
+% \Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
+% \label{eq:pr-correct}
+% \end{equation}
+% Then, the expected utility for a decision, given a threshold and the true probability, is:
+% \begin{equation}
+% \mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
+% \label{eq:expected-utility}
+% \end{equation}
+% where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.
 
-We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}.
+% We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}.
 Under the SPRT strategy, the probability of taking $N$ samples and then choosing $H_1$ is:
-\begin{equation}
-\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-\end{equation}
-for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
-\begin{equation}
-\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
-\label{eq:pr-n}
-\end{equation}
+% \begin{equation}
+% \Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+% \end{equation}
+% for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+% \begin{equation}
+% \Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
+% \label{eq:pr-n}
+% \end{equation}
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/thresholds.pdf}
-        \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$.
+% \begin{figure*}[t]
+%     \begin{center}
+%         \includegraphics[width=\textwidth]{figures/thresholds.pdf}
+%         \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$.
 Black dots in the left two subplots show the optimal threshold $T^*$ and corresponding rate of return for each line.
@@
 Right subplot: difference in rates of return between the variable time cost and fixed time cost, approximated with Equation \ref{eq:ror-diff}.}
-        \label{fig:rors}
-    \end{center}
-\end{figure*}
+%         \label{fig:rors}
+%     \end{center}
+% \end{figure*}
 
-Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
-\begin{equation}
-\mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
-\label{eq:ror-fixed}
-\end{equation}
-where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}.
+% Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
+% \begin{equation}
+% \mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
+% \label{eq:ror-fixed}
+% \end{equation}
+% where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}.
 Finally, given this equation, we can compute the optimal threshold for an agent using the SPRT strategy:
-\begin{equation}
-T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
-\label{eq:optimal-threshold}
-\end{equation}
+% \begin{equation}
+% T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
+% \label{eq:optimal-threshold}
+% \end{equation}
 
-The rate of return and corresponding optimal thresholds for a variety of time costs, as computed by Equations \ref{eq:ror-fixed} and \ref{eq:optimal-threshold}, are shown in the left subplot of Figure \ref{fig:rors}.
+% The rate of return and corresponding optimal thresholds for a variety of time costs, as computed by Equations \ref{eq:ror-fixed} and \ref{eq:optimal-threshold}, are shown in the left subplot of Figure \ref{fig:rors}.
 
-\subsection{Variable time costs}
+% \subsection{Variable time costs}
 
-% convert one and done math to variable time costs
-We now turn to the case where $t_s$ is variable and unknown. Let $t_N:=\sum_{i=1}^N t_s^{(i)}$ be the time it takes to draw $N$ samples. Then, the rate of return becomes:
-\begin{equation}
-\mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
-\label{eq:ror}
-\end{equation}
+% % convert one and done math to variable time costs
+% We now turn to the case where $t_s$ is variable and unknown. Let $t_N:=\sum_{i=1}^N t_s^{(i)}$ be the time it takes to draw $N$ samples. Then, the rate of return becomes:
+% \begin{equation}
+% \mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
+% \label{eq:ror}
+% \end{equation}
 
-Because $t_N$ is always positive, $(t_N+t_a)^{-1}$ is convex. Using Jensen's inequality:
-\begin{equation}
-\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\geq \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a},
-\end{equation}
-where the right hand side of the inequality corresponds to the original formulation by \citeA{Vul:2014ba}.
+% Because $t_N$ is always positive, $(t_N+t_a)^{-1}$ is convex. Using Jensen's inequality:
+% \begin{equation}
+% \mathbb{E}\left[\frac{1}{t_N+t_a}\right]\geq \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a},
+% \end{equation}
+% where the right hand side of the inequality corresponds to the original formulation by \citeA{Vul:2014ba}.
 Thus, the rate of return when the time cost is unknown will always be greater than when it is known.
@@
 
-We can approximate the extent to which samples are more useful when the time cost is unknown by computing using a Taylor expansion around $N\cdot{}\mathbb{E}[t_s]$:
-\begin{equation}
-\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\approx \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}+\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}-\ldots{}
-\end{equation}
-Thus, the difference is approximated by:
-\begin{equation}
-\mathbb{E}\left[\frac{1}{t_s+t_a}\right]-\frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}\approx \frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}
-\end{equation}
-Plugging this back into Equation \ref{eq:ror}, we obtain the overall difference on the rate of return:
-\begin{equation}
-\Delta=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
-\label{eq:ror-diff}
-\end{equation}
+% We can approximate the extent to which samples are more useful when the time cost is unknown by computing using a Taylor expansion around $N\cdot{}\mathbb{E}[t_s]$:
+% \begin{equation}
+% \mathbb{E}\left[\frac{1}{t_N+t_a}\right]\approx \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}+\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}-\ldots{}
+% \end{equation}
+% Thus, the difference is approximated by:
+% \begin{equation}
+% \mathbb{E}\left[\frac{1}{t_s+t_a}\right]-\frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}\approx \frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}
+% \end{equation}
+% Plugging this back into Equation \ref{eq:ror}, we obtain the overall difference on the rate of return:
+% \begin{equation}
+% \Delta=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
+% \label{eq:ror-diff}
+% \end{equation}
 
-In practice, this difference is quite small.
+% In practice, this difference is quite small.
 The middle subplot of Figure \ref{fig:rors} shows the rates of return using a variable time cost,\footnote{The times used for this plot were computed empirically using physical simulations of a ball boucing in a box.
@@
 
-To summarize, we find that the introduction of uncertainty into the time cost has very little effect.
+% To summarize, we find that the introduction of uncertainty into the time cost has very little effect.
 The implication of this result is that even if it \emph{does} takes a variable amount of time to draw a sample, an agent need not bother taking its uncertainty into account: it can rely solely on its estimate of the average sample time to determine an optimal threshold.
 
-\section{Case study: intuitive physics}
-
-How well does the optimal SPRT strategy actually match up with human responses on a task with variable sample costs?
-To answer this question, we considered the scenario where participants watch a ball bouncing around in a box, and must determine whether the ball will go through a hole in the wall.
-
-\subsection{Model}
+\section{Model}
 \label{sec:model}
@@
 
-\subsection{Methods}
+\section{Experiment 1}
 
-\subsubsection{Participants}
+Experiment 1 was a replication of the ``pong'' experiment from \cite{Smith2012}, with the major difference being a new set of stimuli and that it was run on Amazon's Mechanical Turk rather than in the lab.
+
+\subsection{Participants}
+
+We recruited $N=60$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
+Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work.
+Additionally, we excluded $N=18$ participants from analysis for failing to catch the ball on more than one control trial, leaving a total of $N=42$ participants.
+
+\subsection{Stimuli}
+
+There were 48 unique stimuli, each consisting of an animation depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px, as well as a ``paddle'' that was fixed at some $x$-coordinate but moveable along the $y$-axis.
+Each animation had a duration of 0.775 seconds and depicted the ball moving in a particular direction with a velocity of 400px/s.
+Additionally, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+
+Each animation was chosen such that were the ball to continue moving after the end of the animation, it would take exactly \TODO{} seconds to reach the $y$-coordinate of the paddle.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During this ``gap'' period in between the end of the animation and the ball reaching the $x$-coordinate of the paddle, the ball could bounce on the top, right, or bottom walls either 0, 1, or 2 times.
+
+In addition to the 48 experimental trials, there were seven instruction trials and eight control trials.
+The control trials were designed to be extremely easy and consisted of a ball heading straight towards the $x$-coordinate of the paddle (with a angle of incidence of either $90^\circ$ or close to $90^\circ$.
+Thus, participants saw a total of 63 trials throughout the experiment.
+
+\subsection{Procedure}
+
+The experiment was divided into two phases: the training phase, and the experimental phase.
+During the training phase, participants made judgments on the seven instruction trials in order to get used to the task.
+During the experimental phase, participants made judgments on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
+
+On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
+The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
+Participants were instructed to press the ``space'' key to begin the trial.
+Immediately upon pressing ``space'', the initial stimulus presentation began.
+As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
+As soon as the occluder appeared, a timer also appeared and begin counting down for \TODO{} seconds.
+During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.
+
+When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
+If the ball was on the paddle, then participants were told, ``You caught the ball!''.
+If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
+
+Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they caught the ball / the number of trials completed).
+
+\subsection{Results}
+
+\section{Experiment 2}
+
+\subsection{Participants}
 
@@
 
-\subsubsection{Stimuli}
+\subsection{Stimuli}
 
-% include figure of stimulus
-The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
-All stimuli consisted of two separate animations.
-The first was he stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole hitting the wall with the hole in it.
-In both animations, the ball had a velocity of 400px/s.
-Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+The stimuli were modified versions of those used in Experiment 1, with two main differences.
+First, instead of a moveable paddle, there was a wall with a fixed hole in it; the wall was at the same $x$-coordinate as the paddle.
+Second, while the initial stimulus presentation was identical, the stimuli in Experiment 2 had a second animation which was shown after participants responded.
+The feedback, which picked up immediately where the first animation left off, had a duration of 1.5 seconds.
+It depicted the ball either going into the hole or bouncing off the wall that contained the hole.
 
-There were 48 different initial animations, and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
+There were 48 different initial animations (corresponding to the animations used in Experiment 1), and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
 The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
@@
 
-In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
-The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
-Thus, participants saw a total of 63 trials throughout the experiment.
+The training trials and control trials were also the same as those used in Experiment 1, with feedback animations that were the same across participants.
+The feedback and hole sizes of the control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
 
@@
 
-\subsubsection{Procedure}
+\subsection{Procedure}
 
-The experiment was divided into two phases: the training phase, and the experimental phase.
-During the training phase, participants made judgments on the seven instruction trials in order to get used to the task.
-During the experimental phase, participants made judgements on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
-
-On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
-Participants were instructed to press the ``space'' key to begin the trial.
-Immediately upon pressing ``space'', the initial stimulus presentation began.
-As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
+The procedure was very similar to that in Experiment 1, and was identical up until the point that the occluder was shown.
+Instead of then having a fixed amount of time to answer, participants had unlimited time.
 Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' to respond in the affirmative, and `p' to respond in the negative.
@@
 
-\subsection{Results}
+\section{Results}
 
@@
 
-\subsubsection{Responses}
+\subsection{Responses}
 
@@
 
-\subsubsection{Response times}
+\subsection{Response times}
 
@@
 
-\subsubsection{Relationship of responses to reaction time}
+\subsection{Relationship of responses to reaction time}
 
@@
 
-\subsubsection{Comparison to SPRT}
+\subsection{Comparison to SPRT}
 
@@
 
-In this paper, we asked the question: how should a sample-based agent act when it does not know how long it takes to draw a sample?
+% In this paper, we asked the question: how should a sample-based agent act when it does not know how long it takes to draw a sample?
 To answer this question, we examined the optimal behavior of agents using the sequential probability ratio test (SPRT) with unknown time costs.
@@
 
-We additionally ran an experiment to see how well SPRT predicts human behavior on a task which enforces unknown time costs (as well as a range of underlying probabilities).
+% We additionally ran an experiment to see how well SPRT predicts human behavior on a task which enforces unknown time costs (as well as a range of underlying probabilities).
 While we did find a clear relationship between people's responses and their reaction time, analagous to the type of relationship that would be expected from a SPRT-like policy.
@@
 
-However, based on our earlier result that unknown simulation time has little effect, even if we added extra simulation time per bounce to the model, it should not change the best-fitting threshold.
+% However, based on our earlier result that unknown simulation time has little effect, even if we added extra simulation time per bounce to the model, it should not change the best-fitting threshold.
 Future work will investigate this claim further.

### 2015-01-25 manuscript.tex
Work on introduction

@@
 
-\title{How long to simulate?}
+\title{Think again?\\ Optimal mental simulation tracks problem difficulty}
 
@@
 
-% % How do sample-based agents make decisions based on samples that take a variable amount of time?
-% Bayesian agents must often make judgments about situations that require computing a difficult, if not intractable, posterior distribution.
-One popular method to handle this issue is to use a Monte Carlo approximation to the posterior, where the agent draws some number of samples and bases its decision on those samples.
-However, even this approach is not always feasible for agents with limited computational computational power, as it can take thousands or even millions of samples to approach a decent approximation.
-The situation is further complicated by the fact that samples can vary in a variety of ways: for example, some samples may provide more information than others, and some samples may vary in how \emph{long} they take to compute.
-Given these constraints, what is the optimal sampling behavior for a sample-based agent?
+%% The question we're interested in: how many simulations do people take?
+Imagine you are playing a video game---for example, Angry Birds or Desert Golf---in which you need to predict where an object will end up.
+Recent research in the domain of intuitive physics and mental simulation has suggested that people make predictions like these by running noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
+For example, if people are running mental simulations, \emph{how many} simulations do they run?
 
-% % One and done: the best thing to do is take very few samples
-% Recent research by \citeA{Vul:2014ba} asked how many samples an agent should take before making a decision.
-Surprisingly, they found that to optimize success in the \emph{long} run, it is not useful for sample-based agents to take more than a few samples.
+\TODO{something discussing that there are scenarios in which it's useful to take more simulations than others?}
+
+%% What's already been done
+Previous research by \citeA{Vul:2014ba} has asked, in the abstract, how many samples an agent should take before making a decision.
+Surprisingly, they found that to optimize success in the long run, it is not useful for sample-based agents to take more than a few samples.
 For example, suppose that there is a reward for correct answers and no penalty for incorrect answers, and that the agent can take ten samples in the time it takes to actually execute the action that reflects the decision.
 Then, the optimal number of samples that the agent should base their decision on is only one!
-While this is obviously suboptimal for each \emph{individual} decision, over many decisions, this strategy trades off between the amount of time one can actually spend taking actions versus thinking.
+While this is obviously suboptimal for each individual decision, over many decisions, this strategy trades off between the amount of time one can actually spend taking actions versus thinking.
 
-% % SPRT
-% \citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
+%% What's missing
+So far, the theoretical results from \citeA{Vul:2014ba} have largely not been applied to the domain of mental simulation, and lead to several questions regarding how people use their mental simulations.
+First, do people run multiple mental simulations?
+If so, do they run a fixed number of simulations, or vary the number of simulations based on the difficult?
+A supplementary analysis by \citeA{Battaglia2013} suggests that people do run multiple simulation.
+In their analysis, they attempted to determine the number of samples taken by people in several tasks concerning towers of building blocks.
+They did find a consistent story with \citeA{Vul:2014ba}: participants in their experiments seemed to use between three and seven samples per judgment.
+However, their analysis only concerned the variability of responses and did not take into account response time.
+
+%% What we're going to do and how we're going to do it
+In this paper, we investigate how many mental simulations people run when making decisions in a two alternative force choice task, analyzing both their response times and the variability of responses.
+\TODO{plan of the paper}
+
+\section{Modeling mental simulation with SPRT}
+
+% SPRT
+\citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
 For example, consider the case where an agent must decide between two options.
@@
 
-% % But one and done assumes that sampling cost is fixed -- what if samples take a variable amount of time?
-% One piece of the puzzle not addressed by \citeA{Vul:2014ba} was the case where samples themselves take a variable amount of time.
-This case is not unheard of: for example, recent research studying how people reason about the physical world suggests that people may rely on samples from noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-If people are, in fact, using physical simulations, then it is likely that each simulation will take a different amount of time to run, due to the sequential nature of the simulation.
-For example, if the task is to predict whether a bouncing ball will hit a green or red target first \cite{Smith:2013ug}, the time it takes to run the simulation is unknown until the ball actually hits one of the targets.
+\TODO{probably don't actually need to go through all the math here, can just cite the appendix of one and done?}
 
-% However, in nearly all the research on intuitive physics, people have been compared to a simulation-based model which took a large number of samples---rather than a small number of samples which would be optimal in the long run---and those samples have been assumed to take constant time.
-In their appendix, \citeA{Battaglia2013}, attempted to determine the number of samples taken by people in several tasks concerning towers of building blocks.
-They did find a consistent story with \citeA{Vul:2014ba}: participants in their experiments seemed to use between three and seven samples per judgment.
-Despite this analysis, the samples were still assumed to be constant in time cost.
-
-% % Summary
-% In this paper, we ask the question: what SPRT threshold should sample-based agents use when making decisions, if the time cost of taking samples is unknown?
-We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost.
-To show this, we first summarize the formal model as described by \citeA{Vul:2014ba}.
-Then, we extend this model to handle the case where samples take a variable amount of time.
-Finally, we apply the SPRT model to a behavioral case study in order to understand how people treat variable-time samples.
-
-% \section{Sampling with variable time costs}
-
-% \citeA{Vul:2014ba} previously found that optimal sample-based agents should take only a few samples before making a decision, subject to the time cost of taking those samples.
-In this section, we first briefly summarize their formulation of the problem.
-Then, we describe how this formulation must be adjusted to account for samples with variable time costs.
-
-% \subsection{Background}
-
-% % briefly go over one and done math
-% Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+% briefly go over one and done math
+Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 
-% In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
+In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
 In practice, the agent cannot take infinite samples.
@@
 Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
-% \begin{equation}
-% \Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
-% \label{eq:pr-choose-h1}
-% \end{equation}
-% and so the marginal probability of correctly choosing the MAP hypothesis is:
-% \begin{equation}
-% \Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
-% \label{eq:pr-correct}
-% \end{equation}
-% Then, the expected utility for a decision, given a threshold and the true probability, is:
-% \begin{equation}
-% \mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
-% \label{eq:expected-utility}
-% \end{equation}
-% where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.
+\begin{equation}
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+\label{eq:pr-choose-h1}
+\end{equation}
+and so the marginal probability of correctly choosing the MAP hypothesis is:
+\begin{equation}
+\Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
+\label{eq:pr-correct}
+\end{equation}
+Then, the expected utility for a decision, given a threshold and the true probability, is:
+\begin{equation}
+\mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
+\label{eq:expected-utility}
+\end{equation}
+where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.
 
-% We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}.
+We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}.
 Under the SPRT strategy, the probability of taking $N$ samples and then choosing $H_1$ is:
-% \begin{equation}
-% \Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-% \end{equation}
-% for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
-% \begin{equation}
-% \Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
-% \label{eq:pr-n}
-% \end{equation}
+\begin{equation}
+\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+\end{equation}
+for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+\begin{equation}
+\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
+\label{eq:pr-n}
+\end{equation}
 
-% \begin{figure*}[t]
-%     \begin{center}
-%         \includegraphics[width=\textwidth]{figures/thresholds.pdf}
-%         \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$.
-Black dots in the left two subplots show the optimal threshold $T^*$ and corresponding rate of return for each line.
-Left subplot: rates of return for a fixed time cost.
-Middle subplot: rates of return for a variable time cost.
-The distribution of $t_s$ was calculated empirically from simulations of a ball bouncing in a box (see Section \ref{sec:model}).
-Right subplot: difference in rates of return between the variable time cost and fixed time cost, approximated with Equation \ref{eq:ror-diff}.}
-%         \label{fig:rors}
-%     \end{center}
-% \end{figure*}
+Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
+\begin{equation}
+\mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
+\label{eq:ror-fixed}
+\end{equation}
+where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}.
+Finally, given this equation, we can compute the optimal threshold for an agent using the SPRT strategy:
+\begin{equation}
+T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
+\label{eq:optimal-threshold}
+\end{equation}
 
-% Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
-% \begin{equation}
-% \mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
-% \label{eq:ror-fixed}
-% \end{equation}
-% where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}.
-Finally, given this equation, we can compute the optimal threshold for an agent using the SPRT strategy:
-% \begin{equation}
-% T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
-% \label{eq:optimal-threshold}
-% \end{equation}
-
-% The rate of return and corresponding optimal thresholds for a variety of time costs, as computed by Equations \ref{eq:ror-fixed} and \ref{eq:optimal-threshold}, are shown in the left subplot of Figure \ref{fig:rors}.
-
-% \subsection{Variable time costs}
-
-% % convert one and done math to variable time costs
-% We now turn to the case where $t_s$ is variable and unknown. Let $t_N:=\sum_{i=1}^N t_s^{(i)}$ be the time it takes to draw $N$ samples. Then, the rate of return becomes:
-% \begin{equation}
-% \mathbb{E}[U/t\,|\,T,t_a]=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\mathbb{E}\left[\frac{1}{t_N+t_a}\right]\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
-% \label{eq:ror}
-% \end{equation}
-
-% Because $t_N$ is always positive, $(t_N+t_a)^{-1}$ is convex. Using Jensen's inequality:
-% \begin{equation}
-% \mathbb{E}\left[\frac{1}{t_N+t_a}\right]\geq \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a},
-% \end{equation}
-% where the right hand side of the inequality corresponds to the original formulation by \citeA{Vul:2014ba}.
-Thus, the rate of return when the time cost is unknown will always be greater than when it is known.
-Intuitively, this makes sense: when an agent knows less to begin with, the samples it takes will give it more information, ultimately resulting in a higher rate of return.
-
-% We can approximate the extent to which samples are more useful when the time cost is unknown by computing using a Taylor expansion around $N\cdot{}\mathbb{E}[t_s]$:
-% \begin{equation}
-% \mathbb{E}\left[\frac{1}{t_N+t_a}\right]\approx \frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}+\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}-\ldots{}
-% \end{equation}
-% Thus, the difference is approximated by:
-% \begin{equation}
-% \mathbb{E}\left[\frac{1}{t_s+t_a}\right]-\frac{1}{N\cdot{}\mathbb{E}[t_s]+t_a}\approx \frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}
-% \end{equation}
-% Plugging this back into Equation \ref{eq:ror}, we obtain the overall difference on the rate of return:
-% \begin{equation}
-% \Delta=\int_0^1 \sum_{N=T}^\infty \mathbb{E}[U\,|\,T,p]\cdot{}t_a\cdot{}\frac{\mathrm{Var}(t_N)}{(N\cdot{}\mathbb{E}[t_s]+t_a)^3}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p.
-% \label{eq:ror-diff}
-% \end{equation}
-
-% In practice, this difference is quite small.
-The middle subplot of Figure \ref{fig:rors} shows the rates of return using a variable time cost,\footnote{The times used for this plot were computed empirically using physical simulations of a ball boucing in a box.
-See Section \ref{sec:model} for details.} and the right subplot shows the difference computed from \ref{eq:ror-diff}.
-Even the largest difference, which occurs at $T=1$ and $t_a=\mathbb{E}[t_s]$, is so small that it does not change the value of $T^*$; the difference would need to be about 100 times greater in order to have an effect.
-Using different distributions for $\Pr[t_s]$ may have larger effects, but even these are not substantial.
-For example, using a uniform distribution can change $T^*$ from 0 to 1 for smaller cost ratios.
-
-% To summarize, we find that the introduction of uncertainty into the time cost has very little effect.
-The implication of this result is that even if it \emph{does} takes a variable amount of time to draw a sample, an agent need not bother taking its uncertainty into account: it can rely solely on its estimate of the average sample time to determine an optimal threshold.
-
-\section{Model}
-\label{sec:model}
+\section{Modeling physical predictions}
 
@@
 
-\section{Experiment 1}
+\TODO{talk about standard deviation adjustment}
+
+\TODO{talk about adjusting for the number of bounces -- or should this be in the results?}
+
+\section{Experiment 1: Replicating Smith and Vul (2014)}
 

### 2015-01-25 manuscript.tex
Reorder experiments 1 and 2

@@
 
-\section{Experiment 1: Replicating Smith and Vul (2014)}
-
-Experiment 1 was a replication of the ``pong'' experiment from \cite{Smith2012}, with the major difference being a new set of stimuli and that it was run on Amazon's Mechanical Turk rather than in the lab.
-
-\subsection{Participants}
-
-We recruited $N=60$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
-Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work.
-Additionally, we excluded $N=18$ participants from analysis for failing to catch the ball on more than one control trial, leaving a total of $N=42$ participants.
-
-\subsection{Stimuli}
-
-There were 48 unique stimuli, each consisting of an animation depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px, as well as a ``paddle'' that was fixed at some $x$-coordinate but moveable along the $y$-axis.
-Each animation had a duration of 0.775 seconds and depicted the ball moving in a particular direction with a velocity of 400px/s.
-Additionally, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
-
-Each animation was chosen such that were the ball to continue moving after the end of the animation, it would take exactly \TODO{} seconds to reach the $y$-coordinate of the paddle.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During this ``gap'' period in between the end of the animation and the ball reaching the $x$-coordinate of the paddle, the ball could bounce on the top, right, or bottom walls either 0, 1, or 2 times.
-
-In addition to the 48 experimental trials, there were seven instruction trials and eight control trials.
-The control trials were designed to be extremely easy and consisted of a ball heading straight towards the $x$-coordinate of the paddle (with a angle of incidence of either $90^\circ$ or close to $90^\circ$.
-Thus, participants saw a total of 63 trials throughout the experiment.
-
-\subsection{Procedure}
-
-The experiment was divided into two phases: the training phase, and the experimental phase.
-During the training phase, participants made judgments on the seven instruction trials in order to get used to the task.
-During the experimental phase, participants made judgments on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
-
-On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
-The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
-Participants were instructed to press the ``space'' key to begin the trial.
-Immediately upon pressing ``space'', the initial stimulus presentation began.
-As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
-As soon as the occluder appeared, a timer also appeared and begin counting down for \TODO{} seconds.
-During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.
-
-When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
-If the ball was on the paddle, then participants were told, ``You caught the ball!''.
-If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
-
-Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they caught the ball / the number of trials completed).
-
-\subsection{Results}
-
-\section{Experiment 2}
-
-\subsection{Participants}
-
-We recruited $N=328$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
-Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work.
-Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli).
-Additionally, we excluded $N=8$ participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of $N=320$ participants.
-
-\subsection{Stimuli}
-
-The stimuli were modified versions of those used in Experiment 1, with two main differences.
-First, instead of a moveable paddle, there was a wall with a fixed hole in it; the wall was at the same $x$-coordinate as the paddle.
-Second, while the initial stimulus presentation was identical, the stimuli in Experiment 2 had a second animation which was shown after participants responded.
-The feedback, which picked up immediately where the first animation left off, had a duration of 1.5 seconds.
-It depicted the ball either going into the hole or bouncing off the wall that contained the hole.
-
-There were 48 different initial animations (corresponding to the animations used in Experiment 1), and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
-The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
-The two hole sizes were 100px and 200px.
-
-In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
-Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
-
-The training trials and control trials were also the same as those used in Experiment 1, with feedback animations that were the same across participants.
-The feedback and hole sizes of the control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
+\section{Experiment 1}
 
@@
 
+\subsection{Participants}
+
+We recruited $N=328$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
+Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work.
+Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli).
+Additionally, we excluded $N=8$ participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of $N=320$ participants.
+
+\subsection{Stimuli}
+
+The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
+All stimuli consisted of two separate animations.
+The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
+The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole hitting the wall with the hole in it.
+In both animations, the ball had a velocity of 400px/s.
+Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+
+There were 48 different initial animations, and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
+The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
+The two hole sizes were 100px and 200px.
+
+In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
+Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
+
+In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
+The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
+Thus, participants saw a total of 63 trials throughout the experiment.
+
 \subsection{Procedure}
 
-The procedure was very similar to that in Experiment 1, and was identical up until the point that the occluder was shown.
-Instead of then having a fixed amount of time to answer, participants had unlimited time.
+The experiment was divided into two phases: the training phase, and the experimental phase.
+During the training phase, participants made judgments on the seven instruction trials in order to get used to the task.
+During the experimental phase, participants made judgements on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
+
+On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
+Participants were instructed to press the ``space'' key to begin the trial.
+Immediately upon pressing ``space'', the initial stimulus presentation began.
+As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
 Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' to respond in the affirmative, and `p' to respond in the negative.
@@
 After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
-Figure \ref{fig:experiment} shows a few frames from one of the experimental trials.
 
-\section{Results}
+Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they answered correctly / the number of trials completed).
+
+\subsection{Results}
 
@@
 
-\subsection{Responses}
+\subsubsection{Responses}
 
@@
 
-\subsection{Response times}
+\subsubsection{Response times}
 
@@
 
-\subsection{Relationship of responses to reaction time}
+\subsubsection{Relationship of responses to reaction time}
 
@@
 
-\subsection{Comparison to SPRT}
+\section{Experiment 2}
+
+Based on the results of Experiment 1, it is clear that people are spending longer on decisions that they are less confident about.
+In order to determine whether this could be explained by running mental simulations according to the SPRT strategy, we first needed to better characterize the parameters of people's mental simulations.
+Experiment 2 was designed as a conceptual replication of \citeA{Smith2012}, which would allow us to affirm that people are using mental simulation on these types of tasks, and if so, what the parameters of those simulations are.
+
+\subsection{Participants}
+
+We recruited $N=60$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
+Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work.
+Additionally, we excluded $N=18$ participants from analysis for failing to catch the ball on more than one control trial, leaving a total of $N=42$ participants.
+
+\subsection{Stimuli}
+
+The stimuli were modified versions of those used Experiment 1, with two major differences.
+First, instead of a wall with a hole in it, there was a paddle of length \TODO{}px that could move up and down the $y$-axis.
+Second, there was no feedback animation; instead, there was just a single feedback image corresponding to the last frame of the feedback animation.
+Because there was no feedback animation, there were only 48 stimuli (corresponding to the stimulus presentation animations from Experiment 1), plus the seven instruction trials and eight catch trials.
+
+\subsection{Procedure}
+
+Like Experiment 1, the experiment was divided into two phases: the training phase (consisting of seven trials), and the experimental phase (consisting of the 48 experimental trials, with the eight control trials evenly interspersed).
+On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
+The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
+Participants were instructed to press the ``space'' key to begin the trial.
+
+As in Experiment 1, immediately upon pressing ``space'', the initial stimulus presentation began, after which an occluder appeared.
+However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for \TODO{} seconds.
+During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
+If the ball was on the paddle, then participants were told, ``You caught the ball!''.
+If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
+
+Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they caught the ball / the number of trials completed).
+
+\subsection{Results}
+
+\TODO{summarize results showing that experimen 2 replicates Smith \& Vul (2014), and talk about fitting the model parameters}
+
+\section{Does SPRT explain human judgments?}
 
@@
 However, it turns out that the number of bounces is a much better predictor of people's response times than the model itself.
-At first glance, this seems like it could contradict the earlier result that unknown sampling times have little effect on the optimal number of samples to take.
-An alternate possibility is just that each bounce adds time to people's simulations above and beyond what it adds to the model simulations, but does not actually affect the number of samples they take.
-More investigation will be required to fully understand what is going on here.
+
+\TODO{explain SPRT results}
 
@@
 
-% In this paper, we asked the question: how should a sample-based agent act when it does not know how long it takes to draw a sample?
-To answer this question, we examined the optimal behavior of agents using the sequential probability ratio test (SPRT) with unknown time costs.
-Surprisingly, we found that the uncertainty introduced by the unknown sample times did not have a large effect: in most cases, the optimal threshold is the same regardless.
-
-% We additionally ran an experiment to see how well SPRT predicts human behavior on a task which enforces unknown time costs (as well as a range of underlying probabilities).
-While we did find a clear relationship between people's responses and their reaction time, analagous to the type of relationship that would be expected from a SPRT-like policy.
-However, our SPRT model was only a mediocre explanation of people's response times---less so than even the number of times the ball bounced.
-However, people did not see the number of times that the ball bounced; thus, the effect of the number of bounces is a fairly clear sign that they \emph{are} using simulations in some manner.
-Rather than a failing of the SPRT model, this may be a failure of our simulation-based model to appropriately account for additional simulation time from bounces.
-
-% However, based on our earlier result that unknown simulation time has little effect, even if we added extra simulation time per bounce to the model, it should not change the best-fitting threshold.
-Future work will investigate this claim further.
+\TODO{}
 

### 2015-01-25 manuscript.tex
More work on introduction

@@
 Imagine you are playing a video game---for example, Angry Birds or Desert Golf---in which you need to predict where an object will end up.
-Recent research in the domain of intuitive physics and mental simulation has suggested that people make predictions like these by running noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+How do you know where to aim, and how long do you spend thinking about each shot before you take it?
+Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
-For example, if people are running mental simulations, \emph{how many} simulations do they run?
-
-\TODO{something discussing that there are scenarios in which it's useful to take more simulations than others?}
+If people are running mental simulations, \emph{how many} simulations do they run?
 
 %% What's already been done
-Previous research by \citeA{Vul:2014ba} has asked, in the abstract, how many samples an agent should take before making a decision.
-Surprisingly, they found that to optimize success in the long run, it is not useful for sample-based agents to take more than a few samples.
-For example, suppose that there is a reward for correct answers and no penalty for incorrect answers, and that the agent can take ten samples in the time it takes to actually execute the action that reflects the decision.
-Then, the optimal number of samples that the agent should base their decision on is only one!
-While this is obviously suboptimal for each individual decision, over many decisions, this strategy trades off between the amount of time one can actually spend taking actions versus thinking.
+According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment---perhaps even just one.
+While taking a single sample is clearly suboptimal for each individual judgment, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
+Does this story also hold true for mental simulations?
+There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
 
-%% What's missing
-So far, the theoretical results from \citeA{Vul:2014ba} have largely not been applied to the domain of mental simulation, and lead to several questions regarding how people use their mental simulations.
-First, do people run multiple mental simulations?
-If so, do they run a fixed number of simulations, or vary the number of simulations based on the difficult?
-A supplementary analysis by \citeA{Battaglia2013} suggests that people do run multiple simulation.
-In their analysis, they attempted to determine the number of samples taken by people in several tasks concerning towers of building blocks.
-They did find a consistent story with \citeA{Vul:2014ba}: participants in their experiments seemed to use between three and seven samples per judgment.
-However, their analysis only concerned the variability of responses and did not take into account response time.
+A second question concerns the actual strategy used to take samples.
+Do people always take exactly the same number of samples for each decision, or do they vary the number of samples based on problem difficulty?
+While \citeA{Vul:2014ba} looked at a variety of strategies, they concluded that regardless of strategy, the optimal solution was still roughly the same: the agent should take very few samples.
+However, that does not make the choice of strategy irrelevant.
+If the strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times.
+Indeed, such variability can be observed in other types of decision-making tasks, and has been well-modeled by the \textit{sequential probability ratio test} \cite{wald1947sequential}, or SPRT \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}.
+In SPRT, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another hypothesis.
 
 %% What we're going to do and how we're going to do it
-In this paper, we investigate how many mental simulations people run when making decisions in a two alternative force choice task, analyzing both their response times and the variability of responses.
-\TODO{plan of the paper}
+In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics.
+Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
+And, if so, do they do so in a manner consistent with SPRT?
+To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
+We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole.
+We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
+
+%% What we're going to do and how we're going to do it
+The plan of the paper is as follows.
+First, we formalize our hypothesis for how people respond to the question, ``will the ball go through the hole?'', specifying both a simulation-based model as well as the SPRT strategy.
+Second, we describe two behavioral experiments, one in which we asked people to respond to the question of ``will the ball go through the hole?'', and a related experiment that we used to determine the parameters for the simulation-based model.
+Third, we describe the results of the experiments, and compare people's judgments and response times to those from the model.
+Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
 

### 2015-01-25 manuscript.tex
Update modeling section

@@
 
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/experiment.png}
+        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
+The left panel shows the initial screen presented to the participant.
+The middle panel shows the occluded ball, after observing the stimulus presentation.
+The faded gray line shows the path the ball took during the initial presentation.
+The right panel shows the final position of the ball, after observing the feedback.
+As in the middle panel, the faded gray line shows the path of the ball.}
+        \label{fig:experiment}
+    \end{center}
+\end{figure*}
+
 %% What we're going to do and how we're going to do it
@@
 
-\section{Modeling mental simulation with SPRT}
+\section{Modeling mental simulations}
 
-% SPRT
-\citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are.
-For example, consider the case where an agent must decide between two options.
-If they draw samples favoring one of the options with probability 0.95, then the agent can be fairly confident about which is the better option after only a few samples.
-In contrast, if the probability is 0.55, then the agent would need many samples to be confident about which option is better.
-Of course, the agent doesn't know what the probability is: that is the point of sampling.
-One strategy which addresses this issue is known as the \emph{sequential probability ratio test} \cite{wald1947sequential}, or SPRT, and has been used extensively to model a variety of decision making tasks in humans \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}.
-An agent using SPRT accumulates evidence for one option versus another, and stops sampling once a particular threshold of evidence has been reached.
-So, rather than optimizing for a fixed number of samples, the agent should optimize for the threshold.
+Consider the task in Figure \ref{fig:experiment}, in which people observe a blue ball moving around in a box, and are then asked, ``will the ball go through the hole?''.
+How do people make this type of judgment?
+We hypothesize that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
+In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.
 
-\TODO{probably don't actually need to go through all the math here, can just cite the appendix of one and done?}
+\subsection{The ``Noisy Newton'' hypothesis}
 
-% briefly go over one and done math
-Here, we consider the binary (or two-alternative forced choice) case, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
+This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+In particular, \citeA{Smith2012} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
+
+Specifically, \citeA{Smith2012} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
+In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through four parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$).
+
+\subsection{The SPRT strategy}
+
+In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 \end{equation}
-and so the marginal probability of correctly choosing the MAP hypothesis is:
-\begin{equation}
-\Pr[\mathrm{correct}]=\frac{p^{T+1}+(1-p)^{T+1}}{p^T+(1-p)^T}.
-\label{eq:pr-correct}
-\end{equation}
-Then, the expected utility for a decision, given a threshold and the true probability, is:
-\begin{equation}
-\mathbb{E}[U\,|\,T,p]=\Pr[\mathrm{correct}]\cdot{}u^{(+)}+(1-\Pr[\mathrm{correct}])\cdot{}u^{(-)},
-\label{eq:expected-utility}
-\end{equation}
-where $u^{(+)}$ is the utility for a correct answer and $u^{(-)}$ is the utility for an incorrect answer.
 
-We are interested not just in how much utility is gained from a single decision, but how much utility is gained from \emph{each additional sample}.
-Under the SPRT strategy, the probability of taking $N$ samples and then choosing $H_1$ is:
-\begin{equation}
-\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-\end{equation}
+Given the threshold, the probability of taking $N$ samples and then choosing $H_1$ is:
+\begin{multline}
+\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
+\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+\end{multline}
 for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
@@
 \end{equation}
-
-Putting together Equations \ref{eq:expected-utility} and \ref{eq:pr-n}, the expected rate or return, or utility over time, is:
+and so the expected number of samples for a particular decision is:
 \begin{equation}
-\mathbb{E}[U/t\,|\,T,t_a,t_s]=\int_0^1 \sum_{N=T}^\infty \frac{\mathbb{E}[U\,|\,T,p]\cdot{}t_a}{Nt_s+t_a}\Pr[N\,|\,T,p]\Pr[p]\ \mathrm{d}p,
-\label{eq:ror-fixed}
-\end{equation}
-where $t_s$ is the time it takes to draw a single sample, and $t_a$ is the time it takes to make a decision or execute an action \cite{Vul:2014ba}.
-Finally, given this equation, we can compute the optimal threshold for an agent using the SPRT strategy:
-\begin{equation}
-T^*=\mathrm{arg}\max_T \mathbb{E}[U/t\,|\,T,t_a,t_s].
-\label{eq:optimal-threshold}
+\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
 \end{equation}
 
-\section{Modeling physical predictions}
-
-% describe model from sources of uncertainty
-As discussed in the introduction, recent research suggests that people can reason about physical scenarios by running noisy physics simulations \cite<e.g.>{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-Here, we assume this to be the case, and use the model from \citeA{Smith2012}.
-Briefly, their model incorporates four sources of uncertainty into the physical simulations: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$).
-We fit these model parameters to human judgments in a related but separate task.
-Then, to determine the probability that the ball goes in the hole, we simulated $M=10000$ samples from the model.
+To combine the ``Noisy Newton'' hypothesis with the SPRT strategy, we needed to compute the probability, $p$, that the ball goes in the hole.
+To do this, we simulated $M=10000$ samples from the model.
 From these samples, we estimated a truncated normal distribution along the wall with the hole in it, and then computed the probability density lying within the region of the hole.
@@
 \section{Experiment 1}
-
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/experiment.png}
-        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
-The left panel shows the initial screen presented to the participant.
-The middle panel shows the occluded ball, after observing the stimulus presentation.
-The faded gray line shows the path the ball took during the initial presentation.
-The right panel shows the final position of the ball, after observing the feedback.
-As in the middle panel, the faded gray line shows the path of the ball.}
-        \label{fig:experiment}
-    \end{center}
-\end{figure*}
 

### 2015-01-26 manuscript.tex
Add some more stuff about model fitting

@@
 
-\TODO{talk about adjusting for the number of bounces -- or should this be in the results?}
+\section{Experiment 1}
 
-\section{Experiment 1}
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
+        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
+\TODO{fix legends} \TODO{right subplot shouldn't be speed vs.
+accuracy}}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
 
@@
 \subsection{Results}
-
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
-        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
-Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
 
@@
 
+In order to find the expected number of samples by SPRT, we need to know the probability of the ball going through the hole.
+We approximated this from the model fits to data from Experiment 2, with one adjustment.
+Specifically, it is not clear how many samples people would be taking to solve the paddle problem.
+To resolve this issue, we multiplied the standard deviation calculated from the model by a constant number, since statistics tells us:
+
+sd_prediction = sd_samples / sqrt(n_samples)
+
+This provides one of the two free parameters of the model.
+Given that adjustment, we can approximate the posterior belief over where the ball will go as a Gaussian, then trivially calculate the probability mass of that Gaussian that lies within each hole.
+From that, we can get the p(success) for each trial / hole combination
+
+Next, in order to calculate how many samples people will take on average according to SPRT, we need to know the number of samples for threshold - the second free parameter.
+But based on this threshold, we can just plug in Equation 12 from the one-and-done appendix, and get the average number of samples for each trial / hole combination.
+
+Finally, we can assume that there are some startup costs to simulation, but that each simulation sample should take an additional, constant amount of time.
+In which case, there should be a linear relationship between the SPRT sample estimates and the reaction times.
+So I did a grid search to find the set of sd_adj and T parameters that that would maximize the correlation between the two.
+
+The roughly best fitting parameters for this sets the sd adjustment at 0.7 and the SPRT threshold at 2.
+You might have one obvious complaint, which is that if people are taking multiple samples to solve the paddle task, then the sd adjustment should be positive (since it should be proportional to the square root of the number of samples), and it's not - in fact, positive adjustments make the fit awful.
+But I think what's actually going on is that the model overestimates the standard deviation, and interestingly, this is almost exactly by a factor of 1 / 0.7.
+So I think all that this adjustment is doing is correcting for the overestimation in the model.
+
 \section{Does SPRT explain human judgments?}
+
+As we found the number of bounces to be an extremely strong predictor of response time in Experiment 1, we modified our response time equation to incorporate the number of bounces, $B$:
+\begin{equation}
+t = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
+\end{equation}
+where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients. \TODO{figure}
 

### 2015-01-26 manuscript.tex
More work on modeling and fitting

--- 2015-01-25 manuscript.tex
@@
 
-%% What we're going to do and how we're going to do it
+%% Plan of the paper
 The plan of the paper is as follows.
-First, we formalize our hypothesis for how people respond to the question, ``will the ball go through the hole?'', specifying both a simulation-based model as well as the SPRT strategy.
-Second, we describe two behavioral experiments, one in which we asked people to respond to the question of ``will the ball go through the hole?'', and a related experiment that we used to determine the parameters for the simulation-based model.
-Third, we describe the results of the experiments, and compare people's judgments and response times to those from the model.
+First, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze people's accuracy and response times.
+Second, we formalize our hypothesis of how people make judgments in this experiment by specifying a combination of a simulation-based model with the SPRT strategy.
+Third, we describe a second experiment based on the experiment from \citeA{Smith2012} that was used to fit the parameters of our model.
+Then, we compare the model's predictions to people's responses in Experiment 1.
 Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
 
-\section{Modeling mental simulations}
+\section{Experiment 1: Will the ball go in the hole?}
 
-Consider the task in Figure \ref{fig:experiment}, in which people observe a blue ball moving around in a box, and are then asked, ``will the ball go through the hole?''.
-How do people make this type of judgment?
-We hypothesize that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
-In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
+        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
+\TODO{fix legends} \TODO{right subplot shouldn't be speed vs.
+accuracy}}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
 
-\subsection{The ``Noisy Newton'' hypothesis}
-
-There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
-This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
-Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-In particular, \citeA{Smith2012} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
-
-Specifically, \citeA{Smith2012} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
-In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through four parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), and uncertainty in the bounce angle ($\kappa_b$).
-
-\subsection{The SPRT strategy}
-
-In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
-The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
-Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
-
-In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
-In practice, the agent cannot take infinite samples.
-Thus, to determine when to stop sampling (i.e., what the value of $N$ is), we use the \emph{sequential probability ratio test} \cite{wald1947sequential}.
-When using a SPRT strategy, the agent accumulates $Y_N=\sum_{i=1}^N 2X_i-1$, and stops either when $Y_N=T$ or $Y_N=-T$, for some threshold number of samples $T$.
-Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
-\begin{equation}
-\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
-\label{eq:pr-choose-h1}
-\end{equation}
-
-Given the threshold, the probability of taking $N$ samples and then choosing $H_1$ is:
-\begin{multline}
-\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
-\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-\end{multline}
-for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
-\begin{equation}
-\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
-\label{eq:pr-n}
-\end{equation}
-and so the expected number of samples for a particular decision is:
-\begin{equation}
-\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
-\end{equation}
-
-To combine the ``Noisy Newton'' hypothesis with the SPRT strategy, we needed to compute the probability, $p$, that the ball goes in the hole.
-To do this, we simulated $M=10000$ samples from the model.
-From these samples, we estimated a truncated normal distribution along the wall with the hole in it, and then computed the probability density lying within the region of the hole.
-
-\TODO{talk about standard deviation adjustment}
-
-\TODO{talk about adjusting for the number of bounces -- or should this be in the results?}
-
-\section{Experiment 1}
+In order to determine whether people take multiples samples---and if they vary the number of samples---we designed an experiment in which people had to determine whether a ball would go into a hole (see Figure \ref{fig:experiment}).
+In particular, we designed the trials in this experiment such that some were harder than others.
 
@@
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
-        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
-Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
-
 \subsubsection{Responses}
@@
 
-As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear speed-accuracy tradeoff in participants responses and response times.
+As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times.
 In particular, participants were on average faster to respond on trials that they were more certain about, and slower to respond to trials that they were unsure about.
-This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ take much longer to make, because it takes longer to get to one threshold versus the other.
+This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it takes longer to get to one threshold versus the other.
+Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.
+
+\section{Modeling mental simulations}
+
+How do people make the types of judgments that they did in Experiment 1?
+We hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
+In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.
+
+\subsection{The ``Noisy Newton'' hypothesis}
+
+There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
+This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+In particular, \citeA{Smith2012} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
+
+Specifically, \citeA{Smith2012} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
+In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through five parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), uncertainty in the bounce angle ($\kappa_b$), and a ``center bias'' reflecting a bias for people to respond more towards the center of the $y$-axis ($\sigma_0$).
+
+\subsection{The SPRT strategy}
+
+In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
+Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
+
+In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
+In practice, the agent cannot take infinite samples.
+Thus, to determine when to stop sampling (i.e., what the value of $N$ is), we use the \emph{sequential probability ratio test} \cite{wald1947sequential}.
+When using a SPRT strategy, the agent accumulates $Y_N=\sum_{i=1}^N 2X_i-1$, and stops either when $Y_N=T$ or $Y_N=-T$, for some threshold number of samples $T$.
+
+\subsubsection{Modeling responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+\begin{equation}
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+\label{eq:pr-choose-h1}
+\end{equation}
+
+We can compute the probability, $p$, that the ball goes in the hole by running simulations from the model.
+
+\subsubsection{Modeling response times} Given the threshold, the probability of taking $N$ samples and then choosing $H_1$ is:
+\begin{multline}
+\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
+\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+\end{multline}
+for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+\begin{equation}
+\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
+\label{eq:pr-n}
+\end{equation}
+and so the expected number of samples for a particular decision is:
+\begin{equation}
+\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
+\end{equation}
+
+Assuming every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
+However, we found the number of bounces to be an extremely strong predictor of response time in Experiment 1: each additional bounce adds a constant amount of time to the response.
+To account for this, our final response time equation incorporated the number of bounces, $B$, as follows:
+\begin{equation}
+t = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
+\label{eq:rt}
+\end{equation}
+where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients. \TODO{figure}
 
@@
 
-\TODO{summarize results showing that experimen 2 replicates Smith \& Vul (2014), and talk about fitting the model parameters}
+\TODO{summarize results showing that experimen 2 replicates Smith \& Vul (2014)}
+
+We fit the model in two steps.
+First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2.
+\TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$.
+
+From the fitted model, we can estimate the probability that the ball goes in the hole ($p$), with one adjustment.
+Specifically, it is not clear how many samples people take to solve the paddle task.
+If they are taking a fixed number of samples, $M$,\footnote{We assume that in the paddle experiment, people are taking a fixed number of samples, as they only have a small, fixed amount of time to respond.} then we can estimate the true standard deviation of their simulations as $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
+As $M$ is unknown, we treat it as an additional free parameter in our model, adjusting the standard deviation of the model's responses by a fixed constant, $\sigma_{adj}=\sqrt{M}$.
+
+We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1.
+To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it.
+From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
+From this procedure, we found the best fitting parameters to be $\sigma_{adj}=0.7$ \TODO{what is the exact value?} and $T=2$.
+
+\TODO{what about fitting the coefficients from Equation \ref{eq:rt}?}
 
@@
 
-We fit participant responses and response times to the SPRT model with different values of $T$, and found that $T=2$ to have the best fit.
 Participant responses were well correlated with the SPRT model ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).

### 2015-01-26 manuscript.tex
Fix authors, citations

@@
 
-\author{{\large \bf Jessica B.~Hamrick (jhamrick@berkeley.edu)} \\
-  Department of Psychology \\
-  University of California, Berkeley
-  \AND {\large \bf Kevin A.~Smith (k2smith@ucsd.edu)} \\
-  Department of Psychology \\
-  University of California, San Diego
-  \AND {\large \bf Thomas L.~Griffiths (tom\_griffiths@berkeley.edu)} \\
-  Department of Psychology \\
-  University of California, Berkeley
-  \AND {\large \bf Edward Vul (evul@ucsd.edu)} \\
-  Department of Psychology \\
-  University of California, San Diego}
+\author{{\large \bf Jessica B.~Hamrick$^1$ (jhamrick@berkeley.edu),
+    Kevin A.~Smith$^2$ (k2smith@ucsd.edu),}\\
+    {\large \bf Thomas L.~Griffiths$^1$ (tom\_griffiths@berkeley.edu),
+      \& Edward Vul$^2$ (evul@ucsd.edu)}\\
+    $^1$University of California, Berkeley, Department of Psychology, Berkeley CA 94720 USA\\
+    $^2$University of California, San Diego, Department of Psychology, La Jolla, CA 92093 USA}
 
@@
 \begin{abstract}
-\TODO{}
+In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics.
+Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
+And, if so, do they do so in a manner consistent with SPRT?
+To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
+We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole.
+We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
+\TODO{this is identical to a paragraph in the introduction, and probably should be a little different at least}
 
@@
 How do you know where to aim, and how long do you spend thinking about each shot before you take it?
-Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
@@
 Second, we formalize our hypothesis of how people make judgments in this experiment by specifying a combination of a simulation-based model with the SPRT strategy.
-Third, we describe a second experiment based on the experiment from \citeA{Smith2012} that was used to fit the parameters of our model.
+Third, we describe a second experiment based on the experiment from \citeA{Smith:2013fc} that was used to fit the parameters of our model.
 Then, we compare the model's predictions to people's responses in Experiment 1.
@@
 This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
-Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith2012,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-In particular, \citeA{Smith2012} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
+Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
 
-Specifically, \citeA{Smith2012} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
+Specifically, \citeA{Smith:2013fc} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
 In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through five parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), uncertainty in the bounce angle ($\kappa_b$), and a ``center bias'' reflecting a bias for people to respond more towards the center of the $y$-axis ($\sigma_0$).
@@
 \end{equation}
-where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients. \TODO{figure}
+where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients.
 
@@
 In order to determine whether this could be explained by running mental simulations according to the SPRT strategy, we first needed to better characterize the parameters of people's mental simulations.
-Experiment 2 was designed as a conceptual replication of \citeA{Smith2012}, which would allow us to affirm that people are using mental simulation on these types of tasks, and if so, what the parameters of those simulations are.
+Experiment 2 was designed as a conceptual replication of \citeA{Smith:2013fc}, which would allow us to affirm that people are using mental simulation on these types of tasks, and if so, what the parameters of those simulations are.
 
@@
 From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
-From this procedure, we found the best fitting parameters to be $\sigma_{adj}=0.7$ \TODO{what is the exact value?} and $T=2$.
+From this procedure, we found the best fitting parameters to be $\sigma_{adj}=0.7$ \TODO{what is the exact value?} and $T=2$.\footnote{If $\sigma_{adj}=0.7$, then $M=0.49$.
+How could people be taking fewer than one sample?
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
 
@@
 However, it turns out that the number of bounces is a much better predictor of people's response times than the model itself.
+
+\TODO{figure}
 

### 2015-01-26 manuscript.tex
Silly discussion

@@
 
-\subsection{Results}
+\section{Results}
 
-\TODO{summarize results showing that experimen 2 replicates Smith \& Vul (2014)}
-
-We fit the model in two steps.
+We fit the model to people's responses in two steps.
 First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2.
 \TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$.
+With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \TODO{}, left subplot).
+In particular, we found a correlation of $r=0.94$ \TODO{cis} between the model's predicted means of where the ball would end up and people's average location of the paddle.
 
@@
 
-\section{Does SPRT explain human judgments?}
-
-Participant responses were well correlated with the SPRT model ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
-There was also a significant correlation with resonse time for the $T=2$ SPRT model ($r=0.35$, 95\% CI [0.27, 0.43]).
-However, it turns out that the number of bounces is a much better predictor of people's response times than the model itself.
-
-\TODO{figure}
-
-\TODO{explain SPRT results}
+Participant responses were well correlated with a SPRT model with $T=1$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
+There was also a significant correlation with resonse time for the $T=2$ SPRT model as computed with Equation \ref{eq:rt} ($r=0.71$, \TODO{95\% CI []}).
+Figure \TODO{} shows human responses as a function of the model's responses for $T=2$ (middle subplot) as well as human response times as a function of the model's response times (right subplot).
 
@@
 
-\TODO{}
+In this paper, we asked the question: how many simulations do people run?
+We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
+Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+
+The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about).
+This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT.
+To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT.
+In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model.
+Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
 

### 2015-01-28 manuscript.tex
Add new figures
Update figures
Update figures and results, resolve TODOs

@@
 \newcommand{\TODO}[1]{\textcolor{red}{[TODO: #1]}}
+
+\input{results/params.tex}
+\input{results/corrs.tex}
 
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
         \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
@@
 Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
-\TODO{fix legends} \TODO{right subplot shouldn't be speed vs.
-accuracy}}
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
         \label{fig:pct-vs-rt}
@@
 
-On average, participants were correct 76.1\% of the time ($N=17686$) and responded that the ball would go in the hole 52.8\% of the time ($N=17686$).
+On average, participants were correct 76.1\% of the time and responded that the ball would go in the hole 52.8\% of the time ($N=17686$).
 There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$).
@@
 The stimuli were modified versions of those used Experiment 1, with two major differences.
-First, instead of a wall with a hole in it, there was a paddle of length \TODO{}px that could move up and down the $y$-axis.
+First, instead of a wall with a hole in it, there was a paddle of length 100px that could move up and down the $y$-axis.
 Second, there was no feedback animation; instead, there was just a single feedback image corresponding to the last frame of the feedback animation.
@@
 As in Experiment 1, immediately upon pressing ``space'', the initial stimulus presentation began, after which an occluder appeared.
-However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for \TODO{} seconds.
+However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for 2 seconds.
 During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
@@
 
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/model_results.pdf}
+        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
+        \label{fig:model-results}
+    \end{center}
+\end{figure*}
+
 We fit the model to people's responses in two steps.
-First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2.
-\TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$.
-With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \TODO{}, left subplot).
-In particular, we found a correlation of $r=0.94$ \TODO{cis} between the model's predicted means of where the ball would end up and people's average location of the paddle.
+First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2 \cite<for details, see>{Smith:2013fc}.
+Using this procedure, we found the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}.
+With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \ref{fig:model-results}, left subplot).
+In particular, we found a correlation of \PaddleCorr{} between the model's predicted means of where the ball would end up and people's average location of the paddle.
 
@@
 From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
-From this procedure, we found the best fitting parameters to be $\sigma_{adj}=0.7$ \TODO{what is the exact value?} and $T=2$.\footnote{If $\sigma_{adj}=0.7$, then $M=0.49$.
+From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$.
 How could people be taking fewer than one sample?
@@
 
-\TODO{what about fitting the coefficients from Equation \ref{eq:rt}?}
+Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations.
+The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.
 
-Participant responses were well correlated with a SPRT model with $T=1$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]).
-There was also a significant correlation with resonse time for the $T=2$ SPRT model as computed with Equation \ref{eq:rt} ($r=0.71$, \TODO{95\% CI []}).
-Figure \TODO{} shows human responses as a function of the model's responses for $T=2$ (middle subplot) as well as human response times as a function of the model's response times (right subplot).
+Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}).
+There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}).
+Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
 

### 2015-01-28 manuscript.tex
Add empirical analyses

@@
 \input{results/corrs.tex}
+\input{results/hole_empirical_analysis.tex}
 
@@
 
-On average, participants were correct 76.1\% of the time and responded that the ball would go in the hole 52.8\% of the time ($N=17686$).
-There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$).
-Additionally, there was an interaction between feedback type and hole size ($\chi^2(3)=64.469, p<0.001$).
+On average, participants were correct \AvgCorrect{} of the time and responded that the ball would go in the hole \AvgResponse{} of the time (\ResponseN{}), excluding catch trials.
+There was a significant effect of feedback type on participants' responses (\ResponseHoleClass{}) as well as a significant effect of hole size (\ResponseHoleSize{}).
+Additionally, there was an interaction between feedback type and hole size (\ResponseFull{}).
 Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.
@@
 For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples.
-Participants had an average response time of $M=1310.9$ milliseconds ($SD=1296.6$ms).
-There were significant effects of both feedback type ($\chi^2(3)=63.611, p<0.001$) and hole size ($\chi^2(1)=8.9808, p<0.01$) on response time, as well as an interaction between feedback type and hole size ($\chi^2(3)=27.146, p<0.001$).
+Participants had an average response time of \AvgRT{} milliseconds (\StdRT{}ms), excluding catch trials.
+There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}).
 However, the hole size was only significant in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole.

### 2015-01-28 manuscript.tex
Add num participants analysis

@@
 \input{results/hole_empirical_analysis.tex}
+\input{results/num_participants.tex}
 
@@
 
-We recruited $N=328$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
+We recruited \HoleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
 Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work.
 Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli).
-Additionally, we excluded $N=8$ participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of $N=320$ participants.
+Additionally, we excluded \HoleNumFailed{} participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of \HoleNumOk{} participants.
 
@@
 
-We recruited $N=60$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
+We recruited \PaddleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
 Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work.
-Additionally, we excluded $N=18$ participants from analysis for failing to catch the ball on more than one control trial, leaving a total of $N=42$ participants.
+Additionally, we excluded \PaddleNumFailed{} participants from analysis for failing to catch the ball on more than one control trial, leaving a total of \PaddleNumOk{} participants.
 

### 2015-01-29 manuscript_ks.tex
KS edits to the manuscript

--- 2015-01-28 manuscript.tex
@@
 %% The question we're interested in: how many simulations do people take?
-Imagine you are playing a video game---for example, Angry Birds or Desert Golf---in which you need to predict where an object will end up.
+Imagine you are playing the game Angry Birds, where the goal is to launch a bird to knock down a tower.
+As you aim the bird, you need to predict where the bird will go to decide whether your shot will have the desired effect.
 How do you know where to aim, and how long do you spend thinking about each shot before you take it?
-Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+If you shoot the bird without spending time to consider where it will go, your shot will likely be far off.
+But on the other hand, if you spend too long aiming, over time your predictions will only get marginally better, and you eat into the time you have to play until your next meeting.
+Making this physical prediction requires a tradeoff that underlies many cognitive tasks: spending time and cognitive resources to increase confidence about what will transpire next, versus using that information to make decisions in the moment.
+In this paper, we study whether people efficiently trade off between information seeking and exploitation in a physical prediction task.
+
+Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton theory \cite{Sanborn2013}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
-If people are running mental simulations, \emph{how many} simulations do they run?
+If we are running mental simulations, how to we choose how many sample simulations to run?
 
 %% What's already been done
-According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment---perhaps even just one.
-While taking a single sample is clearly suboptimal for each individual judgment, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
+According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
+While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
 Does this story also hold true for mental simulations?
@@
 While \citeA{Vul:2014ba} looked at a variety of strategies, they concluded that regardless of strategy, the optimal solution was still roughly the same: the agent should take very few samples.
-However, that does not make the choice of strategy irrelevant.
-If the strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times.
-Indeed, such variability can be observed in other types of decision-making tasks, and has been well-modeled by the \textit{sequential probability ratio test} \cite{wald1947sequential}, or SPRT \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}.
-In SPRT, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another hypothesis.
+However, that does not make the choice of strategy irrelevant---certain strategies require different numbers of samples depending on how variable those samples are.
+For instance, using the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential}, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another.
+SPRT has been used to explain the variability in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, and so is a candidate mechanism for taking physical simulation samples.
+But if this strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times as more or fewer samples are taken.
 
@@
         \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
-The left panel shows the initial screen presented to the participant.
-The middle panel shows the occluded ball, after observing the stimulus presentation.
+\emph{Left:} the initial screen presented to the participant.
+\emph{Middle:}  the screen is occluded after observing the stimulus presentation.
 The faded gray line shows the path the ball took during the initial presentation.
-The right panel shows the final position of the ball, after observing the feedback.
+\emph{Right:} the final position of the ball, after observing the feedback.
 As in the middle panel, the faded gray line shows the path of the ball.}
@@
         \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
-Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
+        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
 The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
@@
 
-In order to determine whether people take multiples samples---and if they vary the number of samples---we designed an experiment in which people had to determine whether a ball would go into a hole (see Figure \ref{fig:experiment}).
-In particular, we designed the trials in this experiment such that some were harder than others.
+In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future---will a ball traveling through a computer screen go through a hole or not (see Figure \ref{fig:experiment})?
+In particular, we designed the trials such that some were harder than others.
+If people are using an SPRT sampling strategy, we would expect people to take longer (due to more sampling) when it was more ambiguous whether the ball would go through the hole.
 
@@
 
-\subsection{Stimuli}
-
-The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
-All stimuli consisted of two separate animations.
-The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole hitting the wall with the hole in it.
-In both animations, the ball had a velocity of 400px/s.
-Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
-
-There were 48 different initial animations, and for each of these intial animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
-The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
-The two hole sizes were 100px and 200px.
-
-In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
-Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
-
-In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
-The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
-Thus, participants saw a total of 63 trials throughout the experiment.
-
 \subsection{Procedure}
-
-The experiment was divided into two phases: the training phase, and the experimental phase.
-During the training phase, participants made judgments on the seven instruction trials in order to get used to the task.
-During the experimental phase, participants made judgements on the 48 experimental trials, presented in a random order, as well as the eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
 
@@
 Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response.
-Additionally, the gray occluder was removed, and participants were shown the feedback animation.
+Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball.
 After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
 
+During the experiment, participants made judgements on 48 experimental trials, presented in a random order, as well as eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
+In addition, participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
+
 Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they answered correctly / the number of trials completed).
+
+\subsection{Stimuli}
+
+The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
+All stimuli consisted of two separate animations.
+The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
+The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
+In both animations, the ball had a velocity of 400px/s.
+Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+
+There were 48 different initial animations, equally balanced by number of bounces during feedback (16 each for 0, 1, and 2 bounces).
+For each of these iniital animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
+The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
+The two hole sizes were 100px and 200px.
+
+In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
+Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
+This also ensured that the ball would go through the hole exactly half the time, so that participants would not be biased to respond either way based on statistical contingencies.
+
+In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
+The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
+Thus, participants saw a total of 63 trials throughout the experiment.
 
@@
 There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}).
-However, the hole size was only significant in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole.
+However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole.
 Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.
@@
 As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times.
-In particular, participants were on average faster to respond on trials that they were more certain about, and slower to respond to trials that they were unsure about.
-This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it takes longer to get to one threshold versus the other.
+In particular, on trials when there was more agreement amongst participants (the fraction saying 'in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
+This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
 Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.
+
+In addition, we found that response time is affected by the number of bounces during feedback; participants were slower to respond as more bounces were added.
+While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
+\TODO{Can we add statistics here?
+E.g., how much additional time, and something showing that this is above and beyond difficulty (intercept differences with quadratic fits)?} This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
+We will use this theory to further explain expected reaction times in \TODO{Add section here}.
 
@@
 
-\subsection{The ``Noisy Newton'' hypothesis}
+\subsection{The ``noisy Newton'' hypothesis}
 
 There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
-This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
 Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
+In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
 

### 2015-01-29 manuscript_ks.tex
More KS edits

@@
 
-Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton theory \cite{Sanborn2013}.
+Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton hypothesis \cite{Sanborn2013}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
@@
 
+In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole or miss it?
+What would be considered an `efficient' mechanism for taking samples will depend on the structure of the task, and there is a large body of literature discussing how a sample-based agent should make a decision between two choices.
+Specifically, we consider the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential} strategy, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins.
+SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information \TODO{Can we claim this?
+If so, we need a citation}.
+While SPRT is traditionally applied to simple binary decisions (e.g., go left or go right), this framework can be extended with probabilistic physical simulations to make binary decisions about our world.
+
+Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform these dichotomous tasks.
+Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses.
+If samples always provide the same information, this net evidence will reach the threshold quickly, and fewer samples will be taken.
+On the other hand, if samples are more evenly distributed, it will take more samples to reach the net evidence threshold.
+Thus if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
+
 %% What's already been done
-According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
+\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
 While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
 Does this story also hold true for mental simulations?
-There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
+There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
 
-A second question concerns the actual strategy used to take samples.
-Do people always take exactly the same number of samples for each decision, or do they vary the number of samples based on problem difficulty?
-While \citeA{Vul:2014ba} looked at a variety of strategies, they concluded that regardless of strategy, the optimal solution was still roughly the same: the agent should take very few samples.
-However, that does not make the choice of strategy irrelevant---certain strategies require different numbers of samples depending on how variable those samples are.
-For instance, using the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential}, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another.
-SPRT has been used to explain the variability in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, and so is a candidate mechanism for taking physical simulation samples.
-But if this strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times as more or fewer samples are taken.
+%% What we're going to do and how we're going to do it
+In this paper, we investigate whether peoples' behavior on a dichotomous physical prediction task can be explained by taking samples from a noisy Newton physical prediction model, where the number of samples taken is determined by SPRT.
+To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
+We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole.
+We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
+
+%% Plan of the paper
+Here we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling.
+Next we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times.
+We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed.
+Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
 
@@
 
-%% What we're going to do and how we're going to do it
-In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics.
-Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
-And, if so, do they do so in a manner consistent with SPRT?
-To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
-We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole.
-We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
+\section{The SPRT strategy}
 
-%% Plan of the paper
-The plan of the paper is as follows.
-First, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze people's accuracy and response times.
-Second, we formalize our hypothesis of how people make judgments in this experiment by specifying a combination of a simulation-based model with the SPRT strategy.
-Third, we describe a second experiment based on the experiment from \citeA{Smith:2013fc} that was used to fit the parameters of our model.
-Then, we compare the model's predictions to people's responses in Experiment 1.
-Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
+In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
+Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
 
-\section{Experiment 1: Will the ball go in the hole?}
+In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
+In practice, the agent cannot take infinite samples.
+Thus, to determine when to stop sampling (i.e., what the value of $N$ is), the agent continues to sample until the net evidence $Y_N$ reaches some threshold, either $Y_N=T$ to select in favor of $H_1$ or $Y_N=-T$ to select in favor of $H_0$.
+Net evidence is the sum of samples in favor of $H_1$ minus those in favor of $H_0$, or $Y_N=\sum_{i=1}^N 2X_i-1$.
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
-\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-\emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
+\subsection{Selecting responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+\begin{equation}
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+\label{eq:pr-choose-h1}
+\end{equation}
+
+\subsection{Expected number of samples} Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
+\begin{multline}
+\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
+\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+\end{multline}
+for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+\begin{equation}
+\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
+\label{eq:pr-n}
+\end{equation}
+and so the expected number of samples for a particular decision is:
+\begin{equation}
+\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
+\label{eq:expsamp}
+\end{equation}
+
+\section{Experiment}
 
@@
 
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
+        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
+
 \subsection{Results}
@@
 
-\section{Modeling mental simulations}
+\section{Modeling mental sampling}
 
-How do people make the types of judgments that they did in Experiment 1?
-We hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
-In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.
+How do people make the judgment that the ball will go through the hole?
+Following the success of SPRT, we hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}.
+In this section, we lay out the formalism for the simulation-based sampling model, consisting of a physical simulator and SPRT sampler.
 
-\subsection{The ``noisy Newton'' hypothesis}
+\subsection{The physical simulator}
 
@@
 
-\subsection{The SPRT strategy}
+Here, we used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events.
+Because the hole-choice experiment was performed online, we performed an online replication of that experiment to set model parameters (see the Appendix for details).
+Thus the physical prediction parameters were set independently of the performance on this experiment.
 
-In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
-The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$, and from these samples estimate $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
-Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
+\subsection{The SPRT sampler}
 
-In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
-In practice, the agent cannot take infinite samples.
-Thus, to determine when to stop sampling (i.e., what the value of $N$ is), we use the \emph{sequential probability ratio test} \cite{wald1947sequential}.
-When using a SPRT strategy, the agent accumulates $Y_N=\sum_{i=1}^N 2X_i-1$, and stops either when $Y_N=T$ or $Y_N=-T$, for some threshold number of samples $T$.
+The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall.
+However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
+Assuming they took on average $M$ samples, then the standard deviation we are estimating using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
+Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
 
-\subsubsection{Modeling responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
-\begin{equation}
-\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
-\label{eq:pr-choose-h1}
-\end{equation}
+If sampling is pulling from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
+So for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
 
-We can compute the probability, $p$, that the ball goes in the hole by running simulations from the model.
+\subsection{Modeling reaction time}
 
-\subsubsection{Modeling response times} Given the threshold, the probability of taking $N$ samples and then choosing $H_1$ is:
-\begin{multline}
-\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
-\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-\end{multline}
-for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
-\begin{equation}
-\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
-\label{eq:pr-n}
-\end{equation}
-and so the expected number of samples for a particular decision is:
-\begin{equation}
-\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
-\end{equation}
-
-Assuming every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
-However, we found the number of bounces to be an extremely strong predictor of response time in Experiment 1: each additional bounce adds a constant amount of time to the response.
+If we assume that every same takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
+However, we found the number of bounces to be an extremely strong predictor of response time: each additional bounce adds a constant amount of time to the response.
 To account for this, our final response time equation incorporated the number of bounces, $B$, as follows:
@@
 \end{equation}
-where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients.
 
-\section{Experiment 2}
+We could use the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
+We then fit all coefficients ($\beta_0$, $\beta_1$, and $\beta_2$, $\sigma_{adj}$, and $T$) to minimize sum squared error between modeled and observed reaction times.
+
+\subsection{Results}
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/model_results.pdf}
+        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
+        \label{fig:model-results}
+    \end{center}
+\end{figure*}
+
+The fitted model explained the data well, explaining both how accurate participants were for each trial (\HoleResponseCorr{}), and how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).
+
+\TODO{Can we show that accuracy correlation is better with SPRT softmaxing than strict accuracy to further suggest varying number of samples?}
+
+In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction.
+The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014b a}, see the Discussion).
+\TODO{KS ENDED EDITS HERE}
+
+We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1.
+To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it.
+From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
+From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$.
+How could people be taking fewer than one sample?
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
+
+Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations.
+The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.
+
+Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}).
+There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}).
+Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
+
+\section{Discussion}
+
+In this paper, we asked the question: how many simulations do people run?
+We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
+Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+
+The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about).
+This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT.
+To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT.
+In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model.
+Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
+
+\section{Appendix: Experiment for setting physical model parameters}
 
@@
 
-\section{Results}
-
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/model_results.pdf}
-        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
-        \label{fig:model-results}
-    \end{center}
-\end{figure*}
-
+\subsection{Results}
 We fit the model to people's responses in two steps.
@@
 
-We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1.
-To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it.
-From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
-From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$.
-How could people be taking fewer than one sample?
-We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
-
-Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations.
-The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.
-
-Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}).
-There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}).
-Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
-
-\section{Discussion}
-
-In this paper, we asked the question: how many simulations do people run?
-We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
-Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
-
-The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about).
-This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT.
-To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT.
-In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model.
-Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
-
 \bibliographystyle{apacite}

### 2015-01-29 manuscript.tex
Add Kevin's edits

@@
 %% The question we're interested in: how many simulations do people take?
-Imagine you are playing a video game---for example, Angry Birds or Desert Golf---in which you need to predict where an object will end up.
+Imagine you are playing the game Angry Birds, where the goal is to launch a bird to knock down a tower.
+As you aim the bird, you need to predict where the bird will go to decide whether your shot will have the desired effect.
 How do you know where to aim, and how long do you spend thinking about each shot before you take it?
-Recent research in the domain of intuitive physics and mental simulation has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+If you shoot the bird without spending time to consider where it will go, your shot will likely be far off.
+But on the other hand, if you spend too long aiming, over time your predictions will only get marginally better, and you eat into the time you have to play until your next meeting.
+Making this physical prediction requires a tradeoff that underlies many cognitive tasks: spending time and cognitive resources to increase confidence about what will transpire next, versus using that information to make decisions in the moment.
+In this paper, we study whether people efficiently trade off between information seeking and exploitation in a physical prediction task.
+
+Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton hypothesis \cite{Sanborn2013}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
-If people are running mental simulations, \emph{how many} simulations do they run?
+If we are running mental simulations, how to we choose how many sample simulations to run?
+
+In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole or miss it?
+What would be considered an `efficient' mechanism for taking samples will depend on the structure of the task, and there is a large body of literature discussing how a sample-based agent should make a decision between two choices.
+Specifically, we consider the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential} strategy, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins.
+SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information \TODO{Can we claim this?
+If so, we need a citation}.
+While SPRT is traditionally applied to simple binary decisions (e.g., go left or go right), this framework can be extended with probabilistic physical simulations to make binary decisions about our world.
+
+Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform these dichotomous tasks.
+Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses.
+If samples always provide the same information, this net evidence will reach the threshold quickly, and fewer samples will be taken.
+On the other hand, if samples are more evenly distributed, it will take more samples to reach the net evidence threshold.
+Thus if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
 
 %% What's already been done
-According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment---perhaps even just one.
-While taking a single sample is clearly suboptimal for each individual judgment, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
+\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
+While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
 Does this story also hold true for mental simulations?
-There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
-
-A second question concerns the actual strategy used to take samples.
-Do people always take exactly the same number of samples for each decision, or do they vary the number of samples based on problem difficulty?
-While \citeA{Vul:2014ba} looked at a variety of strategies, they concluded that regardless of strategy, the optimal solution was still roughly the same: the agent should take very few samples.
-However, that does not make the choice of strategy irrelevant.
-If the strategy tells the agent to vary the number of samples, then we should see variability in the agent's response times.
-Indeed, such variability can be observed in other types of decision-making tasks, and has been well-modeled by the \textit{sequential probability ratio test} \cite{wald1947sequential}, or SPRT \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}.
-In SPRT, the agent takes samples until it reaches a threshold number of samples in support of one hypothesis over another hypothesis.
-
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/experiment.png}
-        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
-The left panel shows the initial screen presented to the participant.
-The middle panel shows the occluded ball, after observing the stimulus presentation.
-The faded gray line shows the path the ball took during the initial presentation.
-The right panel shows the final position of the ball, after observing the feedback.
-As in the middle panel, the faded gray line shows the path of the ball.}
-        \label{fig:experiment}
-    \end{center}
-\end{figure*}
+There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
 
 %% What we're going to do and how we're going to do it
-In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics.
-Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
-And, if so, do they do so in a manner consistent with SPRT?
+In this paper, we investigate whether peoples' behavior on a dichotomous physical prediction task can be explained by taking samples from a noisy Newton physical prediction model, where the number of samples taken is determined by SPRT.
 To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
@@
 %% Plan of the paper
-The plan of the paper is as follows.
-First, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze people's accuracy and response times.
-Second, we formalize our hypothesis of how people make judgments in this experiment by specifying a combination of a simulation-based model with the SPRT strategy.
-Third, we describe a second experiment based on the experiment from \citeA{Smith:2013fc} that was used to fit the parameters of our model.
-Then, we compare the model's predictions to people's responses in Experiment 1.
+Here we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling.
+Next we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times.
+We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed.
 Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
-
-\section{Experiment 1: Will the ball go in the hole?}
 
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
-Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
-        \label{fig:pct-vs-rt}
+        \includegraphics[width=\textwidth]{figures/experiment.png}
+        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
+\emph{Left:} the initial screen presented to the participant.
+\emph{Middle:}  the screen is occluded after observing the stimulus presentation.
+The faded gray line shows the path the ball took during the initial presentation.
+\emph{Right:} the final position of the ball, after observing the feedback.
+As in the middle panel, the faded gray line shows the path of the ball.}
+        \label{fig:experiment}
     \end{center}
@@
 
-In order to determine whether people take multiples samples---and if they vary the number of samples---we designed an experiment in which people had to determine whether a ball would go into a hole (see Figure \ref{fig:experiment}).
-In particular, we designed the trials in this experiment such that some were harder than others.
+\section{The SPRT strategy}
+
+In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
+Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
+
+In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$.
+In practice, the agent cannot take infinite samples.
+Thus, to determine when to stop sampling (i.e., what the value of $N$ is), the agent continues to sample until the net evidence $Y_N$ reaches some threshold, either $Y_N=T$ to select in favor of $H_1$ or $Y_N=-T$ to select in favor of $H_0$.
+Net evidence is the sum of samples in favor of $H_1$ minus those in favor of $H_0$, or $Y_N=\sum_{i=1}^N 2X_i-1$.
+
+\subsection{Selecting responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+\begin{equation}
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+\label{eq:pr-choose-h1}
+\end{equation}
+
+\subsection{Expected number of samples} Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
+\begin{multline}
+\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
+\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
+\end{multline}
+for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+\begin{equation}
+\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
+\label{eq:pr-n}
+\end{equation}
+and so the expected number of samples for a particular decision is:
+\begin{equation}
+\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
+\label{eq:expsamp}
+\end{equation}
+
+\section{Experiment}
+
+In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future---will a ball traveling through a computer screen go through a hole or not (see Figure \ref{fig:experiment})?
+In particular, we designed the trials such that some were harder than others.
+If people are using an SPRT sampling strategy, we would expect people to take longer (due to more sampling) when it was more ambiguous whether the ball would go through the hole.
 
@@
 Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response.
-Additionally, the gray occluder was removed, and participants were shown the feedback animation.
+Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball.
 After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
 
+During the experiment, participants made judgements on 48 experimental trials, presented in a random order, as well as eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
+In addition, participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
+
 Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they answered correctly / the number of trials completed).
+
+\subsection{Stimuli}
+
+The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
+All stimuli consisted of two separate animations.
+The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
+The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
+In both animations, the ball had a velocity of 400px/s.
+Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+
+There were 48 different initial animations, equally balanced by number of bounces during feedback (16 each for 0, 1, and 2 bounces).
+For each of these iniital animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus.
+The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
+The two hole sizes were 100px and 200px.
+
+In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
+Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
+This also ensured that the ball would go through the hole exactly half the time, so that participants would not be biased to respond either way based on statistical contingencies.
+
+In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
+The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
+Thus, participants saw a total of 63 trials throughout the experiment.
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
+        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
 
@@
 As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times.
-In particular, participants were on average faster to respond on trials that they were more certain about, and slower to respond to trials that they were unsure about.
-This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it takes longer to get to one threshold versus the other.
+In particular, on trials when there was more agreement amongst participants (the fraction saying 'in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
+This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
 Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.
 
-\section{Modeling mental simulations}
+In addition, we found that response time is affected by the number of bounces during feedback; participants were slower to respond as more bounces were added.
+While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
+\TODO{Can we add statistics here?
+E.g., how much additional time, and something showing that this is above and beyond difficulty (intercept differences with quadratic fits)?} This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
+We will use this theory to further explain expected reaction times in \TODO{Add section here}.
 
-How do people make the types of judgments that they did in Experiment 1?
-We hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial according to the \textit{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
-In this section, we lay out the formalism for both the simulation-based model and the SPRT strategy.
+\section{Modeling mental sampling}
 
-\subsection{The ``Noisy Newton'' hypothesis}
+How do people make the judgment that the ball will go through the hole?
+Following the success of SPRT, we hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}.
+In this section, we lay out the formalism for the simulation-based sampling model, consisting of a physical simulator and SPRT sampler.
+
+\subsection{The physical simulator}
 
 There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
-This hypothesis, referred to as the ``Noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
 Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty and dynamics uncertainty.
+In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
 
@@
 \end{equation}
-where $\beta_0$, $\beta_1$, and $\beta_2$ are fitted coefficients.
 
-\section{Experiment 2}
+We could use the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
+We then fit all coefficients ($\beta_0$, $\beta_1$, and $\beta_2$, $\sigma_{adj}$, and $T$) to minimize sum squared error between modeled and observed reaction times.
+
+\subsection{Results}
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/model_results.pdf}
+        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
+        \label{fig:model-results}
+    \end{center}
+\end{figure*}
+
+The fitted model explained the data well, explaining both how accurate participants were for each trial (\HoleResponseCorr{}), and how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).
+
+\TODO{Can we show that accuracy correlation is better with SPRT softmaxing than strict accuracy to further suggest varying number of samples?}
+
+In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction.
+The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion).
+\TODO{KS ENDED EDITS HERE}
+
+We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1.
+To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it.
+From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
+From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$.
+How could people be taking fewer than one sample?
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
+
+Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations.
+The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.
+
+Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}).
+There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}).
+Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
+
+\section{Discussion}
+
+In this paper, we asked the question: how many simulations do people run?
+We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
+Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+
+The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about).
+This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT.
+To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT.
+In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model.
+Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
+
+\section{Appendix: Experiment for setting physical model parameters}
 

### 2015-01-30 manuscript.tex
Add node about arrow in experiment figure
Update results; add statistics about bounces

@@
 \emph{Left:} the initial screen presented to the participant.
+The arrow was not part of the actual stimuli; it has been added to reflect the animation that participants observed after pressing ``space''.
 \emph{Middle:}  the screen is occluded after observing the stimulus presentation.
@@
 For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples.
-Participants had an average response time of \AvgRT{} milliseconds (\StdRT{}ms), excluding catch trials.
+Participants had an average response time of \AvgRT{}, excluding catch trials.
 There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}).
@@
 
-In addition, we found that response time is affected by the number of bounces during feedback; participants were slower to respond as more bounces were added.
+In addition, we found that response time is affected by the number of bounces during feedback.
+Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with once bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
 While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
-\TODO{Can we add statistics here?
-E.g., how much additional time, and something showing that this is above and beyond difficulty (intercept differences with quadratic fits)?} This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
+For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
+From these fits, we see that the intercepts are significantly different across the different numbers of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one bounce, it was \InterceptOneBounces{}; and for two bounces, it was \InterceptTwoBounces{}.
+This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
 We will use this theory to further explain expected reaction times in \TODO{Add section here}.

### 2015-01-31 manuscript.tex
Add comparison of t=1 and t=2

@@
 Thus if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
-
-%% What's already been done
-\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
-While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
-Does this story also hold true for mental simulations?
-There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
 
@@
 \emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
+The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
         \label{fig:pct-vs-rt}
@@
 
-The fitted model explained the data well, explaining both how accurate participants were for each trial (\HoleResponseCorr{}), and how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).
-
-\TODO{Can we show that accuracy correlation is better with SPRT softmaxing than strict accuracy to further suggest varying number of samples?}
+The fitted model explained participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}), and was additionally able to account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).
+Even if the number of bounces is not included, the SPRT model with $T=2$ is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
+In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times beyond the number of bounces.
 
@@
 Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+
+\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
+While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
+Does this story also hold true for mental simulations?
+There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
 

### 2015-01-31 manuscript.tex
One sentence per line

@@
 
-Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015} - the noisy Newton hypothesis \cite{Sanborn2013}.
+Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}---the noisy Newton hypothesis \cite{Sanborn2013}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
-If we are running mental simulations, how to we choose how many sample simulations to run?
+If we are running mental simulations, how to we choose how many simulations to run?
 
-In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole or miss it?
-What would be considered an `efficient' mechanism for taking samples will depend on the structure of the task, and there is a large body of literature discussing how a sample-based agent should make a decision between two choices.
-Specifically, we consider the \textit{sequential probability ratio test}, or SPRT\cite{wald1947sequential} strategy, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins.
-SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information \TODO{Can we claim this?
-If so, we need a citation}.
+In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole, or miss it? 
+To model this task, we turn to the large body of literature discussing how a sample-based agent should make a decision between two choices. 
+Specifically, we consider the \textit{sequential probability ratio test}, or SPRT, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
+SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information.
+\TODO{Can we claim this? If so, we need a citation}
 While SPRT is traditionally applied to simple binary decisions (e.g., go left or go right), this framework can be extended with probabilistic physical simulations to make binary decisions about our world.
@@
 On the other hand, if samples are more evenly distributed, it will take more samples to reach the net evidence threshold. 
-Thus if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
+Thus, if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
 
@@
         \includegraphics[width=\textwidth]{figures/experiment.png}
-        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial.
+        \caption{\textbf{Example experimental trial.} 
+        Each panel shows a different part of the trial. 
         \emph{Left:} the initial screen presented to the participant.
@@
 
-\subsection{Selecting responses} Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+\subsection{Selecting responses}
+
+Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
 \begin{equation}
@@
 
-\subsection{Expected number of samples} Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
+\subsection{Expected number of samples}
+
+Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
 \begin{multline}
@@
 \end{multline}
-for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
+for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. 
+Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
 \begin{equation}
@@
 Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response.
-Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball.
+Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball
 After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
@@
 The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.} During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
+The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.
+\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.}
+During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
 In both animations, the ball had a velocity of 400px/s.
@@
 From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
-From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$.
-How could people be taking fewer than one sample?
+From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.
+\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
 We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
@@
 However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for 2 seconds.
-During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
+During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.
+When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
 If the ball was on the paddle, then participants were told, ``You caught the ball!''.
-If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
+If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.''
+Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
 
@@
 \subsection{Results}
+
 We fit the model to people's responses in two steps. 

### 2015-01-31 manuscript.tex
Work on introduction

@@
 
-Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}---the noisy Newton hypothesis \cite{Sanborn2013}.
+Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}---the ``noisy Newton'' hypothesis \cite{Sanborn2013}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
-If we are running mental simulations, how to we choose how many simulations to run?
+In particular, because the simulations are noisy, it may be beneficial to run multiple simulations in order to obtain more accurate predictions.
+So, if we are running mental simulations, how to we choose how many simulations to run?
 
-In this paper, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole, or miss it? 
-To model this task, we turn to the large body of literature discussing how a sample-based agent should make a decision between two choices. 
+To investigate how many simulations people run, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole, or miss it?
+To model this task, we combine the simulation mechanism of the ``noisy Newton'' hypothesis with a decision strategy for sample-based agents.
 Specifically, we consider the \textit{sequential probability ratio test}, or SPRT, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
-SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost / benefit tradeoff between sampling and exploiting information.
-\TODO{Can we claim this? If so, we need a citation}
-While SPRT is traditionally applied to simple binary decisions (e.g., go left or go right), this framework can be extended with probabilistic physical simulations to make binary decisions about our world.
+SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
 
-Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform these dichotomous tasks. 
+Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform two-alternative forced choice tasks. 
 Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses. 
-If samples always provide the same information, this net evidence will reach the threshold quickly, and fewer samples will be taken. 
-On the other hand, if samples are more evenly distributed, it will take more samples to reach the net evidence threshold. 
-Thus, if people are using an SPRT strategy, we would expect that reaction times on a dichotomous task will vary systematically with task difficulty.
-
-%% What we're going to do and how we're going to do it
-In this paper, we investigate whether peoples' behavior on a dichotomous physical prediction task can be explained by taking samples from a noisy Newton physical prediction model, where the number of samples taken is determined by SPRT.
-To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
-We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
-We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
+If every sample gives the same information (e.g., that the ball goes in the hole), then this net evidence will reach the threshold quickly, and fewer samples will be taken. 
+On the other hand, if the samples are more variable, it will take more samples to reach the net evidence threshold. 
+Thus, if people are relying on SPRT to decide how many simulations to run, we should observe faster response times for obvious cases (such as the ball hitting the wall far away from the hole) than for ambiguous ones (such as the ball just barely missing the hole).
 
 %% Plan of the paper
-Here we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. 
-Next we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
+In this paper, we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. 
+Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
 We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed. 
@@
 In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future---will a ball traveling through a computer screen go through a hole or not (see Figure \ref{fig:experiment})?
-In particular, we designed the trials such that some were harder than others. 
-If people are using an SPRT sampling strategy, we would expect people to take longer (due to more sampling) when it was more ambiguous whether the ball would go through the hole.
+Specifically, we desiged the trials such that some were harder than others by varying the margin by which the ball either missed or went through the hole.
+We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
 

### 2015-01-31 manuscript.tex
Update experiment and empirical results sections

@@
 
-In this paper, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. 
+We consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. 
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 Thus, to determine when to stop sampling (i.e., what the value of $N$ is), the agent continues to sample until the net evidence $Y_N$ reaches some threshold, either $Y_N=T$ to select in favor of $H_1$ or $Y_N=-T$ to select in favor of $H_0$.
-Net evidence is the sum of samples in favor of $H_1$ minus those in favor of $H_0$, or $Y_N=\sum_{i=1}^N 2X_i-1$.
+The net evidence is the sum of samples in favor of $H_1$ minus those in favor of $H_0$, or $Y_N=\sum_{i=1}^N 2X_i-1$.
 
@@
 
-In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future---will a ball traveling through a computer screen go through a hole or not (see Figure \ref{fig:experiment})?
-Specifically, we desiged the trials such that some were harder than others by varying the margin by which the ball either missed or went through the hole.
-We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future.
+Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
+We designed the trials such that some were harder than others by varying the margin by which the ball either missed or went through the hole.
+According to SPRT, people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
 
@@
 Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response.
-Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball
+Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball.
 After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
@@
 The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.
+The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.%
 \footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.}
@@
 There were 48 different initial animations, equally balanced by number of bounces during feedback (16 each for 0, 1, and 2 bounces). 
-For each of these iniital animations, there were four different types of feedback and two different hole sizes, giving a total of eight versions of each stimulus. 
-The four feedback types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
+For each of these initial animations, there were four different trial types and two different hole sizes, giving a total of eight versions of each stimulus. 
+The four trial types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
 The two hole sizes were 100px and 200px.
 
-In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Hole Type $\times$ Hole Size.
-Thus, each participant saw each initial animation exactly once, each hole type exactly 12 times, and each hole size exactly 24 times.
+In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
+Thus, each participant saw each initial animation exactly once, each trial type exactly 12 times, and each hole size exactly 24 times.
 This also ensured that the ball would go through the hole exactly half the time, so that participants would not be biased to respond either way based on statistical contingencies.
@@
         \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color).
+        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
 \emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-\emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.
+\emph{Right:} each point corresponds to a different stimulus, trial type, and hole size.
 The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
@@
 On average, participants were correct \AvgCorrect{} of the time and responded that the ball would go in the hole \AvgResponse{} of the time (\ResponseN{}), excluding catch trials.
-There was a significant effect of feedback type on participants' responses (\ResponseHoleClass{}) as well as a significant effect of hole size (\ResponseHoleSize{}).
-Additionally, there was an interaction between feedback type and hole size (\ResponseFull{}).
-Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.
+There was a significant effect of trial type on participants' responses (\ResponseHoleClass{}) as well as a significant effect of hole size (\ResponseHoleSize{}).
+Additionally, there was an interaction between trial type and hole size (\ResponseFull{}).
+For three out of the four trial types, there was a significant difference between responses for the two different hole sizes (for CI, \ResponseCIttest{}; for FI, \ResponseCIttest{}; and for FM, \ResponseFMttest{}), with the exception being the ``close miss'' (CM) trials (\ResponseCMttest{}).
+Figure \ref{fig:pct-vs-rt}A shows responses as a function of trial type and hole size.
 
@@
 Participants had an average response time of \AvgRT{}, excluding catch trials.
-There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}).
-However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole.
-Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.
+There were significant effects of both trial type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between trial type and hole size (\RTFull{}).
+However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials (\ResponsetimeFIttest{}), in which the ball went straight through the center of the hole (for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
+Figure \ref{fig:pct-vs-rt}B shows the response times as a function of trial type and hole size.
 
@@
 
-As shown in Figure \ref{fig:pct-vs-rt} (right subplot), we found a clear effect of certainty on people's response times.
-In particular, on trials when there was more agreement amongst participants (the fraction saying 'in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
+As shown in Figure \ref{fig:pct-vs-rt}C, we found a clear effect of certainty on people's response times.
+In particular, on trials when there was more agreement amongst participants (the fraction saying `in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
 This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
@@
 For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
-From these fits, we see that the intercepts are significantly different across the different numbers of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one bounce, it was \InterceptOneBounces{}; and for two bounces, it was \InterceptTwoBounces{}.
+From these fits, we see that the intercepts are significantly different across the different numbers of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one bounce, \InterceptOneBounces{}; and for two bounces, \InterceptTwoBounces{}.
 This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.

### 2015-01-31 manuscript.tex
Misc edits, cleanup, tightening

@@
 
+% space below "Figure 1: ...", but only for inline figures
+%\addtolength{\textfloatsep}{-0.1cm}
+
+\addtolength{\abovecaptionskip}{-0.25cm}
+\addtolength{\belowcaptionskip}{-0.5cm}
+
 \title{Think again?\\ Optimal mental simulation tracks problem difficulty}
@@
 Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
-And, if so, do they do so in a manner consistent with SPRT? 
 To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
@@
 We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-In brief, find that people's responses are well-predicted by a model of simulation, and that their response times are well-predicted by combining that model with a SPRT strategy.
-\TODO{this is identical to a paragraph in the introduction, and probably should be a little different at least}
+In brief, we find that judgments of whether the ball goes in and the corresponding response times are well-predicted by a model that combines noisy physical simulation with an optimal sampling strategy known as the \emph{sequential probability ratio test}.
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[t!]
     \begin{center}
@@
 
-\subsection{Selecting responses}
-
-Independent of the number of samples actually taken, the probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+The probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
 \begin{equation}
-\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T},
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T}
 \label{eq:pr-choose-h1}
 \end{equation}
-
-\subsection{Expected number of samples}
 
@@
 for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. 
-Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then:
-\begin{equation}
-\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p].
-\label{eq:pr-n}
-\end{equation}
-and so the expected number of samples for a particular decision is:
+Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then $\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p]$.
+So, the expected number of samples for a particular decision is:
 \begin{equation}
@@
 \end{equation}
+
+To summarize thus far, Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp} give us a formal hypothesis for what decisions people make, and how long they choose to make them. 
+In the next section, we present an experiment to empirically test this hypothesis.
 
@@
 In addition, participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
-
-Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they answered correctly / the number of trials completed).
 
@@
 \emph{Right:} each point corresponds to a different stimulus, trial type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
 The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
@@
 This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
-We will use this theory to further explain expected reaction times in \TODO{Add section here}.
 
@@
 
-How do people make the judgment that the ball will go through the hole?
-Following the success of SPRT, we hypothesized that they predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}.
-In this section, we lay out the formalism for the simulation-based sampling model, consisting of a physical simulator and SPRT sampler.
+In the previous section, we presented an experiment in which participants had to judge whether a ball would go through a hole.
+The results indicate a clear relationship between people's responses and response times---one which appears qualitatively similar to the one we would expect from SPRT.
+In this section, we flesh out our hypothesis that people predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}.
 
@@
 Because the hole-choice experiment was performed online, we performed an online replication of that experiment to set model parameters (see the Appendix for details).
-Thus the physical prediction parameters were set independently of the performance on this experiment.
+Thus, the physical prediction parameters were set independently of the results of the experiment in this paper.
 
@@
 
+\begin{figure}[t]
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/model_rt_results.pdf}
+        \caption{\textbf{Model vs.
+human response times.} Each point corresponds to a different stimulus, trial type, and hole size; color and shape indicate the number of times the ball bounced during feedback.
+The $x$-axis is the fitted model response times, and the $y$-axis is the logarithmic mean response times of participants.}
+        \label{fig:model-rt-results}
+    \end{center}
+\end{figure}
+
 The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall.
 However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
-Assuming they took on average $M$ samples, then the standard deviation we are estimating using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
+Assuming they took on average $M$ samples, then the standard deviation we estimate using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
 Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
 
-If sampling is pulling from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
-So for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
+If sampling pulls from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
+So, for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
 
@@
 
-If we assume that every same takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
+If we assume that every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
 However, we found the number of bounces to be an extremely strong predictor of response time: each additional bounce adds a constant amount of time to the response.
@@
 \begin{equation}
-t = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
+RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
 \label{eq:rt}
@@
 
-We could use the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
-We then fit all coefficients ($\beta_0$, $\beta_1$, and $\beta_2$, $\sigma_{adj}$, and $T$) to minimize sum squared error between modeled and observed reaction times.
+To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
+We then fit all parameters ($T$, $\sigma_{adj}$, $\beta_0$, $\beta_1$, and $\beta_2$) to minimize sum squared error between modeled and observed reaction times, using $n=10000$ samples from the physical simulation model.
+The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.} \betazero{}, \betaone{}, and \betatwo{}.
 
@@
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/model_results.pdf}
-        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
-        \label{fig:model-results}
-    \end{center}
-\end{figure*}
-
-The fitted model explained participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}), and was additionally able to account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).
-Even if the number of bounces is not included, the SPRT model with $T=2$ is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
+The fitted model explains participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-response-results}), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-rt-results}).
+Even if the number of bounces is not included, the SPRT model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
 In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times beyond the number of bounces.
-
-In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction.
-The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion).
-\TODO{KS ENDED EDITS HERE}
-
-We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1.
-To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it.
-From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole.
-From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.
-\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
-We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}
-
-Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations.
-The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.
-
-Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}).
-There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}).
-Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
 
@@
 Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+
+In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction.
+The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion).
+
+\begin{figure}[t]
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/model_response_results.pdf}
+        \caption{\textbf{Model vs.
+human judgments.} Each point corresponds to a different stimulus, trial type, and hole size.
+The $x$-axis is the probability the model says the ball will go in the hole, and the $y$-axis is the proportion of participants saying the ball will go in the hole.}
+        \label{fig:model-response-results}
+    \end{center}
+\end{figure}
 
@@
 
-\section{Appendix: Experiment for setting physical model parameters}
+\section{Appendix}
 
-Based on the results of Experiment 1, it is clear that people are spending longer on decisions that they are less confident about.
-In order to determine whether this could be explained by running mental simulations according to the SPRT strategy, we first needed to better characterize the parameters of people's mental simulations.
-Experiment 2 was designed as a conceptual replication of \citeA{Smith:2013fc}, which would allow us to affirm that people are using mental simulation on these types of tasks, and if so, what the parameters of those simulations are.
+In order to fit the parameters for the physical simulation model, we ran an online replication of the experiment from \citeA{Smith:2013fc}.
 
@@
 The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
-Participants were instructed to press the ``space'' key to begin the trial.
+Participants were instructed to press ``space'' to begin the trial.
 
@@
 
-Throughout the experiment, participants saw two counters: one showing their total progress (the number of trials completed / total trials), and their score (the number of times they caught the ball / the number of trials completed).
-
 \subsection{Results}
 
-We fit the model to people's responses in two steps. 
-First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2 \cite<for details, see>{Smith:2013fc}. 
-Using this procedure, we found the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}. 
-With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \ref{fig:model-results}, left subplot).
+We fit the model parameters of $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses \cite<for details, see>{Smith:2013fc}, finding the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}.
+With these parameters, we found very similar results to those from \citeA{Smith:2013fc}.
 In particular, we found a correlation of \PaddleCorr{} between the model's predicted means of where the ball would end up and people's average location of the paddle.
-
-From the fitted model, we can estimate the probability that the ball goes in the hole ($p$), with one adjustment. 
-Specifically, it is not clear how many samples people take to solve the paddle task.
-If they are taking a fixed number of samples, $M$,\footnote{We assume that in the paddle experiment, people are taking a fixed number of samples, as they only have a small, fixed amount of time to respond.} then we can estimate the true standard deviation of their simulations as $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
-As $M$ is unknown, we treat it as an additional free parameter in our model, adjusting the standard deviation of the model's responses by a fixed constant, $\sigma_{adj}=\sqrt{M}$.
 

### 2015-01-31 manuscript.tex
Misc small edits, make abstract a todo

@@
 \begin{abstract}
-In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics. 
+\TODO{In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics. 
 Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
@@
 We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
-We hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-In brief, we find that judgments of whether the ball goes in and the corresponding response times are well-predicted by a model that combines noisy physical simulation with an optimal sampling strategy known as the \emph{sequential probability ratio test}.
+Following the predictions of the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential}, we hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+In brief, we find that judgments of whether the ball goes in and the corresponding response times are well-predicted by a model that combines noisy physical simulation with SPRT.}
 
@@
 
-In the best possible case, the agent takes infinite samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. 
-In practice, the agent cannot take infinite samples. 
+In the best possible case, the agent takes infinitely many samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. 
+In practice, the agent cannot take infinitely many samples. 
 Thus, to determine when to stop sampling (i.e., what the value of $N$ is), the agent continues to sample until the net evidence $Y_N$ reaches some threshold, either $Y_N=T$ to select in favor of $H_1$ or $Y_N=-T$ to select in favor of $H_0$.

### 2015-02-01 manuscript.tex
Add keywords
Merge modeling sections

@@
 \textbf{Keywords:} 
-add your choice of indexing terms or keywords; kindly use a
-semicolon; between each term
+mental simulation; intuitive physics; SPRT; computational modeling
 \end{abstract}
@@
 
-Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform two-alternative forced choice tasks. 
-Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses. 
-If every sample gives the same information (e.g., that the ball goes in the hole), then this net evidence will reach the threshold quickly, and fewer samples will be taken. 
-On the other hand, if the samples are more variable, it will take more samples to reach the net evidence threshold. 
-Thus, if people are relying on SPRT to decide how many simulations to run, we should observe faster response times for obvious cases (such as the ball hitting the wall far away from the hole) than for ambiguous ones (such as the ball just barely missing the hole).
-
-%% Plan of the paper
-In this paper, we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. 
-Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
-We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed. 
-Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
-
 \begin{figure*}[t!]
@@
 
-\section{The SPRT strategy}
+Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform two-alternative forced choice tasks. 
+Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses. 
+If every sample gives the same information (e.g., that the ball goes in the hole), then this net evidence will reach the threshold quickly, and fewer samples will be taken. 
+On the other hand, if the samples are more variable, it will take more samples to reach the net evidence threshold. 
+Thus, if people are relying on SPRT to decide how many simulations to run, we should observe faster response times for obvious cases (such as the ball hitting the wall far away from the hole) than for ambiguous ones (such as the ball just barely missing the hole).
 
-We consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. 
+%% Plan of the paper
+In this paper, we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. 
+Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
+We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed. 
+Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
+
+\section{Making decisions from mental simulations}
+
+Consider the task in Figure \ref{fig:experiment}, in which people observe a ball moving inside a box, and must predict whether it will go through a hole or not. How do people solve this problem?
+In this section, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or SPRT.
+
+\subsection{Modeling physical simulation}
+
+There is a growing body of evidence that people reason about physical scenes like the one in Figure \ref{fig:experiment} by running noisy simulations.
+This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+
+\citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
+Specifically, \citeA{Smith:2013fc} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
+In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through five parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), uncertainty in the bounce angle ($\kappa_b$), and a ``center bias'' reflecting a bias for people to respond more towards the center of the $y$-axis ($\sigma_0$).
+
+Here, we used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events.
+Because the experiment in Figure \ref{fig:experiment} (see Experiment) was performed online, we additionally performed an online replication of the experiment from \citeA{Smith:2013fc} to set model parameters (see the Appendix for details).
+Thus, the physical prediction parameters were set independently of the results of the experiment in this paper.
+
+The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall.
+However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
+Assuming they took on average $M$ samples, then the standard deviation we estimate using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
+Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
+
+If sampling pulls from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
+So, for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
+
+\subsection{The SPRT strategy}
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
+        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
+\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{Right:} each point corresponds to a different stimulus, trial type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
+The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
+
+If people are running simulations to reason about physical scenes, then a natural question is: how many simulations do they run?
+Because the simulations are noisy, it might be benefial to run multiple simulations in order to get a better estimate of the outcome.
+However, each simulation comes with a time cost.
+To optimize this speed-accuracy tradeoff, we apply the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential} to the samples drawn from the physical simulation.
+By combining these two models, we can make predictions both for people's judgments, and how long they take to make those judgments.
+
+Formally, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$. 
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 
-\section{Experiment}
+\section{Experiment: Will the ball go in the hole?}
 
@@
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
-\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-\emph{Right:} each point corresponds to a different stimulus, trial type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
-The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
-
 \subsection{Results}
@@
 
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/model_results.pdf}
+        \caption{\textbf{Model vs.
+human comparison.} In both plots, each point corresponds to a different stimulus, trial type, and hole size.
+Dashed lines indicate perfect correspondence between model and people.
+\emph{Left}: The $x$-axis is the probability the model says the ball will go in the hole, and the $y$-axis is the proportion of participants saying the ball will go in the hole.
+\emph{Right}: Color and shape indicate the number of times the ball bounced during feedback.
+The $x$-axis is the model response times, and the $y$-axis is the logarithmic mean response times of participants.}
+        \label{fig:model-results}
+    \end{center}
+\end{figure*}
+
 As shown in Figure \ref{fig:pct-vs-rt}C, we found a clear effect of certainty on people's response times.
@@
 
-\section{Modeling mental sampling}
-
-In the previous section, we presented an experiment in which participants had to judge whether a ball would go through a hole.
-The results indicate a clear relationship between people's responses and response times---one which appears qualitatively similar to the one we would expect from SPRT.
-In this section, we flesh out our hypothesis that people predict where the ball will go by running noisy physical simulations, and that they run a variable number of simulations on each trial based on SPRT principles \cite{wald1947sequential}.
-
-\subsection{The physical simulator}
-
-There is a growing body of evidence that people reason about physical scenes by running noisy simulations.
-This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
-Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-In particular, \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
-
-Specifically, \citeA{Smith:2013fc} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
-In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through five parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), uncertainty in the bounce angle ($\kappa_b$), and a ``center bias'' reflecting a bias for people to respond more towards the center of the $y$-axis ($\sigma_0$).
-
-Here, we used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events.
-Because the hole-choice experiment was performed online, we performed an online replication of that experiment to set model parameters (see the Appendix for details).
-Thus, the physical prediction parameters were set independently of the results of the experiment in this paper.
-
-\subsection{The SPRT sampler}
-
-\begin{figure}[t]
-    \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/model_rt_results.pdf}
-        \caption{\textbf{Model vs.
-human response times.} Each point corresponds to a different stimulus, trial type, and hole size; color and shape indicate the number of times the ball bounced during feedback.
-The $x$-axis is the fitted model response times, and the $y$-axis is the logarithmic mean response times of participants.}
-        \label{fig:model-rt-results}
-    \end{center}
-\end{figure}
-
-The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall.
-However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
-Assuming they took on average $M$ samples, then the standard deviation we estimate using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
-Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
-
-If sampling pulls from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
-So, for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
-
-\subsection{Modeling reaction time}
+\subsubsection{Model comparison}
 
@@
 
-\subsection{Results}
-
-The fitted model explains participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-response-results}), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-rt-results}).
+The fitted model explains participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
 Even if the number of bounces is not included, the SPRT model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
@@
 The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion).
-
-\begin{figure}[t]
-    \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/model_response_results.pdf}
-        \caption{\textbf{Model vs.
-human judgments.} Each point corresponds to a different stimulus, trial type, and hole size.
-The $x$-axis is the probability the model says the ball will go in the hole, and the $y$-axis is the proportion of participants saying the ball will go in the hole.}
-        \label{fig:model-response-results}
-    \end{center}
-\end{figure}
 
@@
 
-\subsection{Participants}
+\subsubsection{Participants}
 
@@
 
-\subsection{Stimuli}
+\subsubsection{Stimuli}
 
@@
 
-\subsection{Procedure}
+\subsubsection{Procedure}
 
@@
 
-\subsection{Results}
+\subsubsection{Results}
 

### 2015-02-01 manuscript.tex
Work on introduction

@@
 %% The question we're interested in: how many simulations do people take?
-Imagine you are playing the game Angry Birds, where the goal is to launch a bird to knock down a tower. 
-As you aim the bird, you need to predict where the bird will go to decide whether your shot will have the desired effect. 
+How does the mind best make use of its computational resources?
+For example, imagine you are playing a game of Angry Birds, where the goal is to launch a bird to knock down a tower. 
+As you aim, you need to predict where the bird will go to decide whether your shot will have the desired effect. 
 How do you know where to aim, and how long do you spend thinking about each shot before you take it? 
-If you shoot the bird without spending time to consider where it will go, your shot will likely be far off. 
-But on the other hand, if you spend too long aiming, over time your predictions will only get marginally better, and you eat into the time you have to play until your next meeting. 
-Making this physical prediction requires a tradeoff that underlies many cognitive tasks: spending time and cognitive resources to increase confidence about what will transpire next, versus using that information to make decisions in the moment.
-In this paper, we study whether people efficiently trade off between information seeking and exploitation in a physical prediction task.
+More generally, if an agent has the ability to make predictions about scenarios such as these, how long do they spend making predictions versus taking actions?
 
-Recent research in the domain of physical reasoning has revealed that people make predictions like these by running noisy physical simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}---the ``noisy Newton'' hypothesis \cite{Sanborn2013}.
+Recent research in the domain of physical reasoning has revealed that people make predictions about physical scenes---such as those found in Angry Birds---by running noisy physical simulations \cite{Sanborn2013,Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
@@
 To investigate how many simulations people run, we focus on a dichotomous prediction task---will a ball in motion on a computer screen go through a hole, or miss it?
-To model this task, we combine the simulation mechanism of the ``noisy Newton'' hypothesis with a decision strategy for sample-based agents.
+To model this task, we combine a mechanism of noisy physical simulation with a decision strategy for sample-based agents.
 Specifically, we consider the \textit{sequential probability ratio test}, or SPRT, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
 SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
+Importantly, the SPRT strategy predicts that people need to take more samples---and thus also will take a longer time to respond---on more difficult tasks.
 
@@
 
-Crucially, the SPRT framework allows us to make testable predictions about how quickly people perform two-alternative forced choice tasks. 
-Because it involves sampling until the net evidence reaches a threshold, the number of samples will depend on the variability of the hypotheses. 
-If every sample gives the same information (e.g., that the ball goes in the hole), then this net evidence will reach the threshold quickly, and fewer samples will be taken. 
-On the other hand, if the samples are more variable, it will take more samples to reach the net evidence threshold. 
-Thus, if people are relying on SPRT to decide how many simulations to run, we should observe faster response times for obvious cases (such as the ball hitting the wall far away from the hole) than for ambiguous ones (such as the ball just barely missing the hole).
-
 %% Plan of the paper
-In this paper, we first explain the SPRT framework and how it makes predictions about the number of samples required based on variability in sampling. 
+Drawing on the results from both physical simulation and decision-making, we hypothesize that people make predictions by running mental simulations, and that they vary the number of simulations based on the difficulty of the task.
+In this paper, we first formalize our model, combining the physical prediction model from \citeA{Smith:2013fc} with the SPRT decision strategy. 
 Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
-We then demonstrate that combining the physical prediction model from \citeA{Smith:2013fc} with SPRT can explain the empirical pattern of accuracy and response times we observed. 
-Finally, we discuss the implications of our results on the broader, underlying question: how do people use mental simulation?
+We then demonstrate that our model can explain the empirical pattern of responses and response times we observed. 
+Finally, we discuss the implications of our results on the broader, underlying question: how do people optimally make use of mental simulations?
 
@@
 
-Consider the task in Figure \ref{fig:experiment}, in which people observe a ball moving inside a box, and must predict whether it will go through a hole or not. How do people solve this problem?
+Consider the task in Figure \ref{fig:experiment}, in which people observe a ball moving inside a box, and must predict whether it will go through a hole or not.
+How do people solve this problem?
 In this section, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or SPRT.
@@
 There is a growing body of evidence that people reason about physical scenes like the one in Figure \ref{fig:experiment} by running noisy simulations.
-This hypothesis, referred to as the ``noisy Newton'' hypothesis, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
+This hypothesis, referred to as the ``noisy Newton'' hypothesis \cite{Sanborn2013}, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
 Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
@@
 
-In this paper, we asked the question: how many simulations do people run?
-We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
+In this paper, we asked the question: how do people make best use of their mental simulations?
+Specifically, how do people determine how many simulations to run?
+We hypothesized that people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
 Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.

### 2015-02-01 manuscript.tex
Work on discussion

@@
 However, we found the number of bounces to be an extremely strong predictor of response time: each additional bounce adds a constant amount of time to the response.
-To account for this, our final response time equation incorporated the number of bounces, $B$, as follows:
-\begin{equation}
-RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]
-\label{eq:rt}
-\end{equation}
+To account for this, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
 
@@
 
-In this paper, we asked the question: how do people make best use of their mental simulations?
-Specifically, how do people determine how many simulations to run?
-We hypothesized that people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others.
-Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
+In this paper, we asked the question: do people optimally use mental simulations?
+We hypothesized that people use noisy physical simulations to predict whether a ball would go in a hole, and that they vary the number of simulations in order to exploit the fact that some judgments are easier to make than others.
+Specifically, if people are making the best use of their mental simulations, then they should take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
 
-In addition, the parameters of the sampling process can further inform us about how people accomplish physical prediction.
-The best fitting threshold was \threshold{}, suggesting people gather little information before making a decision (in line with the theory of \cite{Vul:2014ba}, see the Discussion).
+The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on more difficult trials.
+Comparing people's responses and response times to those of the model, we found an extremely strong fit.
+This provides evidence that people not only rely approximate physical simulations, but that they optimally vary the number of simulations that they run according to SPRT.
 
-\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one.
-While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments.
-Does this story also hold true for mental simulations?
-There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
+If SPRT is the optimal strategy, then what is the optimal threshold?
+We found the best fitting SPRT threshold to be \threshold{}, which is consistent with previous research.
+According to \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples.
+While taking a small number of samples clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, this strategy maximizes expected utility across a large number of judgments.
+There has been some evidence that this story also holds true for mental simulations.
+For example, \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
+However, this paper is the first to provide evidence not only that people use a small number of simulations, but that they systematically vary the number of simulations.
 
-The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about).
-This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT.
-To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT.
-In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model.
-Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
+Mental simulation is a powerful and flexible tool, as it offers us a way to make predictions about scenarios that have not yet come to pass, or which may never come to pass.
+In this work, we demonstrated that when people use mental simulation, they are sensitive to the difficulty of the task and accordingly adjust how many simulations they run.
+This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but specifically \emph{how} they use it.
+While there are still many questions left unanswered---e.g., how do people use simulations in non-binary tasks?---this work brings us one step closer to understanding of how mental simulation is used.
 

### 2015-02-01 manuscript.tex
Abstract, fix typos, tightening

@@
 \begin{abstract}
-\TODO{In this paper, we investigate the number of simulations that people run when reasoning about a task that requires mental simulation of physics. 
-Specifically, we ask the question: do people vary the number of mental simulations that they run depending on the difficulty of the problem?
-To answer these questions, we ran a behavioral experiment in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall.
+In this paper, we investigate how people use mental simulations.
+In particular, do people vary the number of mental simulations that they run in order to optimally balance speed and accuracy?
+To answer this question, we focused on the particular domain of intuitive physics, for which there is prior evidence that people use mental simulation to make predictions about the world \cite<e.g.>{Smith:2013fc,Battaglia2013}.
+We combined a model of approximate, noisy physical simulation with a well-known strategy in decision making called the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
+Our model predicted that people should vary the number of simulations that they run depending on the difficulty of the task.
+Specifically, they should use more samples when it is harder to make an accurate prediction.
+We tested this hypothesis through a task in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall. 
 We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
-Following the predictions of the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential}, we hypothesized that people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-In brief, we find that judgments of whether the ball goes in and the corresponding response times are well-predicted by a model that combines noisy physical simulation with SPRT.}
+Both people's judgments and their response times were well-predicted by our model, demonstrating that people have a systematic strategy by which they use their mental simulations.
 
@@
 In this paper, we first formalize our model, combining the physical prediction model from \citeA{Smith:2013fc} with the SPRT decision strategy. 
-Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' accuracy and response times. 
+Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' judgments and response times. 
 We then demonstrate that our model can explain the empirical pattern of responses and response times we observed. 
@@
 \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
-Specifically, \citeA{Smith:2013fc} asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
-In order to predict where people would place the paddle on each trial, their model incorporated uncertainty in its physical simulations through five parameters: perceptual uncertainty over the position of the ball ($\sigma_p$), uncertainty in the initial direction of velocity ($\kappa_v$), ongoing uncertainty in the direction of movement ($\kappa_m$), uncertainty in the bounce angle ($\kappa_b$), and a ``center bias'' reflecting a bias for people to respond more towards the center of the $y$-axis ($\sigma_0$).
+Specifically, they asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
 
-Here, we used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events.
-Because the experiment in Figure \ref{fig:experiment} (see Experiment) was performed online, we additionally performed an online replication of the experiment from \citeA{Smith:2013fc} to set model parameters (see the Appendix for details).
-Thus, the physical prediction parameters were set independently of the results of the experiment in this paper.
+Here, we also used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events, with a few small differences.
+First, because our experiment (see the Experiment section) was performed online, we needed to refit the model parameters to reflect these different viewing conditions.
+To do this independently of the results of the experiment in this paper, we performed an online replication of the experiment from \citeA{Smith:2013fc} (see the Appendix for details).
 
-The physical prediction model provides a posterior predictive distribution of where the ball will be when it encounters the plane of the wall.
-However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
+Second, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
 Assuming they took on average $M$ samples, then the standard deviation we estimate using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
 Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
-
 If sampling pulls from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
-So, for a given threshold $T$, we can calculate the expected number of samples for any trial using equation \ref{eq:expsamp}.
 
@@
         \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
-\emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-\emph{Right:} each point corresponds to a different stimulus, trial type, and hole size.
+        \caption{\textbf{Response times as a function of response.} \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
+\emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{C:} each point corresponds to a different stimulus, trial type, and hole size.
 The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
@@
 
-If people are running simulations to reason about physical scenes, then a natural question is: how many simulations do they run?
+If people are running simulations to reason about physical scenes, then how many simulations do they run?
 Because the simulations are noisy, it might be benefial to run multiple simulations in order to get a better estimate of the outcome.
@@
 
-To summarize thus far, Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp} give us a formal hypothesis for what decisions people make, and how long they choose to make them. 
+To summarize thus far, Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp} give us a formal hypothesis for what decisions people make, and how long they take to make them. 
 In the next section, we present an experiment to empirically test this hypothesis.
@@
 
-In order to determine whether people take physical simulation samples in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future.
+In order to determine whether people run simulations in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future.
 Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
@@
 On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole. 
-Participants were instructed to press the ``space'' key to begin the trial. 
-Immediately upon pressing ``space'', the initial stimulus presentation began. 
-As soon as the initial stimulus animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
-Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' to respond in the affirmative, and `p' to respond in the negative. 
-Immediately after responding, text appeared saying ``Correct!'' or ``Incorrect.'', depending on the participants' response.
-Additionally, the gray occluder was removed, and participants were shown feedback animation of the path of the ball.
-After the feedback animation was complete, the final frame of the animation remained on the screen until participants pressed ``space'' to advance to the next trial.
+Participants were instructed to press ``space'' to begin the trial. 
+Immediately upon pressing ``space'', an animation of the initial stimulus began (see Stimuli). 
+As soon as this animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
+Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' if they thought it would, and `p' if they thought it would not. 
+After responding, text appeared saying ``Correct!'' or ``Incorrect.''
+The gray occluder was removed, and participants were shown a feedback animation of the path of the ball (see Stimuli).
+The final frame of this animation remained on the screen until participants pressed ``space'' to advance to the next trial.
 
-During the experiment, participants made judgements on 48 experimental trials, presented in a random order, as well as eight control trials, which were also shown in a random order, but interspersed with the experimental trials such that every 8th trial was a control trial.
+During the experiment, participants made judgments on 48 experimental trials, presented in a random order, as well as eight control trials, which were shown after every seven experiment trials, also in a random order.
 In addition, participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
@@
 
-The stimuli consisted of animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
-All stimuli consisted of two separate animations.
-The first was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was the feedback, which picked up immediately where the first animation left off, and which had a duration of 1.5 seconds and depicted the ball either going into the hole or bouncing off the wall that contained the hole.%
-\footnote{To enforce the constraint that the ball always travel the same distance during the feedback animation, the $x$-coordinate of the wall with the hole in it was allowed to vary across stimuli.}
-During the feedback animation, the ball could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
-In both animations, the ball had a velocity of 400px/s.
-Additionally, in the animations, the path that the ball had traveled so far was drawn with a faded gray line (see Figure \ref{fig:experiment}).
+The stimuli consisted of two animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
+The first animation was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
+The second animation was 1.5 seconds of feedback, and picked up immediately where the first animation left off.
+The feedback depicted the ball either going into the hole or bouncing off the wall that contained the hole.
+Across all stimuli, the ball always traveled the same distance during the feedback animation, and could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
+In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a faded gray line on the floor (see Figure \ref{fig:experiment}).
 
@@
 Dashed lines indicate perfect correspondence between model and people.
-\emph{Left}: The $x$-axis is the probability the model says the ball will go in the hole, and the $y$-axis is the proportion of participants saying the ball will go in the hole.
-\emph{Right}: Color and shape indicate the number of times the ball bounced during feedback.
+\emph{A:} The $x$-axis is the probability the model says the ball will go in the hole, and the $y$-axis is the proportion of participants saying the ball will go in the hole.
+\emph{B:} Color and shape indicate the number of times the ball bounced during feedback.
 The $x$-axis is the model response times, and the $y$-axis is the logarithmic mean response times of participants.}

### 2015-02-01 manuscript.tex
More tightening

@@
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
-\emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
-\emph{C:} each point corresponds to a different stimulus, trial type, and hole size.
-The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
-The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
-
 If people are running simulations to reason about physical scenes, then how many simulations do they run?
@@
 \section{Experiment: Will the ball go in the hole?}
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
+        \caption{\textbf{Response times as a function of response.} \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
+\emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times.
+\emph{C:} each point corresponds to a different stimulus, trial type, and hole size.
+The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time.
+The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
 
@@
 The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
-Thus, participants saw a total of 63 trials throughout the experiment.
+Thus, participants saw a total of 63 trials.
 
@@
 Additionally, there was an interaction between trial type and hole size (\ResponseFull{}).
-For three out of the four trial types, there was a significant difference between responses for the two different hole sizes (for CI, \ResponseCIttest{}; for FI, \ResponseCIttest{}; and for FM, \ResponseFMttest{}), with the exception being the ``close miss'' (CM) trials (\ResponseCMttest{}).
+For three out of the four trial types, there was a significant difference between responses for the two different hole sizes (for CI, \ResponseCIttest{}; for FI, \ResponseCIttest{}; and for FM, \ResponseFMttest{}), with the exception being the CM trials (\ResponseCMttest{}).
 Figure \ref{fig:pct-vs-rt}A shows responses as a function of trial type and hole size.
@@
 There were significant effects of both trial type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between trial type and hole size (\RTFull{}).
-However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials (\ResponsetimeFIttest{}), in which the ball went straight through the center of the hole (for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
-Figure \ref{fig:pct-vs-rt}B shows the response times as a function of trial type and hole size.
+As shown in Figure \ref{fig:pct-vs-rt}B, there was only evidence for a difference in reaction times by hole size in the case of the FI trials (\ResponsetimeFIttest{}), in which the ball went straight through the center of the hole (for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
 
@@
 This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
-Thus, it is clear that people are not spending a fixed amount of time thinking about each trial; rather, they spend more time thinking about the ``hard'' trials than the ``easy'' trials.
 
@@
 For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
-From these fits, we see that the intercepts are significantly different across the different numbers of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one bounce, \InterceptOneBounces{}; and for two bounces, \InterceptTwoBounces{}.
+From these fits, we see that the intercepts increase as a function of the number of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one, \InterceptOneBounces{}; and for two, \InterceptTwoBounces{}.
 This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
@@
 To account for this, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
-
 To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
@@
 The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
-We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.} \betazero{}, \betaone{}, and \betatwo{}.
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is also adjusting for the inflated uncertainty in the model.} \betazero{}, \betaone{}, and \betatwo{}.
 
@@
 Even if the number of bounces is not included, the SPRT model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
-In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times beyond the number of bounces.
+In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times.
 
@@
 We hypothesized that people use noisy physical simulations to predict whether a ball would go in a hole, and that they vary the number of simulations in order to exploit the fact that some judgments are easier to make than others.
-Specifically, if people are making the best use of their mental simulations, then they should take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.
-
 The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on more difficult trials.
@@
 
-\section{Appendix}
-
-In order to fit the parameters for the physical simulation model, we ran an online replication of the experiment from \citeA{Smith:2013fc}.
+\section{Appendix: Replication of \citeA{Smith:2013fc}}
 
@@
 
-The stimuli were modified versions of those used Experiment 1, with two major differences.
+The stimuli were modified versions of those used the main experiment, with two differences.
 First, instead of a wall with a hole in it, there was a paddle of length 100px that could move up and down the $y$-axis.
-Second, there was no feedback animation; instead, there was just a single feedback image corresponding to the last frame of the feedback animation.
-Because there was no feedback animation, there were only 48 stimuli (corresponding to the stimulus presentation animations from Experiment 1), plus the seven instruction trials and eight catch trials.
+Second, instead of a full feedback animation, we just displayed the last frame of the animation.
+Because there was no feedback animation, there were only 48 stimuli, plus the seven instruction trials and eight catch trials.
 
@@
 
-Like Experiment 1, the experiment was divided into two phases: the training phase (consisting of seven trials), and the experimental phase (consisting of the 48 experimental trials, with the eight control trials evenly interspersed).
+The experiment was divided into two phases: the training phase (consisting of seven trials), and the experimental phase (consisting of the 48 experimental trials, with the eight control trials evenly interspersed).
 On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
 The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
-Participants were instructed to press ``space'' to begin the trial.
-
-As in Experiment 1, immediately upon pressing ``space'', the initial stimulus presentation began, after which an occluder appeared.
-However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for 2 seconds.
+Participants were instructed to press ``space'' to begin the trial and display the stimulus presentation animation.
+After the stimulus presentation, a gray occluder appeared, as well as a timer that began counting down for 2 seconds.
 During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.
@@
 If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.''
-Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.
+Participants were then instructed to press ``space'' to begin the next trial.
 

### 2015-02-02 manuscript.tex
Fix misspellings

@@
 If people are running simulations to reason about physical scenes, then how many simulations do they run?
-Because the simulations are noisy, it might be benefial to run multiple simulations in order to get a better estimate of the outcome.
+Because the simulations are noisy, it might be beneficial to run multiple simulations in order to get a better estimate of the outcome.
 However, each simulation comes with a time cost.
@@
 On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
-The paddle begin at the center of the $y$-axis, and was freely moveable along the $y$-axis from the very beginning of the trial.
+The paddle begin at the center of the $y$-axis, and was freely movable along the $y$-axis from the very beginning of the trial.
 Participants were instructed to press ``space'' to begin the trial and display the stimulus presentation animation.
@@
 
-We fit the model parameters of $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses \cite<for details, see>{Smith:2013fc}, finding the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}.
+We fit the model parameters of $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to participant's responses \cite<for details, see>{Smith:2013fc}, finding the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}.
 With these parameters, we found very similar results to those from \citeA{Smith:2013fc}.

### 2015-02-02 manuscript.tex
Hone in on the introduction, make SPRT smallcaps

@@
 To answer this question, we focused on the particular domain of intuitive physics, for which there is prior evidence that people use mental simulation to make predictions about the world \cite<e.g.>{Smith:2013fc,Battaglia2013}.
-We combined a model of approximate, noisy physical simulation with a well-known strategy in decision making called the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential}.
+We combined a model of approximate, noisy physical simulation with a well-known strategy in decision making called the \emph{sequential probability ratio test}, or \textsc{sprt} \cite{wald1947sequential}.
 Our model predicted that people should vary the number of simulations that they run depending on the difficulty of the task.
@@
 \textbf{Keywords:} 
-mental simulation; intuitive physics; SPRT; computational modeling
+mental simulation; intuitive physics; \textsc{sprt}; computational modeling
 \end{abstract}
@@
 %% The question we're interested in: how many simulations do people take?
-How does the mind best make use of its computational resources?
-For example, imagine you are playing a game of Angry Birds, where the goal is to launch a bird to knock down a tower. 
-As you aim, you need to predict where the bird will go to decide whether your shot will have the desired effect. 
-How do you know where to aim, and how long do you spend thinking about each shot before you take it? 
-More generally, if an agent has the ability to make predictions about scenarios such as these, how long do they spend making predictions versus taking actions?
+How does the mind optimally allocate its resources?
+Consider the game of Angry Birds, where the goal is to launch birds to knock down a tower.
+To take a shot, the player can imagine---or \emph{mentally simulate}---the path the bird will take and how it will affect the tower.
+How long should the player spend thinking before they let each bird fly?
+If they spend no time thinking, they are likely to miss the target.
+But, if they spend too long thinking, it will take much longer to receive the satisfaction of beating the level.
+More generally, if an agent can mentally simulate the results of an action, how long should they spend simulating before acting?
 
-Recent research in the domain of physical reasoning has revealed that people make predictions about physical scenes---such as those found in Angry Birds---by running noisy physical simulations \cite{Sanborn2013,Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
-However, while this research has investigated the \emph{mechanism} by which people make these types of predictions, there has been very little investigation into \emph{how} people actually use this mechanism.
+In the domain of physical reasoning, research has revealed that people make predictions about physical scenes---such as those found in Angry Birds---by running noisy physical simulations \cite{Sanborn2013,Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+However, while this research has investigated the \emph{mechanism} for making these predictions, there has been very little investigation into how people \emph{use} this mechanism. 
 In particular, because the simulations are noisy, it may be beneficial to run multiple simulations in order to obtain more accurate predictions.
-So, if we are running mental simulations, how to we choose how many simulations to run?
+Is there an optimal number of simulations to run in these situations?
+If so, do people behave optimally?
 
@@
 To model this task, we combine a mechanism of noisy physical simulation with a decision strategy for sample-based agents.
-Specifically, we consider the \textit{sequential probability ratio test}, or SPRT, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
-SPRT has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
-Importantly, the SPRT strategy predicts that people need to take more samples---and thus also will take a longer time to respond---on more difficult tasks.
+Specifically, we consider the \textit{sequential probability ratio test}, or \textsc{sprt}, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
+Often under the name of the \emph{drift-diffusion} model, \textsc{sprt} has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
+Importantly, the \textsc{sprt} strategy predicts that people need to take more samples---and thus also will take a longer time to respond---on more difficult tasks.
 
@@
 Drawing on the results from both physical simulation and decision-making, we hypothesize that people make predictions by running mental simulations, and that they vary the number of simulations based on the difficulty of the task.
-In this paper, we first formalize our model, combining the physical prediction model from \citeA{Smith:2013fc} with the SPRT decision strategy. 
+In this paper, we first formalize our model, combining the simulation model from \citeA{Smith:2013fc} with the \textsc{sprt} decision strategy. 
 Next, we describe an experiment in which we asked participants to respond to the question of, ``will the ball go through the hole?'', and analyze peoples' judgments and response times. 
 We then demonstrate that our model can explain the empirical pattern of responses and response times we observed. 
-Finally, we discuss the implications of our results on the broader, underlying question: how do people optimally make use of mental simulations?
+Finally, we discuss the implications of our results on the broader, underlying question: how should people optimally make use of mental simulations?
 
@@
 How do people solve this problem?
-In this section, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or SPRT.
+In this section, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or \textsc{sprt}.
 
@@
 
-\subsection{The SPRT strategy}
+\subsection{The \textsc{sprt} strategy}
 
@@
 However, each simulation comes with a time cost.
-To optimize this speed-accuracy tradeoff, we apply the \emph{sequential probability ratio test}, or SPRT \cite{wald1947sequential} to the samples drawn from the physical simulation.
+To optimize this speed-accuracy tradeoff, we apply the \emph{sequential probability ratio test}, or \textsc{sprt} \cite{wald1947sequential} to the samples drawn from the physical simulation.
 By combining these two models, we can make predictions both for people's judgments, and how long they take to make those judgments.
@@
 
-In order to determine whether people run simulations in a way consistent with SPRT, we designed an experiment in which people made a binary judgment about what will happen in the future.
+In order to determine whether people run simulations in a way consistent with \textsc{sprt}, we designed an experiment in which people made a binary judgment about what will happen in the future.
 Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
 We designed the trials such that some were harder than others by varying the margin by which the ball either missed or went through the hole.
-According to SPRT, people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+According to \textsc{sprt}, people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
 
@@
 In particular, on trials when there was more agreement amongst participants (the fraction saying `in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
-This tradeoff mirrors the same tradeoff found in SPRT: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
+This tradeoff mirrors the same tradeoff found in \textsc{sprt}: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
 
@@
 The fitted model explains participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
-Even if the number of bounces is not included, the SPRT model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
-In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times.
+Even if the number of bounces is not included, the \textsc{sprt} model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
+In contrast, a simpler model that takes only a single sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times.
 
@@
 Comparing people's responses and response times to those of the model, we found an extremely strong fit.
-This provides evidence that people not only rely approximate physical simulations, but that they optimally vary the number of simulations that they run according to SPRT.
+This provides evidence that people not only rely approximate physical simulations, but that they optimally vary the number of simulations that they run according to \textsc{sprt}.
 
-If SPRT is the optimal strategy, then what is the optimal threshold?
-We found the best fitting SPRT threshold to be \threshold{}, which is consistent with previous research.
+If \textsc{sprt} is the optimal strategy, then what is the optimal threshold?
+We found the best fitting \textsc{sprt} threshold to be \threshold{}, which is consistent with previous research.
 According to \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples.

### 2015-02-02 manuscript.tex
typo

@@
 In addition, we found that response time is affected by the number of bounces during feedback.
-Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with once bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
+Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with one bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
 While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.

### 2015-02-02 manuscript.tex
Small changes in response to Kevin's comments

@@
 We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
-Both people's judgments and their response times were well-predicted by our model, demonstrating that people have a systematic strategy by which they use their mental simulations.
+Both people's judgments and their response times were well-predicted by our model, demonstrating that people have a systematic strategy to allocate their resources for mental simulation.
 
@@
 There were significant effects of both trial type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between trial type and hole size (\RTFull{}).
-As shown in Figure \ref{fig:pct-vs-rt}B, there was only evidence for a difference in reaction times by hole size in the case of the FI trials (\ResponsetimeFIttest{}), in which the ball went straight through the center of the hole (for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
+As in Figure \ref{fig:pct-vs-rt}B, hole size only had an effect in the case of the FI trials (\ResponsetimeFIttest{}; for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
 
@@
 If we assume that every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
-However, we found the number of bounces to be an extremely strong predictor of response time: each additional bounce adds a constant amount of time to the response.
+However, we found the number of bounces to be a strong predictor of response time.
 To account for this, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
+Briefly, $\beta_0$ is the time to set up the simulation and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
 To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
@@
 For example, \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
-However, this paper is the first to provide evidence not only that people use a small number of simulations, but that they systematically vary the number of simulations.
+However, this paper is the first to provide evidence not only that people use a small number of simulations, but that they systematically vary the number of simulations rationally in response to task demands.
 

### 2015-02-03 manuscript.tex
Update in response to Tom's comments

@@
 
-\title{Think again?\\ Optimal mental simulation tracks problem difficulty}
+\title{Think again?\\ The amount of mental simulation tracks uncertainty in the outcome}
 
@@
 We combined a model of approximate, noisy physical simulation with a well-known strategy in decision making called the \emph{sequential probability ratio test}, or \textsc{sprt} \cite{wald1947sequential}.
-Our model predicted that people should vary the number of simulations that they run depending on the difficulty of the task.
-Specifically, they should use more samples when it is harder to make an accurate prediction.
+Our model predicted that people should vary the number of simulations that they run depending on their own uncertainty about the outcome.
+Specifically, they should use more samples when it is harder to make an accurate prediction due to higher uncertainty in their simulations.
 We tested this hypothesis through a task in which people watched a ball bouncing around in a box, and had to judge whether it would first go through a hole in the wall, or bounce off that wall. 
-We varied the difficulty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
+We varied the uncertainty of each trial by changing the size of the holes and the margin by which the ball either went through the hole or missed the hole. 
 Both people's judgments and their response times were well-predicted by our model, demonstrating that people have a systematic strategy to allocate their resources for mental simulation.
@@
 %% The question we're interested in: how many simulations do people take?
-How does the mind optimally allocate its resources?
+How should the mind optimally allocate its computational resources?
 Consider the game of Angry Birds, where the goal is to launch birds to knock down a tower.
@@
 
-In the domain of physical reasoning, research has revealed that people make predictions about physical scenes---such as those found in Angry Birds---by running noisy physical simulations \cite{Sanborn2013,Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+In the domain of physical reasoning, research suggests that people make predictions about physical scenes---such as those found in Angry Birds---by running noisy physical simulations \cite{Sanborn2013,Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 However, while this research has investigated the \emph{mechanism} for making these predictions, there has been very little investigation into how people \emph{use} this mechanism. 
@@
 Often under the name of the \emph{drift-diffusion} model, \textsc{sprt} has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
-Importantly, the \textsc{sprt} strategy predicts that people need to take more samples---and thus also will take a longer time to respond---on more difficult tasks.
+Importantly, the \textsc{sprt} strategy predicts that people need to take more samples---and thus also will take a longer time to respond---when there is roughly equal evidence for both hypotheses.
 
@@
 %% Plan of the paper
-Drawing on the results from both physical simulation and decision-making, we hypothesize that people make predictions by running mental simulations, and that they vary the number of simulations based on the difficulty of the task.
+Drawing on the results from both physical simulation and decision-making, we hypothesize that people make predictions by running mental simulations, and that they vary the number of simulations based on their uncertainty.
 In this paper, we first formalize our model, combining the simulation model from \citeA{Smith:2013fc} with the \textsc{sprt} decision strategy. 
@@
 This hypothesis, referred to as the ``noisy Newton'' hypothesis \cite{Sanborn2013}, states that people have approximate knowledge of physical laws instantiated in a runnable model of intuitive physics.
-Using this model, they can extrapolate the future of physical scenes by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
+Using this model, they can extrapolate the future by running a series of noisy simulations \cite{Smith:2013fc,Battaglia2013,Smith:2013ug,Smith:2013th,Smith:2014tx,Ullman:2014ut,Hamrick:2015}.
 
 \citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
-Specifically, they asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis.
-
-Here, we also used the model of \citeA{Smith:2013fc} to describe how people simulate individual possible physical events, with a few small differences.
-First, because our experiment (see the Experiment section) was performed online, we needed to refit the model parameters to reflect these different viewing conditions.
-To do this independently of the results of the experiment in this paper, we performed an online replication of the experiment from \citeA{Smith:2013fc} (see the Appendix for details).
-
-Second, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
-Assuming they took on average $M$ samples, then the standard deviation we estimate using the physical simulator ($\sigma_{judgments}$) is not equal to the standard deviation of distributions of simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{sims} = \sigma_{judgments} / \sqrt{M}$.
-Therefore, we allowed for one free parameter to adjust this variance such that $\sigma_{adj}=\sqrt{M}$.
-If sampling pulls from this distribution, the probability of a ball going `in' ($H_1$) on any given sample is simply the density of the probability distribution that overlaps with the hole ($p$).
+Using a model like this, we can hypothesize how people reason about the task in Figure \ref{fig:experiment}: that they run noisy physical simulations to estimate where the ball will go.
 
@@
 
-The probability of choosing $H_1$ given that $H_1$ is the MAP hypothesis is:
+Independent of the actual number of samples taken, the probability of choosing the MAP hypothesis ($H_1$) is:
 \begin{equation}
-\Pr[\hat{H}(Y_N)=H_1\,|\,H_1]=\frac{p^T}{p^T+(1-p)^T}
+\Pr[\hat{H}(Y_N)=H_1\,|\,H_1,T,p]=\frac{p^T}{p^T+(1-p)^T},
 \label{eq:pr-choose-h1}
 \end{equation}
-
-Given the threshold $T$, the probability of taking $N$ samples and then choosing $H_1$ is:
-\begin{multline}
-\Pr[N,H_1\,|\,T,p]=\left(\frac{2^N}{2T}\right)p^{\frac{N+T}{2}}(1-p)^{\frac{N-T}{2}}\cdot{}\\
-\sum_{\nu=1}^{2T-1}\cos\left(\frac{\nu\pi}{2T}\right)^{N-1}\sin\left(\frac{\nu\pi}{2T}\right)\sin\left(\frac{\nu\pi}{2}\right)
-\end{multline}
-for $N\geq T$ and where $N$ is of the same parity as $T$ \cite[ch.~XIV, eq. 5.7]{Feller:1968ut}. 
-Because we are dealing with binary hypotheses, the marginal probability of $N$ samples is then $\Pr[N\,|\,T,p]=\Pr[N,H_1\,|\,T,p]+\Pr[N,H_1\,|\,T,1-p]$.
-So, the expected number of samples for a particular decision is:
+and the expected number of samples taken before reaching either $Y_N=T$ or $Y_N=-T$ is given by:
 \begin{equation}
-\mathbb{E}[N\,|\,T,p]=\sum_{N=T}^\infty N\cdot{}\Pr[N\,|\,T,p]
+\mathbb{E}[N\,|\,T,p]=\frac{T}{1-2p}-\frac{2T}{1-2p}\cdot{}\frac{1-((1-p)/p)^T}{1-((1-p)/p)^{2T}},
 \label{eq:expsamp}
 \end{equation}
+which is derived by \citeA[ch.~XIV, eq. 3.4]{Feller:1968ut}.
 
-To summarize thus far, Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp} give us a formal hypothesis for what decisions people make, and how long they take to make them. 
-In the next section, we present an experiment to empirically test this hypothesis.
+\subsection{Combining simulation and \textsc{sprt}}
 
-\section{Experiment: Will the ball go in the hole?}
+In order to combine simulation and \textsc{sprt}, we used the model from \citeA{Smith:2013fc} to sample possible trajectories of the ball.
+We then used those trajectories to estimate a posterior predictive distribution of where the ball will go.
+Specifically, this distribution was a truncated normal, with the mean and standard deviation estimated from samples from the physical simulation model.
+Then, the probability $p$ that the ball goes in the hole is the probability mass overlapping the hole.
+This probability can then be used to compute Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp}, which give a formal hypothesis for what decisions people make, and how long they choose to make them.
+
+Because our experiment (described in the next section) was performed online, we needed to fit the parameters of the model from \citeA{Smith:2013fc} to reflect these different viewing conditions.
+To do this independently of the results of the experiment in this paper, we performed an online replication of the experiment from \citeA{Smith:2013fc} in which we asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis (see the Appendix for details).
+However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
+Assuming they took on average $M$ samples, then the standard deviation of their judgments ($\sigma_{judgments}$) is not equal to the standard deviation of their simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{judgments} = \sigma_{sims} / \sqrt{M}$.
+Therefore, to estimate $\sigma_{sims}$, we allowed for a free parameter, $\sigma_{adj}=\sqrt{M}$, which multiplied our original estimate of the standard deviation.
+
+\section{Testing the \textsc{sprt} model of mental simulation}
 
@@
 Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
-We designed the trials such that some were harder than others by varying the margin by which the ball either missed or went through the hole.
-According to \textsc{sprt}, people should be faster to respond on ``easy'' trials (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole), and slower to respond on ``hard'' trials (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+We designed the trials such that, if people were using mental simulations, those trials should be more uncertain.
+Specifically, we varied the margin by which the ball either missed or went through the hole.
+According to \textsc{sprt}, people should be slower to respond on trials where, according to their simulations, the probability that the ball goes in the hole is close to $p=0.5$ (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
+They should be faster to respond when their simulations are more certain (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole).
 
@@
 We hypothesized that people use noisy physical simulations to predict whether a ball would go in a hole, and that they vary the number of simulations in order to exploit the fact that some judgments are easier to make than others.
-The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on more difficult trials.
+The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on the trials they were most uncertain about.
 Comparing people's responses and response times to those of the model, we found an extremely strong fit.
@@
 Mental simulation is a powerful and flexible tool, as it offers us a way to make predictions about scenarios that have not yet come to pass, or which may never come to pass.
-In this work, we demonstrated that when people use mental simulation, they are sensitive to the difficulty of the task and accordingly adjust how many simulations they run.
+In this work, we demonstrated that when people use mental simulation, they are sensitive to their own uncertainty in reasoning about the task and accordingly adjust how many simulations they run.
 This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but specifically \emph{how} they use it.

### 2015-02-04 manuscript.tex
Small tweaks in response to Kevin's comments

@@
 But, if they spend too long thinking, it will take much longer to receive the satisfaction of beating the level.
-More generally, if an agent can mentally simulate the results of an action, how long should they spend simulating before acting?
+More generally, if running simulations will provide a more accurate forecast but incur a sampling cost, how long should an agent spend simulating before acting?
 
@@
         Each panel shows a different part of the trial. 
-        \emph{Left:} the initial screen presented to the participant.
+        \emph{A:} the initial screen presented to the participant.
         The arrow was not part of the actual stimuli; it has been added to reflect the animation that participants observed after pressing ``space''. 
-        \emph{Middle:}  the screen is occluded after observing the stimulus presentation. 
+        \emph{B:}  the screen is occluded after observing the stimulus presentation. 
         The faded gray line shows the path the ball took during the initial presentation. 
-        \emph{Right:} the final position of the ball, after observing the feedback. 
+        \emph{C:} the final position of the ball, after observing the feedback. 
         As in the middle panel, the faded gray line shows the path of the ball.}
@@
 Formally, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+In the case of the task in Figure \ref{fig:experiment}, we can think of $H_1$ as the hypothesis that the ball goes in, and $H_0$ as the hypothesis that it does not. 
 The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
@@
 
-In the best possible case, the agent takes infinitely many samples and chooses the maximum \emph{a posteriori} (MAP) hypothesis with probability $p$. 
+In the best possible case, the agent takes infinitely many samples and chooses the \emph{maximum a posteriori} (MAP) hypothesis with probability $p$. 
 In practice, the agent cannot take infinitely many samples. 
@@
         \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response times as a function of response.} \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
+        \caption{\textbf{Response characteristics as a function of trial type.}
+        \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
         \emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. 
@@
 Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
-We designed the trials such that, if people were using mental simulations, those trials should be more uncertain.
-Specifically, we varied the margin by which the ball either missed or went through the hole.
-According to \textsc{sprt}, people should be slower to respond on trials where, according to their simulations, the probability that the ball goes in the hole is close to $p=0.5$ (e.g., where the ball just barely goes through the hole, or just barely misses the hole).
-They should be faster to respond when their simulations are more certain (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole).
+We designed the trials to elicit a range of responses by varying the margin by which the ball either missed or went through the hole.
+According to \textsc{sprt}, people should be slower to respond on trials where, according to their simulations, the probability that the ball goes in the hole is close to $p=0.5$ (e.g., where the ball just barely goes through the hole, or just barely misses the hole), and they should be faster to respond when their simulations are more certain (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole).
 
@@
 
-The stimuli consisted of two animations depicting a blue ball with a radius of 10px bouncing around in a box with dimensions 900px $\times$ 650px.
+The stimuli consisted of two animations depicting a blue ball with a radius of 10px moving in a box with dimensions 900px $\times$ 650px.
 The first animation was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
 The second animation was 1.5 seconds of feedback, and picked up immediately where the first animation left off.
-The feedback depicted the ball either going into the hole or bouncing off the wall that contained the hole.
+The feedback showed the ball either going into the hole or bouncing off the wall that contained the hole.
 Across all stimuli, the ball always traveled the same distance during the feedback animation, and could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
-In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a faded gray line on the floor (see Figure \ref{fig:experiment}).
+In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a gray line on the floor (see Figure \ref{fig:experiment}).
 
@@
         \includegraphics[width=\textwidth]{figures/model_results.pdf}
-        \caption{\textbf{Model vs.
-human comparison.} In both plots, each point corresponds to a different stimulus, trial type, and hole size.
+        \caption{\textbf{Model vs. human comparison.} 
+        In both plots, each point corresponds to a different stimulus, trial type, and hole size. 
         Dashed lines indicate perfect correspondence between model and people. 
@@
 If we assume that every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
-However, we found the number of bounces to be a strong predictor of response time.
-To account for this, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
+However, because bounces were a strong predictor of response time, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
 Briefly, $\beta_0$ is the time to set up the simulation and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
@@
 The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
-We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is also adjusting for the inflated uncertainty in the model.} \betazero{}, \betaone{}, and \betatwo{}.
+We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is also adjusting for the inflated uncertainty in the model, and people are taking approximately one sample to catch the ball.} \betazero{}, \betaone{}, and \betatwo{}.
 
@@
 Second, instead of a full feedback animation, we just displayed the last frame of the animation.
-Because there was no feedback animation, there were only 48 stimuli, plus the seven instruction trials and eight catch trials.
+Because there was no hole that could vary by trial, there were only 48 stimuli, plus the seven instruction trials and eight catch trials.
 

### 2015-04-28 manuscript.tex
Update results
More results, update based on reviewer comments

@@
 \input{results/hole_empirical_analysis.tex}
+\input{results/hole_empirical_learning.tex}
 \input{results/num_participants.tex}
+\input{results/model_comparison.tex}
 
@@
 Then, the probability $p$ that the ball goes in the hole is the probability mass overlapping the hole.
-This probability can then be used to compute Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp}, which give a formal hypothesis for what decisions people make, and how long they choose to make them.
+This probability can then be used to compute Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp}, which give a formal hypothesis for what decisions people make, and how long it takes them.
 
@@
 
-In order to determine whether people run simulations in a way consistent with \textsc{sprt}, we designed an experiment in which people made a binary judgment about what will happen in the future.
+To determine whether people choose the number of simulations in a way consistent with \textsc{sprt}, we designed an experiment in which people made a binary judgment about what will happen in the future.
 Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
@@
 
-For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples.
+For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 10000 bootstrap samples.
 Participants had an average response time of \AvgRT{}, excluding catch trials.
@@
 As in Figure \ref{fig:pct-vs-rt}B, hole size only had an effect in the case of the FI trials (\ResponsetimeFIttest{}; for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
+
+\subsubsection{Effect of practice}
+
+To check for any effect of practice on participants responses, we computed Spearman rank correlations (with 95\% confidence intervals computed from 10000 bootstrap samples) between trial number and accuracy, as well as between trial number and response time.
+We found an overall effect of practice on accuracy (\ResponseTrialCorr{}), though in the second half of the experiment, this effect had disappeared (\ResponseTrialCorrLate{}).
+There was also an overall effect of practice on response time (\RTTrialCorr{}), which was strong both in the first (\RTTrialCorrEarly{}) and second (\RTTrialCorrLate{}) halves of the experiment.
+Future work will need to include a longer training period to alleviate these practice effects.
 
@@
 As shown in Figure \ref{fig:pct-vs-rt}C, we found a clear effect of certainty on people's response times.
-In particular, on trials when there was more agreement amongst participants (the fraction saying `in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
+We fit both 1st- and 2nd-order polynomial functions to the relationship between responses and response times, and found the 2nd-order function to be a much better fit according to both AIC and BIC (for the 1st-order function, \AicFirstOrder{} and \BicFirstOrder{}; for the 2nd-order function, \AicSecondOrder{} and \BicSecondOrder{}).
+These results indicate that on trials when there was more agreement amongst participants (the fraction saying `in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
 This tradeoff mirrors the same tradeoff found in \textsc{sprt}: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
@@
 While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
-For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses.
-From these fits, we see that the intercepts increase as a function of the number of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one, \InterceptOneBounces{}; and for two, \InterceptTwoBounces{}.
-This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation.
+We fit a new 2nd-order polynomial function to participants' responses, and included the number of bounces as an additional regressor.
+With this new model, we find that the number of bounces is a strong predictor of response time above and beyond uncertainty (with bounces, \AicSecondOrderWithBounces{} and \BicSecondOrderWithBounces{}; without bounces, \AicSecondOrder{} and \BicSecondOrder{}).
+By looking at the coefficient for the number of bounces, we find that the each bounce adds approximately \RTBounceCoef{} to the overall response time.
+Thus, even if people are using a \textsc{sprt}-like strategy, there is an additional time cost per bounce that cannot be explained by simulation variance alone.
 
@@
 If we assume that every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
-However, because bounces were a strong predictor of response time, our final response time equation incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
+However, because bounces were a strong predictor of response time, our final response time equation also incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
 Briefly, $\beta_0$ is the time to set up the simulation and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
 To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
-We then fit all parameters ($T$, $\sigma_{adj}$, $\beta_0$, $\beta_1$, and $\beta_2$) to minimize sum squared error between modeled and observed reaction times, using $n=10000$ samples from the physical simulation model.
+We then fit all parameters ($T$, $\sigma_{adj}$, $\beta_0$, $\beta_1$, and $\beta_2$) to minimize sum squared error between modeled and observed reaction times, using 10000 samples from the physical simulation model.
 The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
@@
 
-The fitted model explains participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
+We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples.
+The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
 Even if the number of bounces is not included, the \textsc{sprt} model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
-In contrast, a simpler model that takes only a single sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times.
+
+A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) and about as well at explaining RT (\NoSamplesHoleRTCorr{}) as the full model.
+However, this model cannot explain the variation of RT within bounces, while the full model can.
+For the model with $T=1$, the correlation of RT for zero bounces was \NoSamplesHoleRTCorrZeroBounces{}; for one bounce, it was \NoSamplesHoleRTCorrOneBounce{}; and for two bounces, it was \NoSamplesHoleRTCorrTwoBounces{}.
+In contrast, for the model with $T=2$, the correlation of RT for zero bounces was \HoleRTCorrZeroBounces{}; for one bounce, it was \HoleRTCorrOneBounce{}; and for two bounces, it was \HoleRTCorrTwoBounces{}.
+The model with $T=1$ also fares slightly worse overall according to both BIC and AIC (for $T=1$, \BicNoSamples{} and \AicNoSamples{}; for $T=2$, \BicFull{} and \AicFull{}).
 
@@
 Comparing people's responses and response times to those of the model, we found an extremely strong fit.
-This provides evidence that people not only rely approximate physical simulations, but that they optimally vary the number of simulations that they run according to \textsc{sprt}.
+This provides evidence that people not only rely on approximate physical simulations, but that they optimally vary the number of simulations that they run according to \textsc{sprt}.
 

### 2015-04-28 manuscript.tex
Small edits

@@
 How long should the player spend thinking before they let each bird fly?
-If they spend no time thinking, they are likely to miss the target.
+If they spend very little time thinking, they are likely to miss the target.
 But, if they spend too long thinking, it will take much longer to receive the satisfaction of beating the level.
@@
 The feedback showed the ball either going into the hole or bouncing off the wall that contained the hole.
-Across all stimuli, the ball always traveled the same distance during the feedback animation, and could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
+Across all stimuli, the ball always traveled the same distance during both the stimulus and feedback animations, and could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
 In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a gray line on the floor (see Figure \ref{fig:experiment}).
@@
 However, because bounces were a strong predictor of response time, our final response time equation also incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
-Briefly, $\beta_0$ is the time to set up the simulation and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
+Briefly, $\beta_0$ is the time to set up the simulation(s) and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
 To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.

### 2015-04-28 manuscript.tex
Put correlations in a table

@@
 \usepackage{color}
+\usepackage{booktabs}
 
@@
 % space below "Figure 1: ...", but only for inline figures
-%\addtolength{\textfloatsep}{-0.1cm}
+\addtolength{\textfloatsep}{0.1cm}
 
@@
 We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples.
-The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
-Even if the number of bounces is not included, the \textsc{sprt} model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).
-
-A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) and about as well at explaining RT (\NoSamplesHoleRTCorr{}) as the full model.
-However, this model cannot explain the variation of RT within bounces, while the full model can.
-For the model with $T=1$, the correlation of RT for zero bounces was \NoSamplesHoleRTCorrZeroBounces{}; for one bounce, it was \NoSamplesHoleRTCorrOneBounce{}; and for two bounces, it was \NoSamplesHoleRTCorrTwoBounces{}.
-In contrast, for the model with $T=2$, the correlation of RT for zero bounces was \HoleRTCorrZeroBounces{}; for one bounce, it was \HoleRTCorrOneBounce{}; and for two bounces, it was \HoleRTCorrTwoBounces{}.
-The model with $T=1$ also fares slightly worse overall according to both BIC and AIC (for $T=1$, \BicNoSamples{} and \AicNoSamples{}; for $T=2$, \BicFull{} and \AicFull{}).
+The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A).
+A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}).
+As shown in Table \ref{tbl:rt}, both models do equally well at explaining overall RT in terms of correlation.
+According to both BIC and AIC, the $T=1$ model does slightly worse (\BicNoSamples{} and \AicNoSamples{}) than the full model (\BicFull{} and \AicFull{}).
+Moreover, the $T=1$ model cannot explain variance in RTs within bounces, whereas the full model with $T=2$ can (Table \ref{tbl:rt}).
+If the number of bounces is excluded entirely, the full model can predict human RTs to a moderate degree (\NoBouncesHoleRTCorr{}), while the model with $T=1$ cannot predict RTs at all.
 
@@
 This provides evidence that people not only rely on approximate physical simulations, but that they optimally vary the number of simulations that they run according to \textsc{sprt}.
+
+\begin{table}
+    \begin{tabular}{ccl}
+    \toprule
+    \textbf{Threshold} & \textbf{Bounces} & \textbf{Correlation} \\
+    \midrule
+    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
+          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
+          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
+          & all & \NoSamplesHoleRTCorr{} \\
+    \midrule
+    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
+          & 1   & \HoleRTCorrOneBounce{} \\
+          & 2   & \HoleRTCorrTwoBounces{} \\
+          & all & \HoleRTCorr{} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Correlations between human and model RTs.}
+    \label{tbl:rt}
+\end{table}
 

### 2015-04-29 manuscript.tex
Tightening down to 6 pages

@@
 %% The question we're interested in: how many simulations do people take?
-How should the mind optimally allocate its computational resources?
+How should the mind allocate its computational resources?
 Consider the game of Angry Birds, where the goal is to launch birds to knock down a tower.
@@
 To model this task, we combine a mechanism of noisy physical simulation with a decision strategy for sample-based agents.
-Specifically, we consider the \textit{sequential probability ratio test}, or \textsc{sprt}, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
-Often under the name of the \emph{drift-diffusion} model, \textsc{sprt} has been used successfully to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
+We consider the \textit{sequential probability ratio test}, or \textsc{sprt}, in which an agent takes samples that point to one hypothesis or another, and continues to do so until the net samples in favor of one hypothesis reaches a threshold, at which point that hypothesis wins \cite{wald1947sequential}.
+Often under the name of the \emph{drift-diffusion} model, \textsc{sprt} has been used to explain behavior in a number of decision-making tasks \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}, as it provides an optimal cost-benefit tradeoff between sampling and exploiting information \cite{Wald:1950uw}.
 Importantly, the \textsc{sprt} strategy predicts that people need to take more samples---and thus also will take a longer time to respond---when there is roughly equal evidence for both hypotheses.
@@
 We then demonstrate that our model can explain the empirical pattern of responses and response times we observed. 
-Finally, we discuss the implications of our results on the broader, underlying question: how should people optimally make use of mental simulations?
+Finally, we discuss the implications of our results on the broader, underlying question: how should people make use of mental simulations?
 
@@
 
-Consider the task in Figure \ref{fig:experiment}, in which people observe a ball moving inside a box, and must predict whether it will go through a hole or not.
+Consider the task in Figure \ref{fig:experiment}, in which people observe a ball moving inside a box, and must predict whether it will go through the hole.
 How do people solve this problem?
-In this section, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or \textsc{sprt}.
+Here, we formalize a model that answers this question by combining noisy physical simulations with a decision-making strategy known as the \emph{sequential probability ratio test}, or \textsc{sprt}.
 
@@
 
-\citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in exactly where objects are and their motion trajectories) and dynamic uncertainty (stochastic noise added to account for unknowable variation in motion---e.g., a textured floor would cause a ball rolling along it to deviate from a straight line).
-Using a model like this, we can hypothesize how people reason about the task in Figure \ref{fig:experiment}: that they run noisy physical simulations to estimate where the ball will go.
+\citeA{Smith:2013fc} investigated the various sources of uncertainty in these simulations, finding that people's judgments were best captured by a model that took into account both perceptual uncertainty (noise in object locations and their trajectories) and dynamic uncertainty (noise in the object's motion---e.g., a textured floor would cause a ball to deviate from a straight line).
+Using this model, we hypothesize that people reason about the task in Figure \ref{fig:experiment} by running noisy physical simulations to estimate where the ball will go.
 
@@
 
-Formally, we consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
-In the case of the task in Figure \ref{fig:experiment}, we can think of $H_1$ as the hypothesis that the ball goes in, and $H_0$ as the hypothesis that it does not. 
-The agent may take samples $X_i$ from a Bernoulli distribution parameterized by an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
+We consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
+In the case of the task in Figure \ref{fig:experiment}, $H_1$ is the hypothesis that the ball goes in, and $H_0$ is the hypothesis that it does not. 
+The agent may take samples $X_i$ from a Bernoulli distribution with an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
 Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
+
+\begin{figure*}[t]
+    \begin{center}
+        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
+        \caption{\textbf{Response characteristics as a function of trial type.}
+        \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
+        \emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of RTs. 
+        \emph{C:} each point corresponds to a different stimulus, trial type, and hole size.  
+        The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean RT. 
+        The black line indicates a 2nd-order polynomial fit between responses and RTs and the shaded gray region indicates the 95\% confidence interval around the fit.}
+        \label{fig:pct-vs-rt}
+    \end{center}
+\end{figure*}
 
@@
 
-In order to combine simulation and \textsc{sprt}, we used the model from \citeA{Smith:2013fc} to sample possible trajectories of the ball.
-We then used those trajectories to estimate a posterior predictive distribution of where the ball will go.
-Specifically, this distribution was a truncated normal, with the mean and standard deviation estimated from samples from the physical simulation model.
-Then, the probability $p$ that the ball goes in the hole is the probability mass overlapping the hole.
+In order to combine simulation and \textsc{sprt}, we used the model from \citeA{Smith:2013fc} to sample possible trajectories of the ball, from which we estimated a truncated normal posterior predictive distribution of where the ball will go.
+From this distribution, we compute the probability $p$ that the ball goes in the hole as the probability mass overlapping the hole.
 This probability can then be used to compute Equations \ref{eq:pr-choose-h1} and \ref{eq:expsamp}, which give a formal hypothesis for what decisions people make, and how long it takes them.
@@
 Because our experiment (described in the next section) was performed online, we needed to fit the parameters of the model from \citeA{Smith:2013fc} to reflect these different viewing conditions.
-To do this independently of the results of the experiment in this paper, we performed an online replication of the experiment from \citeA{Smith:2013fc} in which we asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis (see the Appendix for details).
-However, it is possible that the participants in the auxiliary experiment used more than one sample to determine where the ball would go.
-Assuming they took on average $M$ samples, then the standard deviation of their judgments ($\sigma_{judgments}$) is not equal to the standard deviation of their simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{judgments} = \sigma_{sims} / \sqrt{M}$.
+To do this, we performed an online replication of the experiment from \citeA{Smith:2013fc} in which we asked people to catch a ball like the one in Figure \ref{fig:experiment} using a paddle that could move up and down along the $y$-axis (see Appendix).
+If we assume participants in this auxiliary experiment took on average $M$ samples, then the standard deviation of their judgments ($\sigma_{judgments}$) is not equal to the standard deviation of their simulations ($\sigma_{sims}$), but is instead related by the equation: $\sigma_{judgments} = \sigma_{sims} / \sqrt{M}$.
 Therefore, to estimate $\sigma_{sims}$, we allowed for a free parameter, $\sigma_{adj}=\sqrt{M}$, which multiplied our original estimate of the standard deviation.
@@
 
-\begin{figure*}[t]
-    \begin{center}
-        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
-        \caption{\textbf{Response characteristics as a function of trial type.}
-        \emph{A:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular trial type ($x$-axis) and hole size (color).
-        \emph{B:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. 
-        \emph{C:} each point corresponds to a different stimulus, trial type, and hole size.  
-        The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$-axis is the logarithmic mean response time. 
-        The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
-        \label{fig:pct-vs-rt}
-    \end{center}
-\end{figure*}
-
-To determine whether people choose the number of simulations in a way consistent with \textsc{sprt}, we designed an experiment in which people made a binary judgment about what will happen in the future.
-Specifically, we asked participants to reason about whether a ball traveling across a computer screen would go through a hole or not (see Figure \ref{fig:experiment}).
+To determine whether people choose simulations in a way consistent with \textsc{sprt}, we ran an experiment in which people made a binary judgment about whether a ball traveling across a computer screen would go through a hole (see Figure \ref{fig:experiment}).
 We designed the trials to elicit a range of responses by varying the margin by which the ball either missed or went through the hole.
-According to \textsc{sprt}, people should be slower to respond on trials where, according to their simulations, the probability that the ball goes in the hole is close to $p=0.5$ (e.g., where the ball just barely goes through the hole, or just barely misses the hole), and they should be faster to respond when their simulations are more certain (e.g., where the ball goes directly through the center of a large hole, or hits the wall very far away from the hole).
+According to \textsc{sprt}, when people's simulations are uncertain---i.e., when the probability that the ball goes in the hole is close to $p=0.5$, such as when the ball just barely goes through the hole---they should be slower to respond.
+People should be faster to respond when their simulations are more certain, such as when the ball misses the hole by a wide margin.
 
@@
 We recruited \HoleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
-Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work.
-Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli). 
-Additionally, we excluded \HoleNumFailed{} participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of \HoleNumOk{} participants.
+Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for 6.5 minutes of work.
+Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged (see Stimuli). 
+We excluded \HoleNumFailed{} participants for answering incorrectly on more than one control trial (see Stimuli), leaving a total of \HoleNumOk{} participants.
 
@@
 On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole. 
-Participants were instructed to press ``space'' to begin the trial. 
-Immediately upon pressing ``space'', an animation of the initial stimulus began (see Stimuli). 
-As soon as this animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder to participants of where the ball had come from).
-Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' if they thought it would, and `p' if they thought it would not. 
+Participants were instructed to press ``space'' to begin the trial, after which an animation of the initial stimulus began (see Stimuli). 
+As soon as this animation concluded, a gray box was drawn over the screen, occluding the ball (but not the line depicting the path it had traveled so far; this was left in as a reminder of where the ball had come from).
+Participants were asked, ``will the ball go in the hole?'', and were instructed to press `q' if they thought it would, and `p' otherwise. 
 After responding, text appeared saying ``Correct!'' or ``Incorrect.''
@@
 
-During the experiment, participants made judgments on 48 experimental trials, presented in a random order, as well as eight control trials, which were shown after every seven experiment trials, also in a random order.
-In addition, participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
-
-\subsection{Stimuli}
-
-The stimuli consisted of two animations depicting a blue ball with a radius of 10px moving in a box with dimensions 900px $\times$ 650px.
-The first animation was the stimulus presentation, which had a duration of 0.775 seconds and depicted the ball moving in a particular direction.
-The second animation was 1.5 seconds of feedback, and picked up immediately where the first animation left off.
-The feedback showed the ball either going into the hole or bouncing off the wall that contained the hole.
-Across all stimuli, the ball always traveled the same distance during both the stimulus and feedback animations, and could bounce on the other walls either 0, 1, or 2 times before going into the hole or hitting the wall with the hole in it.
-In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a gray line on the floor (see Figure \ref{fig:experiment}).
-
-There were 48 different initial animations, equally balanced by number of bounces during feedback (16 each for 0, 1, and 2 bounces). 
-For each of these initial animations, there were four different trial types and two different hole sizes, giving a total of eight versions of each stimulus. 
-The four trial types were: ``far in'' (FI), where the ball went directly through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
-The two hole sizes were 100px and 200px.
-
-In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
-Thus, each participant saw each initial animation exactly once, each trial type exactly 12 times, and each hole size exactly 24 times.
-This also ensured that the ball would go through the hole exactly half the time, so that participants would not be biased to respond either way based on statistical contingencies.
-
-In addition to the 48 experimental trials, there were seven instruction trials and eight control trials, which were the same for all participants.
-The control trials were designed to be extremely easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
-Thus, participants saw a total of 63 trials.
-
-\subsection{Results}
-
-\subsubsection{Responses}
-
-On average, participants were correct \AvgCorrect{} of the time and responded that the ball would go in the hole \AvgResponse{} of the time (\ResponseN{}), excluding catch trials.
-There was a significant effect of trial type on participants' responses (\ResponseHoleClass{}) as well as a significant effect of hole size (\ResponseHoleSize{}).
-Additionally, there was an interaction between trial type and hole size (\ResponseFull{}).
-For three out of the four trial types, there was a significant difference between responses for the two different hole sizes (for CI, \ResponseCIttest{}; for FI, \ResponseCIttest{}; and for FM, \ResponseFMttest{}), with the exception being the CM trials (\ResponseCMttest{}).
-Figure \ref{fig:pct-vs-rt}A shows responses as a function of trial type and hole size.
-
-\subsubsection{Response times}
-
-For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 10000 bootstrap samples.
-Participants had an average response time of \AvgRT{}, excluding catch trials.
-There were significant effects of both trial type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between trial type and hole size (\RTFull{}).
-As in Figure \ref{fig:pct-vs-rt}B, hole size only had an effect in the case of the FI trials (\ResponsetimeFIttest{}; for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
-
-\subsubsection{Effect of practice}
-
-To check for any effect of practice on participants responses, we computed Spearman rank correlations (with 95\% confidence intervals computed from 10000 bootstrap samples) between trial number and accuracy, as well as between trial number and response time.
-We found an overall effect of practice on accuracy (\ResponseTrialCorr{}), though in the second half of the experiment, this effect had disappeared (\ResponseTrialCorrLate{}).
-There was also an overall effect of practice on response time (\RTTrialCorr{}), which was strong both in the first (\RTTrialCorrEarly{}) and second (\RTTrialCorrLate{}) halves of the experiment.
-Future work will need to include a longer training period to alleviate these practice effects.
-
-\subsubsection{Relationship of responses to reaction time}
+Participants were given seven instruction trials prior to the experiment to familiarize them with the procedure.
+Then, participants made judgments on 48 experimental trials in a random order.
+There were also eight control trials, which were shown in a random order after every seven experiment trials.
 
@@
         \emph{B:} Color and shape indicate the number of times the ball bounced during feedback. 
-        The $x$-axis is the model response times, and the $y$-axis is the logarithmic mean response times of participants.}
+        The $x$-axis is the model RTs, and the $y$-axis is the logarithmic mean RTs of participants.}
         \label{fig:model-results}
@@
 
-As shown in Figure \ref{fig:pct-vs-rt}C, we found a clear effect of certainty on people's response times.
-We fit both 1st- and 2nd-order polynomial functions to the relationship between responses and response times, and found the 2nd-order function to be a much better fit according to both AIC and BIC (for the 1st-order function, \AicFirstOrder{} and \BicFirstOrder{}; for the 2nd-order function, \AicSecondOrder{} and \BicSecondOrder{}).
-These results indicate that on trials when there was more agreement amongst participants (the fraction saying `in' is closer to $0$ or $1$), participants were faster to respond than when responses were more variable.
-This tradeoff mirrors the same tradeoff found in \textsc{sprt}: decisions for which $p\approx0.5$ are slower, because it on average takes more samples to get to one threshold versus the other.
+\subsection{Stimuli}
 
-In addition, we found that response time is affected by the number of bounces during feedback.
+The stimuli consisted of two animations---the \emph{stimulus presentation} and the \emph{feedback} animations---depicting a blue ball with a radius of 10px moving in a box with dimensions 900px $\times$ 650px.
+In both animations, the ball had a velocity of 400px/s, and as it moved, it traced a gray line (see Figure \ref{fig:experiment}).
+The stimulus presentation had a duration of 0.775s and depicted the ball moving in a particular direction.
+The feedback had a duration of 1.5s and picked up where the stimulus presentation left off; it showed the ball either going into the hole or bouncing off the wall that contained the hole for.
+Across all stimuli, the ball traveled the same distance during both animations, and could bounce on the other walls 0, 1, or 2 times before going into the hole or hitting the wall with the hole.
+
+There were 48 different initial animations, equally balanced by number of bounces during feedback (16 each for 0, 1, and 2 bounces). 
+For each of these initial animations, there were four trial types and two hole sizes, for a total of eight versions of each stimulus. 
+The four trial types were: ``far in'' (FI), where the ball went through the center of the hole; ``far miss'' (FM), where the ball missed the hole by a wide margin; ``close in'' (CI), where the ball just barely went through the hole; and `` close miss'' (CM), where the ball just barely missed the hole.
+The two hole sizes were 100px and 200px.
+
+In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
+Thus, each participant saw each initial animation once, each trial type 12 times, and each hole size 24 times.
+This also ensured that the ball would go through the hole half the time, so that participants would not be biased to respond either way.
+Additionally, there were seven instruction trials and eight control trials, which were the same for all participants.
+The control trials were designed to be easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
+Thus, participants saw a total of 63 trials.
+
+\subsection{Results}
+
+\subsubsection{Responses}
+
+On average, participants were correct \AvgCorrect{} of the time and responded that the ball would go in the hole \AvgResponse{} of the time (\ResponseN{}), excluding catch trials.
+There was a significant effect of trial type on participants' responses (\ResponseHoleClass{}) as well as a significant effect of hole size (\ResponseHoleSize{}).
+There was also an interaction between trial type and hole size (\ResponseFull{}).
+There was a significant difference between responses for the two hole sizes (for CI, \ResponseCIttest{}; for FI, \ResponseCIttest{}; and for FM, \ResponseFMttest{}) except on the CM trials (\ResponseCMttest{}).
+Figure \ref{fig:pct-vs-rt}A shows responses as a function of trial type and hole size.
+
+\subsubsection{Response times}
+
+For all analyses of response time (RT), we computed averages using bootstrapped logarithmic means (exponential of the mean of the log RTs), using 10000 bootstrap samples.
+On average, participants responded in \AvgRT{}, excluding catch trials.
+There were effects of both trial type (\RTHoleClass{}) and hole size (\RTHoleSize{}), as well as an interaction between trial type and hole size (\RTFull{}).
+As in Figure \ref{fig:pct-vs-rt}B, hole size only had an effect in the case of the FI trials (\ResponsetimeFIttest{}; for CI, \ResponsetimeCIttest{}; for CM, \ResponsetimeCMttest{}; and for FM, \ResponsetimeFMttest{}).
+
 Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with one bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}).
-While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost.
-We fit a new 2nd-order polynomial function to participants' responses, and included the number of bounces as an additional regressor.
-With this new model, we find that the number of bounces is a strong predictor of response time above and beyond uncertainty (with bounces, \AicSecondOrderWithBounces{} and \BicSecondOrderWithBounces{}; without bounces, \AicSecondOrder{} and \BicSecondOrder{}).
-By looking at the coefficient for the number of bounces, we find that the each bounce adds approximately \RTBounceCoef{} to the overall response time.
-Thus, even if people are using a \textsc{sprt}-like strategy, there is an additional time cost per bounce that cannot be explained by simulation variance alone.
+
+\subsubsection{Relationship of responses and RTs}
+
+According to \textsc{sprt}, participants should be slower on trials for which they are less certain (i.e., when their average response is closer to 0.5), and faster when they are more certain (i.e., when their average response is closer to 0 or 1).
+Figure \ref{fig:pct-vs-rt}C illustrates that this trend does indeed appear.
+To demonstrate this more quantitatively, we fit both 1st- and 2nd- order polynomial functions to the relationship between responses and RTs.
+The 1st-order function had \AicFirstOrder{} and \BicFirstOrder{}, while the 2nd-order function had \AicSecondOrder{} and \BicSecondOrder{}.
+
+Participants' responses do not fully account for their RTs, however: the number of bounces is also a strong predictor of RT.
+Although people do make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer RTs, there appears to be an additional time cost.
+We modified the 2nd-order polynomial to include the number of bounces as an regressor, and found that the number of bounces is a strong predictor of RT above and beyond the responses (with bounces, \AicSecondOrderWithBounces{} and \BicSecondOrderWithBounces{}; without bounces, \AicSecondOrder{} and \BicSecondOrder{}).
+From the coefficient, we find that the each bounce adds \RTBounceCoef{}.
+Thus, even if people are using a \textsc{sprt}-like strategy, there is a time cost per bounce that cannot be explained by simulation variance alone.
+This suggests that there is a discrepancy between our simulation model and the manner in which people are \emph{actually} running simulations; investigating the details of this discrepancy is an area for future work.
+
+\subsubsection{Learning}
+
+To check for practice effects, we computed Spearman rank correlations (with 95\% confidence intervals computed from 10000 bootstrap samples) between trial number and accuracy, as well as between trial number and RT.
+We found an overall effect of practice on accuracy (\ResponseTrialCorr{}), though in the second half of the experiment, this effect disappeared (\ResponseTrialCorrLate{}).
+There was also an overall effect of practice on RT (\RTTrialCorr{}), which was strong both in the first (\RTTrialCorrEarly{}) and second (\RTTrialCorrLate{}) halves of the experiment.
+Future work will need to include a longer training period to alleviate these practice effects.
 
@@
 
-If we assume that every sample takes the same amount of time, response times as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
-However, because bounces were a strong predictor of response time, our final response time equation also incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
-Briefly, $\beta_0$ is the time to set up the simulation(s) and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
-To compute this equation, we used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
-We then fit all parameters ($T$, $\sigma_{adj}$, $\beta_0$, $\beta_1$, and $\beta_2$) to minimize sum squared error between modeled and observed reaction times, using 10000 samples from the physical simulation model.
-The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample?
-We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is also adjusting for the inflated uncertainty in the model, and people are taking approximately one sample to catch the ball.} \betazero{}, \betaone{}, and \betatwo{}.
-
-We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples.
-The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A).
-A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}).
-As shown in Table \ref{tbl:rt}, both models do equally well at explaining overall RT in terms of correlation.
-According to both BIC and AIC, the $T=1$ model does slightly worse (\BicNoSamples{} and \AicNoSamples{}) than the full model (\BicFull{} and \AicFull{}).
-Moreover, the $T=1$ model cannot explain variance in RTs within bounces, whereas the full model with $T=2$ can (Table \ref{tbl:rt}).
-If the number of bounces is excluded entirely, the full model can predict human RTs to a moderate degree (\NoBouncesHoleRTCorr{}), while the model with $T=1$ cannot predict RTs at all.
-
-\section{Discussion}
-
-In this paper, we asked the question: do people optimally use mental simulations?
-We hypothesized that people use noisy physical simulations to predict whether a ball would go in a hole, and that they vary the number of simulations in order to exploit the fact that some judgments are easier to make than others.
-The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on the trials they were most uncertain about.
-Comparing people's responses and response times to those of the model, we found an extremely strong fit.
-This provides evidence that people not only rely on approximate physical simulations, but that they optimally vary the number of simulations that they run according to \textsc{sprt}.
-
 \begin{table}
+    \centering
     \begin{tabular}{ccl}
     \toprule
-    \textbf{Threshold} & \textbf{Bounces} & \textbf{Correlation} \\
+    \textbf{Model} & \textbf{Bounces} & \textbf{Correlation} \\
     \midrule
@@
 
+If we assume that every sample takes the same amount of time, RTs as predicted by the model should be directly proportional to $\mathbb{E}[N\,|\,T,p]$.
+However, because bounces were a strong predictor of RT, we also incorporated the number of bounces, $B$, according to $RT = \beta_0 + (\beta_1 + \beta_2\cdot{}\mathbb{E}[B]) \cdot{}\mathbb{E}[N\,|\,T,p]$.
+Briefly, $\beta_0$ is the time to set up the simulation(s) and to respond, $\beta_1$ is the time to simulate with no bounces, and $\beta_2$ is the time needed to simulate each bounce.
+We used the physical simulation model to determine $\mathbb{E}[B]$ as the average number of times the ball bounced across all model simulations.
+We then fit all parameters ($T$, $\sigma_{adj}$, $\beta_0$, $\beta_1$, and $\beta_2$) to minimize sum squared error between modeled and observed RTs, using 10000 samples from the physical simulation model.
+The best fitting values were: \threshold{}, \sdadj{},\footnote{If \sdadj{}, then $M<1$. How could people be taking less than one sample?
+We suspect that $\sigma_{adj}<1$ because the model overestimates the standard deviation of the ball's trajectory; thus, it is likely that people are taking one sample, and $\sigma_{adj}$ is adjusting for inflated uncertainty in the model.} \betazero{}, \betaone{}, and \betatwo{}.
+
+We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples.
+The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and is also a good predictor of RT (\HoleRTCorr{}).
+A model that takes one sample each time (equivalent to \textsc{sprt} with $T=1$) is slightly better at explaining people's responses (\RawHoleResponseCorr{}), and is equally good at explaining overall RT in terms of correlation (\NoSamplesHoleRTCorr{}).
+However, according to both BIC and AIC, the $T=1$ model is slightly worse (\BicNoSamples{} and \AicNoSamples{}) than the full model (\BicFull{} and \AicFull{}) at explaining RTs.
+Moreover, the $T=1$ model cannot explain variance in RTs within bounces, whereas the full model with $T=2$ can (see Table \ref{tbl:rt}).
+If the number of bounces is excluded, the model with $T=2$ can predict human RTs to a moderate degree (\NoBouncesHoleRTCorr{}), while the model with $T=1$ cannot predict RTs at all.
+
+\section{Discussion}
+
+In this paper, we asked the question: do people optimally use mental simulations?
+We hypothesized that people use noisy physical simulations to predict whether a ball would go in a hole, and that they vary the number of simulations in order to exploit the fact that some judgments are easier to make than others.
+The results of our experiment paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on the trials they were most uncertain about.
+Comparing people's responses and response times to those of the model, we found a strong fit.
+This provides evidence that people not only rely on approximate physical simulations, but that they vary the number of simulations that they run according to \textsc{sprt}.
+
 If \textsc{sprt} is the optimal strategy, then what is the optimal threshold?
@@
 According to \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples.
-While taking a small number of samples clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, this strategy maximizes expected utility across a large number of judgments.
+While taking a small number of samples provides a worse chance of making a good decision than taking multiple samples, over the long run, this strategy maximizes expected utility across a large number of judgments.
 There has been some evidence that this story also holds true for mental simulations.
 For example, \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.
-However, this paper is the first to provide evidence not only that people use a small number of simulations, but that they systematically vary the number of simulations rationally in response to task demands.
+However, this paper is the first to provide evidence not only that people use a small number of simulations, but that they vary the number of simulations in response to task demands.
 
@@
 In this work, we demonstrated that when people use mental simulation, they are sensitive to their own uncertainty in reasoning about the task and accordingly adjust how many simulations they run.
-This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but specifically \emph{how} they use it.
+This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but \emph{how} they use it.
 While there are still many questions left unanswered---e.g., how do people use simulations in non-binary tasks?---this work brings us one step closer to understanding of how mental simulation is used.
+
+\subsection{Acknowledgments}
+
+This work was supported by \TODO{}
 
@@
 
-We recruited \PaddleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework.
-Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work.
-Additionally, we excluded \PaddleNumFailed{} participants from analysis for failing to catch the ball on more than one control trial, leaving a total of \PaddleNumOk{} participants.
+We recruited \PaddleNumComplete{} participants using psiTurk \cite{McDonnell12}.
+Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for 5 minutes of work.
+We excluded \PaddleNumFailed{} participants for failing to catch the ball on more than one control trial.
 
@@
 
-The stimuli were modified versions of those used the main experiment, with two differences.
+The stimuli were modified versions of those used in the main experiment, with two differences.
 First, instead of a wall with a hole in it, there was a paddle of length 100px that could move up and down the $y$-axis.
-Second, instead of a full feedback animation, we just displayed the last frame of the animation.
-Because there was no hole that could vary by trial, there were only 48 stimuli, plus the seven instruction trials and eight catch trials.
+Second, instead of a full feedback animation, we just displayed the last frame.
+Because there was no hole that could vary by trial, there were only 48 stimuli, plus seven instruction and eight catch trials.
 
@@
 
-The experiment was divided into two phases: the training phase (consisting of seven trials), and the experimental phase (consisting of the 48 experimental trials, with the eight control trials evenly interspersed).
-On each trial, participants were shown the scene, including the initial position of the ball and the location of the hole.
-The paddle begin at the center of the $y$-axis, and was freely movable along the $y$-axis from the very beginning of the trial.
-Participants were instructed to press ``space'' to begin the trial and display the stimulus presentation animation.
+Like the main experiment, there were two phases: the training phase and the experimental phase.
+On each trial, participants were shown the scene, including the initial position of the ball.
+The paddle begin at the center of the $y$-axis, and was freely movable at the start of the trial.
+Participants were instructed to press ``space'' to begin the trial and display the stimulus animation.
 After the stimulus presentation, a gray occluder appeared, as well as a timer that began counting down for 2 seconds.
-During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.
-When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed.
-If the ball was on the paddle, then participants were told, ``You caught the ball!''.
-If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.''
-Participants were then instructed to press ``space'' to begin the next trial.
+During this time, participants had to move the paddle to catch the ball in the position it would be when the timer was up.
+When the timer finished, the paddle froze, the occluder was removed, and the full path of the ball was revealed.
+Participants were told whether they caught the ball or not, and then instructed to press ``space'' to begin the next trial.
 
@@
 \bibliographystyle{apacite}
-
+\renewcommand{\bibliographytypesize}{\small}
 \setlength{\bibleftmargin}{.125in}
 \setlength{\bibindent}{-\bibleftmargin}
-
 \bibliography{references}

### 2015-04-30 manuscript.tex
Minor clarifications, grant information

@@
     \end{tabular}
-    \caption{Correlations between human and model RTs.}
+    \vspace{.25cm}
+    \caption{\textbf{Correlations between human and model RTs.} The SPRT model ($T=2$) can capture variations in RTs within bounce conditions, while the single sample model ($T=1$) cannot.
+Note that the correlations for the $T=1$ model are non-zero because we estimate $\mathbb{E}[B]$ from the simulation model, so there is some variation in the expected number of bounces across stimuli.}
     \label{tbl:rt}
@@
 
-Mental simulation is a powerful and flexible tool, as it offers us a way to make predictions about scenarios that have not yet come to pass, or which may never come to pass.
+Mental simulation is a powerful and flexible tool, as it offers a way to make predictions about scenarios that have not yet (or may never) come to pass.
 In this work, we demonstrated that when people use mental simulation, they are sensitive to their own uncertainty in reasoning about the task and accordingly adjust how many simulations they run.
@@
 
-This work was supported by \TODO{}
+This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and \TODO{}.
 
@@
 Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for 5 minutes of work.
-We excluded \PaddleNumFailed{} participants for failing to catch the ball on more than one control trial.
+We excluded \PaddleNumFailed{} people for failing to catch the ball on more than one control trial.
 

### 2015-04-30 manuscript.tex
More clarification

@@
     \caption{\textbf{Correlations between human and model RTs.} The SPRT model ($T=2$) can capture variations in RTs within bounce conditions, while the single sample model ($T=1$) cannot.
-Note that the correlations for the $T=1$ model are non-zero because we estimate $\mathbb{E}[B]$ from the simulation model, so there is some variation in the expected number of bounces across stimuli.}
+To compute the correlations within bounce conditions, we grouped stimuli by the number of bounces shown in the feedback, but within bounce conditions we estimate $\mathbb{E}[B]$ from the simulation model.
+Thus, the expected number of bounces varies slightly across stimuli, which is why the correlations for the $T=1$ model are non-zero.}
     \label{tbl:rt}

### 2015-05-01 manuscript.tex
Remaining grant information, a few more minor edits

@@
 The agent may take samples $X_i$ from a Bernoulli distribution with an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples.
-Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
+Then, the decision rule that minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.
 
@@
 
-In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
+In order to ensure that participants never saw the same initial animation twice, we used a Latin square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
 Thus, each participant saw each initial animation once, each trial type 12 times, and each hole size 24 times.
@@
 
-This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and \TODO{}.
+This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and grant number N00014-13-1-0341 from the Office of Naval Research.
 
